### 2021-07-05 msgauge-temp.tex
Kickstarting the repository.

%- HandOut Flag -----------------------------------------------------------------------------------------
\makeatletter
\@ifundefined{ifHandout}{%
  \expandafter\newif\csname ifHandout\endcsname
}{}
\makeatother

%- D0cum3nt ----------------------------------------------------------------------------------------------
%\documentclass[beamer,10pt]{standalone}   
\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue

\ifHandout
	\setbeameroption{show notes} %print notes   
\fi

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usetikzlibrary{positioning}
\usepackage{multicol}

%--Beamer Style-----------------------------------------------------------------------------------------------
\usetheme{toninus}
\usepackage{animate}
\usetikzlibrary{positioning, arrows}
\usetikzlibrary{shapes}

\begin{document}

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Symplectic geometry}
\begin{columns}[T]
	\begin{column}{.50\linewidth}
		\centering
		\textit{ "geometric approach" to mechanics \dots}
		%
		\begin{columns}
			\begin{column}{.50\linewidth}
				\begin{center}
					\includegraphics[width=0.8\linewidth]{Pictures/pendulum13}			
				\end{center}
			\end{column}	
			\begin{column}{.50\linewidth}
				\begin{center}
					\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
				\end{center}
			\end{column}	
		\end{columns}
		%
		\begin{defblock}[Symplectic Manifold]
			\includestandalone[width=0.95\textwidth]{Pictures/Figure_sym}	
		\end{defblock}
		%
		\begin{exblock}[$M = T^\ast Q$ is symplectic]
			$\omega = d \theta $ with
			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
		\end{exblock}
	\end{column}
	\vrule{}
	\pause
	\begin{column}{.50\linewidth}
		\centering
		\textit{ "algebraic approach" to mechanics \dots}
		\vspace{1em}	
		\begin{defblock}[Classical Observables]
			Unital, associative, commutative algebra $C^\infty(M)$.
		\end{defblock}
		%
		\vspace{1em}
		\pause
		\begin{defblock}[Hamiltonian vector fields]
			$v_f \in \mathfrak{X}(M)$ such that:
			$$\iota_{v_f} \omega = -df \quad \text{(exact)}$$ %$\in B^1(M)$
			\small$v_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.
		\end{defblock}
		%
		\begin{defblock}[Poisson Algebra of Observables]
			$C^\infty(M)$ is a Poisson algebra with
			$$\{f,g\} = \iota_{v_g} \iota_{v_f} \omega = \omega(v_f,v_g) ~.$$
		\end{defblock}
	\end{column}
\end{columns}
\end{frame}
\note[itemize]{
	\footnotesize

	\item We work in the framework of multisymplectic geometry which is one of the possible generalizations of the well-established field of symplectic geometry.

	\item To recall what symplectic geometry is let me assume a particular point of view: mechanics.
	\\
	Idea:"
	Symplectic geometry is a branch of differential geometry studying symplectic manifolds; it originated as a formalization of the mathematical apparatus of classical mechanics and geometric optics."{\href{https://ncatlab.org/nlab/show/symplectic+geometry}{nlab}}

	Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, ordinary, classical, mechanical systems.

	\item $\theta$ = \emph{tautological 1-form}.
		$\theta$ evaluated at $p\in T^*Q$ in the fibre of $q\in Q$ and contracted with $v$ coincides with the form $p$ evaluated at $q$ and contracted with the push forward of $v$.

	\item We identify a special class of vector fields.
		Out of them one can define a Lie bracket.

	\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Multisymplectic geometry in a nutshell}
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
	\end{block}
	\vfill	
	\begin{table}
		\only<2>{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
            \\
            \hline
  \multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &  \multicolumn{1}{@{}c@{}}{}              \\
		\end{tabular}

		}
		\onslide<3->{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting 
			\tikz[baseline,remember picture]{\node[rounded corners,
                        fill=orange!10,draw=orange!30,anchor=base]            
            			(target) {homotopy comomentum map};
            }
            \\
            \hline
  \multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &
            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
               \\
		\end{tabular}
		}
	\end{table}		
	\vfill
	\onslide<4->{

	\begin{block}{Scope of the thesis}
		\begin{itemize}
			\item[$\bullet$] Develop theory of 
				\tikz[baseline,remember picture]{\node[rounded corners,
                        fill=orange!10,draw=orange!30,anchor=base]            
            			(base) {homotopy comomentum maps};
            	}
            \item[$\bullet$] produce new meaningful examples.
		\end{itemize}
	\end{block}

                    \begin{tikzpicture}[overlay,remember picture]
                    \path[->]<4-> (base.north east) edge[bend right](target.south east);
                    \end{tikzpicture}
	}

\end{frame}
\note[itemize]{
	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
point-like particle constrained to some manifold), it is possible to associate a multisymplectic
manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}

	\item General ideas basic parallelisms with caveats
	\item caveat: points in multiphase spaces are not states
	\item the table hides the duality between geometric and algebraic approaches to the problem.
	\item 
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Multisymplectic manifolds} %Fragile -->workaround tikzcd
	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)}]
	\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
	\end{defblock}
	%
	\begin{defblock}[Non-degenerate $(n+1)$-form]
		\begin{columns}
			\begin{column}{.45\linewidth}
				\centering{
				The $\omega^\flat$ (flat) bundle map is injective.
				}
			\end{column}
			\begin{column}{.5\linewidth}
						\vspace{-.5em}
				\[
				\begin{tikzcd}[column sep= small,row sep=0ex,
				/tikz/column 1/.append style={anchor=base east}]
				    \omega^\flat \colon T M \ar[r]& \Lambda^n T^\ast M \\
  						 (x,u) \ar[r, mapsto]& (x,\iota_{u} \omega_x)						
				\end{tikzcd}	
				\]
			\end{column}
		\end{columns}
	\end{defblock}
	%
	\pause
	\begin{defblock}[Hamiltonian $(n-1)$-forms]
		\begin{displaymath}
			\Omega^{n-1}_{ham}(M,\omega) 	:=
			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
				\exists \mathscr{v}_\sigma \in \mathfrak{X}(M) ~:~ 
				\tikz[baseline,remember picture]{\node[rounded corners,
                        fill=orange!5,draw=orange!30,anchor=base]            
            			(target) {$d \sigma = -\iota_{\mathscr{v}_\sigma} \omega$ };
            	}				
				~\biggr\} 
			\end{displaymath}
	\end{defblock}
	%
	%
	\pause
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!5,draw=orange!30,anchor=base]            
            	 (base) at ($(current page.east)-(2.25,1.8)$) [rotate=-0,text width=4cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
		}	
	\begin{tikzpicture}[overlay,remember picture]
    	\path[->] (base.west) edge[bend left,red](target.south west);
    \end{tikzpicture}	
	\pause
	\vfill
	%
	\begin{block}{Examples:}
		\vspace{-.5em}
		\setbeamercovered{transparent}
		\begin{itemize}[<+->]
			\item[$\bullet$] $n=1$ \qquad\qquad\qquad $\Rightarrow$\quad $\omega$ is a symplectic form
			\item[$\bullet$]  $n=(dim(M)-1)$ \quad$\Rightarrow$\quad $\omega$ is a volume form
			%Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
			%\item[$\bullet$] Let $G$ a semisimple Lie group and $\langle\cdot,\cdot \rangle$  its killing form. Then $\langle [\cdot,\cdot],\cdot \rangle$ extends to a biinvariant multisymplectic form $\omega$.
			\item[$\bullet$] Let $Q$ a smooth manifold, the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.%
			\quad
			\textit{(cfr, \href{https://arxiv.org/abs/physics/9801019}{GIMMSY} construction for classical field theories)}
		\end{itemize}
	\end{block}

%
\end{frame}
\note[itemize]{
	\item Multisymplectic ($n$-plectic) geometry is a generalization of symplectic geometry where a closed, non degenerate $n+1$-form $(n\geq 1)$  takes the place of the symplectic 2-form

	\item multisymplectic means \emph{going higher} in the degree of $\omega$

	\item non degeneracy means $\iota_v\omega = 0 \Leftrightarrow v=0$.

	\item examples 
		\begin{itemize}
			\item[$\bullet$] 1-plectic $=$ symplectic
			\item[$\bullet$] Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
			\item[$\bullet$] The multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.
		\end{itemize}

	\item We recognize the special class of forms, called Hamiltonian, determining the Hamiltonian vector fields. 
	Not every $n-1$ form admits an Hamiltonian vector field.
	When it exists, non degeneracy guarantees unicity.

	\item Observe also that, by degree reason, when $n$ is equal to $1$ or $dim(M)+1$ an injective flat map $\flat$ is also bijective.

	\item It is important to stress that mechanical systems are not the only source instances of this class of of structures. 
				e.g. any semisimple Lie groups has associated a 2-plectic structure and any oriented $n+1$ dimensional manifold is naturally $n$-plectic.

}
%---------------------------------------------------------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Lie $\infty$-algebra of Observables}
\begin{frame}[fragile,t]{Lie $\infty$-algebra of Observables (higher observables) }
	Let be $(M,\omega)$ a $n$-plectic manifold.
	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)}]
		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
		\vspace{-2.5em}
		\begin{center}
		\ifHandout
			\includestandalone{Pictures/Figure_Observables}	
		\else
			\includestandalone{Pictures/Frame_Observables}
		\fi				
		\end{center}
		\onslide<2->{
			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
			\vspace{-1.5em}
			\begin{center}
				\includestandalone{Pictures/Equation_Multibracket}	
			\end{center}
		}
		%
	\end{defblock}
  	\vfill
	\onslide<3->{
		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
	\vfill
	\begin{columns}
		\hfill
		\begin{column}{.11\linewidth}	
			If $n>1$:

		\end{column}	
		\begin{column}{.8\linewidth}
		\begin{itemize}
			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
			\hspace*{4.25em}
			 Jacobi equation \emph{up to homotopies}.
		\end{itemize}		
		\end{column}		
	\end{columns}
	}
  \end{frame}
 \note[itemize]{
	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$ 
 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
 }
%------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Homotopy comomentum maps}\label{frame:hcmm-main}
\begin{frame}[fragile]{Homotopy comomentum maps}
	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
	\vfill
	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)}]
		\ifHandout
			\includestandalone{Pictures/Figure_Lifting}
		\else
			\includestandalone{Pictures/Frame_Lifting}
		\fi					
	\end{defblock}
	\onslide<4->{
	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
			%
			HCMM is a sequence of (graded-skew) multilinear maps:
			\begin{displaymath}
				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
			\end{displaymath}
			\emph{fulfilling:}%\emph{such that:}
			\begin{itemize}
				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
				\item<6-> $d f_k (p) = f_{k-1} (
				\tikz[baseline,remember picture]{\node[rounded corners,
                        fill=green!5,draw=green!30,anchor=base]            
            			(target) {$\partial $ };
            	}				
				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
			\end{itemize}
		\onslide<7->{
			\tikz[overlay,remember picture]
			{
				\node[rounded corners,
	                 draw=green!30,anchor=base]            
	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
			}	
		\begin{tikzpicture}[overlay,remember picture]
	    	\path[->] (base.west) edge[bend right,green](target.north east);
	    \end{tikzpicture}
	    }
	\end{lemblock}	
	}
	\vfill
\end{frame}
\note[itemize]{
	\item  An infinitesimal symmetry is a lie algebra morphism such that $\mathcal{L}_{v_x} \omega = 0 ~ \forall x \in \mathfrak{g}$.
	\\ (It is also call an infinitesimal multisymplectic action and $v_x$ is the infinitesimal generator of the action, corresponding to $x \in \mathfrak g$.) 
	\item Essentially, admitting a comoment maps mean that $v$ acts via Hamiltonian vector fields.
	\item In mechanical terms, a moment map is a tool associated with a Hamiltonian action of a Lie group on a symplectic manifold, used to construct conserved quantities for the action.(see \ref{frame:HCMMandConserved} in appendix.
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

\begin{frame}[fragile]{Compatibility between gauge transformations and comoment maps}
	%
	Consider $(M,\omega)$ \alert{symplectic mfd.}
	\only<5-11>{ and \alert{\underline{prequantizable}} ($S^1$-bundle $P$, connection $\theta$)}
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/Frame_BigDiagram_symplectic}
	\end{center}
	%
	\vspace{-2em}
	\begin{minipage}[t][1.7cm][t]{\textwidth}
	\begin{itemize}
		\only<1-4>{
			\item<2-> Given a Symp. mfd. $(M,\omega)$ there is a naturally associated Poisson algebra ...
			\item<3-> .\alert<+>{... and also a Lie Algebroid}.
			\item<4-> A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra;
		}
		\only<5-6>{
			\item<5-> Prequantization Bundle $S^1\hookrightarrow P \to M$ with connection $\theta$,
			\item<5-> "infinitesimal quantomorphisms" $Q(P,\theta):=\lbrace Y \in \mathfrak{X}(P)~|~ \mathcal{L}_Y \theta =0 \}$.
		}
		\only<7-11>{
		\item<7-> Consider a deformed structure $\tilde{\omega}= \omega + d B$ with $B\in C^\infty(M)$;
		\item<9-> There is a natural isomorphism in the Lie Alg.oids category,
		\item<11-> Considering $\mathfrak{g}\circlearrowleft M$ preserving $\omega$ and $\tilde{\omega}$ ...
		}
		\item<12-> Neglect the prequantization...
		\vspace{-1em} 
			\begin{displaymath}
				\begin{tikzcd}
					\Psi~:&[-1em] C^{\infty}(M)_\omega \ar[r,"\Psi"]& \Gamma(TM\oplus \mathbb{R})_\omega
					\\[-2em]
					& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
				\end{tikzcd}
			\end{displaymath}
	\end{itemize}
	\end{minipage}
	\vfill
	\tcbset{colback=white,
	colbacktitle=white,
	colframe=red!70!black,
	boxrule=1pt,
	colupper=red!70!black,
	arc=15pt,
	}
	\begin{minipage}[t][1.7cm][t]{\textwidth}
	\only<6>{ 
		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
			\color{blue}{
			The left square and right triangles commutes!
			}
		\end{tcolorbox}
	}
	\only<11>{
		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
			\color{blue}{
			The left square and right triangle commute!
			}
		\end{tcolorbox}
	}
	\only<12>{
		\vspace{-.75em}
		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
			\color{blue}{
			The central pentagon commutes!
			}
		\end{tcolorbox}
	\vfill
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{What happens in the higher (n-plectic) case?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\end{minipage}
	%
\end{frame}
\note[itemize]{
	\item The horizontal embedding is  $f \mapsto (v_f,f)$;
	\item Vertical maps are also known as \emph{Gauge transformations}
	\item upshot: 
	\begin{enumerate}
		\item 
	\end{enumerate}
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
	Consider now $\omega$ \alert{$n$-plectic}
	\vfill
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_Embedding_Diagram_k-plectic_V1}
	\end{center}
	\vfill
	\only<1-3>{
	\begin{itemize}
		\item<2-> Higher analogue of the Courant algebroid $\rightsquigarrow$ \alert{\emph{Vinogradov algebroid}}
			\begin{displaymath}
			E^n = \left(TM\oplus\bigwedge^{n-1}T^\ast M \right)
			\end{displaymath}
		\item<3->  Vin. alg.oids are $NQ$-manifolds ($L_\infty$-algebroids).
		\\ Associated $L_\infty$-algebra on the graded vector space
		\begin{displaymath}\label{eq:VSpace}
			{\mathcal{V}^k} =
			\begin{cases}
				\mathfrak{X}(M)\oplus \Omega^{n-1}(M)  &\quad k=0,\\
				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
			\end{cases}
		\end{displaymath}
	\end{itemize}
	}

	\only<4->{
	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2021}.]
	\begin{itemize}[leftmargin=0pt]
		\item[$\cdot$]<4-> 
			consider the graded vector subspace $\mathcal{A}$
			\begin{displaymath}
			\mathclap{
			{\mathcal{A}^k} =
			\begin{cases}
		\left.\left\lbrace
		\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
		~ \right\vert ~
		\iota_X \omega = -d \alpha\right\rbrace
&\quad k=0,\\
				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
			\end{cases}			
			}
			\end{displaymath}						
		\item[$\cdot$]<5-> 
			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
		\item[$\cdot$]<6->

			$L_\infty(M,\omega) \cong 
				(\mathcal{A},\pi) \color{blue}\cong\color{black}
				(\mathcal{A},\mu) \hookrightarrow
				L_\infty(E^n,\omega)$
	\end{itemize}
	\end{thmblock}
	}
	\only<6->{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!1,draw=orange!30,anchor=base]            
            	 (base) at ($(current page.east)-(2.25,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
            	 Complete proof\\
            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
            	 }}};
		}			
	}

\end{frame}
\note{}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Compatibility with Gauge transformations}
	Consider now $\omega$ \alert{n-plectic} \quad and \alert{$\tilde{\omega}=\omega + d B$}:
	\vfill
	%
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_Gauge_Diagram_k-plectic}
	\end{center}	
	%
	\vfill
	%

	\begin{itemize}
	\only<1-3>{
		\item<2-> Vinogradov alg.oids w.r.t cohomologous twisting closed forms are isomorphic.
		\item<3-> Induced isomorphism at the level of $L_\infty$-algebras
	}
	\only<4->{
		\item<4-> Consider a Lie algebra action $\mathfrak{g}\to \mathfrak{X}(M)$ admitting HCMM w.r.t $\omega$ and $\tilde{\omega}$
	}
	\end{itemize}

	\vfill
	\tcbset{colback=white,
		colbacktitle=white,
		colframe=blue!70!black,
		boxrule=1pt,
		colupper=blue!70!black,
		arc=15pt,
		}
	\onslide<5->{
	\begin{tcolorbox}[sidebyside,righthand width=.75\linewidth]
		Thm: \cite{Miti2021}
		\tcblower
		\color{blue}
The central square commutes. 
			\\\emph{(On the nose, not "up to homotopies")}.
	\end{tcolorbox}	
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!1,draw=orange!30,anchor=base]            
            	 (base) at ($(current page.east)-(1.75,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
            	 Complete proof\\
            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
            	 }}};
		}

	}

\end{frame}
\note[itemize]{
	\item Our results can be seen as a tiny step toward  undestanding the analogue of prequantization in the setting of multisymplectic geometry (hence field theory).
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

\end{document}

### 2021-07-06 msgauge-appendix.tex
Slides, first version.

--- 2021-07-05 msgauge-temp.tex
@@
+%+----------------------------------------------------------------------------+
+%| SLIDES: 
+%| Chapter: Complementary material - details on eventual questions
+%| Author: Antonio miti
+%| Event: PHD preliminary Defence
+%+----------------------------------------------------------------------------+
+
 %- HandOut Flag -----------------------------------------------------------------------------------------
-\makeatletter
-\@ifundefined{ifHandout}{%
-  \expandafter\newif\csname ifHandout\endcsname
-}{}
-\makeatother
+\newif\ifHandout
 
 %- D0cum3nt ----------------------------------------------------------------------------------------------
-%\documentclass[beamer,10pt]{standalone}   
-\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
+\documentclass[beamer,10pt]{standalone}   
+%\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
 
+%- HandOut Flag -----------------------------------------------------------------------------------------
 \ifHandout
@@
 \usepackage{custom-style}
-\usetikzlibrary{positioning}
-\usepackage{multicol}
 
@@
 \usetheme{toninus}
-\usepackage{animate}
-\usetikzlibrary{positioning, arrows}
-\usetikzlibrary{shapes}
 
+\providecommand{\blank}{\text{\textvisiblespace}}
+
+\newcommand{\subsectiontitle}{
+  \begin{frame}
+  \vfill
+  \centering
+  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
+    \usebeamerfont{title}\insertsectionhead\par%
+    \usebeamerfont{title}\insertsubsectionhead\par%
+  \end{beamercolorbox}
+  \vfill
+  \end{frame}
+}
+
+\providecommand{\blank}{\text{\textvisiblespace}}
+
+%---------------------------------------------------------------------------------------------------------------------------------------------------
+%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
 \begin{document}
+%------------------------------------------------------------------------------------------------
+
+%##################################################################################
+\begin{frame}
+	\begin{center}
+	\Huge\emph{Supplementary Material}
+	\end{center}
+\end{frame}
+\note[itemize]{
+	\item
+}
+\addtocounter{framenumber}{-1}
+%##################################################################################
+
+%===================================================================================
+\section{Background}
+%===================================================================================
 
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Symplectic geometry}
-\begin{columns}[T]
-	\begin{column}{.50\linewidth}
-		\centering
-		\textit{ "geometric approach" to mechanics \dots}
-		%
-		\begin{columns}
-			\begin{column}{.50\linewidth}
-				\begin{center}
-					\includegraphics[width=0.8\linewidth]{Pictures/pendulum13}			
-				\end{center}
-			\end{column}	
-			\begin{column}{.50\linewidth}
-				\begin{center}
-					\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
-				\end{center}
-			\end{column}	
-		\end{columns}
-		%
-		\begin{defblock}[Symplectic Manifold]
-			\includestandalone[width=0.95\textwidth]{Pictures/Figure_sym}	
-		\end{defblock}
-		%
-		\begin{exblock}[$M = T^\ast Q$ is symplectic]
-			$\omega = d \theta $ with
-			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
-		\end{exblock}
-	\end{column}
-	\vrule{}
-	\pause
-	\begin{column}{.50\linewidth}
-		\centering
-		\textit{ "algebraic approach" to mechanics \dots}
-		\vspace{1em}	
-		\begin{defblock}[Classical Observables]
-			Unital, associative, commutative algebra $C^\infty(M)$.
-		\end{defblock}
-		%
-		\vspace{1em}
-		\pause
-		\begin{defblock}[Hamiltonian vector fields]
-			$v_f \in \mathfrak{X}(M)$ such that:
-			$$\iota_{v_f} \omega = -df \quad \text{(exact)}$$ %$\in B^1(M)$
-			\small$v_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.
-		\end{defblock}
-		%
-		\begin{defblock}[Poisson Algebra of Observables]
-			$C^\infty(M)$ is a Poisson algebra with
-			$$\{f,g\} = \iota_{v_g} \iota_{v_f} \omega = \omega(v_f,v_g) ~.$$
-		\end{defblock}
-	\end{column}
-\end{columns}
-\end{frame}
-\note[itemize]{
-	\footnotesize
-
-	\item We work in the framework of multisymplectic geometry which is one of the possible generalizations of the well-established field of symplectic geometry.
-
-	\item To recall what symplectic geometry is let me assume a particular point of view: mechanics.
-	\\
-	Idea:"
-	Symplectic geometry is a branch of differential geometry studying symplectic manifolds; it originated as a formalization of the mathematical apparatus of classical mechanics and geometric optics."{\href{https://ncatlab.org/nlab/show/symplectic+geometry}{nlab}}
-
-	Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, ordinary, classical, mechanical systems.
-
-	\item $\theta$ = \emph{tautological 1-form}.
-		$\theta$ evaluated at $p\in T^*Q$ in the fibre of $q\in Q$ and contracted with $v$ coincides with the form $p$ evaluated at $q$ and contracted with the push forward of $v$.
-
-	\item We identify a special class of vector fields.
-		Out of them one can define a Lie bracket.
-
-	\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)
-}
+\subsection{MultiSymplectic Geometry}
 %-------------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Lie $\infty$-algebra of Observables}
-\begin{frame}[fragile,t]{Lie $\infty$-algebra of Observables (higher observables) }
-	Let be $(M,\omega)$ a $n$-plectic manifold.
-	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)}]
-		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
-		\vspace{-2.5em}
-		\begin{center}
-		\ifHandout
-			\includestandalone{Pictures/Figure_Observables}	
-		\else
-			\includestandalone{Pictures/Frame_Observables}
-		\fi				
-		\end{center}
-		\onslide<2->{
-			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
-			\vspace{-1.5em}
-			\begin{center}
-				\includestandalone{Pictures/Equation_Multibracket}	
-			\end{center}
-		}
-		%
-	\end{defblock}
-  	\vfill
-	\onslide<3->{
-		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
-	\vfill
-	\begin{columns}
-		\hfill
-		\begin{column}{.11\linewidth}	
-			If $n>1$:
+\subsection{References}
 
-		\end{column}	
-		\begin{column}{.8\linewidth}
-		\begin{itemize}
-			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
-			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
-			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
-			\hspace*{4.25em}
-			 Jacobi equation \emph{up to homotopies}.
-		\end{itemize}		
-		\end{column}		
-	\end{columns}
-	}
+%------------------------------------------------------------------------------------------------
+% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
+\begin{frame}[t,allowframebreaks]{Extended Bibliography}
+	\bibliographystyle{alpha}
+	\bibliography{bibfile}
 \end{frame}
- \note[itemize]{
-	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
- 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
-	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
-	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
- 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
- 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
-	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
- 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
- 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
- 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
-  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$
- 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
-  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
- }
 %------------------------------------------------------------------------------------------------
 
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Homotopy comomentum maps}\label{frame:hcmm-main}
-\begin{frame}[fragile]{Homotopy comomentum maps}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
-	\vfill
-	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)}]
-		\ifHandout
-			\includestandalone{Pictures/Figure_Lifting}
-		\else
-			\includestandalone{Pictures/Frame_Lifting}
-		\fi					
-	\end{defblock}
-	\onslide<4->{
-	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
-			%
-			HCMM is a sequence of (graded-skew) multilinear maps:
-			\begin{displaymath}
-				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
-				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
-			\end{displaymath}
-			\emph{fulfilling:}%\emph{such that:}
-			\begin{itemize}
-				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
-				\item<6-> $d f_k (p) = f_{k-1} (
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=green!5,draw=green!30,anchor=base]            
-            			(target) {$\partial $ };
-            	}				
-				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
-				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
-			\end{itemize}
-		\onslide<7->{
-			\tikz[overlay,remember picture]
-			{
-				\node[rounded corners,
-	                 draw=green!30,anchor=base]            
-	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
-			}	
-		\begin{tikzpicture}[overlay,remember picture]
-	    	\path[->] (base.west) edge[bend right,green](target.north east);
-	    \end{tikzpicture}
-	    }
-	\end{lemblock}	
-	}
-	\vfill
-\end{frame}
-\note[itemize]{
-	\item  An infinitesimal symmetry is a lie algebra morphism such that $\mathcal{L}_{v_x} \omega = 0 ~ \forall x \in \mathfrak{g}$.
-	\\ (It is also call an infinitesimal multisymplectic action and $v_x$ is the infinitesimal generator of the action, corresponding to $x \in \mathfrak g$.) 
-	\item Essentially, admitting a comoment maps mean that $v$ acts via Hamiltonian vector fields.
-	\item In mechanical terms, a moment map is a tool associated with a Hamiltonian action of a Lie group on a symplectic manifold, used to construct conserved quantities for the action.(see \ref{frame:HCMMandConserved} in appendix.
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-\begin{frame}[fragile]{Compatibility between gauge transformations and comoment maps}
-	%
-	Consider $(M,\omega)$ \alert{symplectic mfd.}
-	\only<5-11>{ and \alert{\underline{prequantizable}} ($S^1$-bundle $P$, connection $\theta$)}
-	%
-	\begin{center}
-			\includestandalone[width=.8\textwidth]{Pictures/Frame_BigDiagram_symplectic}
-	\end{center}
-	%
-	\vspace{-2em}
-	\begin{minipage}[t][1.7cm][t]{\textwidth}
-	\begin{itemize}
-		\only<1-4>{
-			\item<2-> Given a Symp. mfd. $(M,\omega)$ there is a naturally associated Poisson algebra ...
-			\item<3-> .\alert<+>{... and also a Lie Algebroid}.
-			\item<4-> A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra;
-		}
-		\only<5-6>{
-			\item<5-> Prequantization Bundle $S^1\hookrightarrow P \to M$ with connection $\theta$,
-			\item<5-> "infinitesimal quantomorphisms" $Q(P,\theta):=\lbrace Y \in \mathfrak{X}(P)~|~ \mathcal{L}_Y \theta =0 \}$.
-		}
-		\only<7-11>{
-		\item<7-> Consider a deformed structure $\tilde{\omega}= \omega + d B$ with $B\in C^\infty(M)$;
-		\item<9-> There is a natural isomorphism in the Lie Alg.oids category,
-		\item<11-> Considering $\mathfrak{g}\circlearrowleft M$ preserving $\omega$ and $\tilde{\omega}$ ...
-		}
-		\item<12-> Neglect the prequantization...
-		\vspace{-1em} 
-			\begin{displaymath}
-				\begin{tikzcd}
-					\Psi~:&[-1em] C^{\infty}(M)_\omega \ar[r,"\Psi"]& \Gamma(TM\oplus \mathbb{R})_\omega
-					\\[-2em]
-					& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
-				\end{tikzcd}
-			\end{displaymath}
-	\end{itemize}
-	\end{minipage}
-	\vfill
-	\tcbset{colback=white,
-	colbacktitle=white,
-	colframe=red!70!black,
-	boxrule=1pt,
-	colupper=red!70!black,
-	arc=15pt,
-	}
-	\begin{minipage}[t][1.7cm][t]{\textwidth}
-	\only<6>{ 
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The left square and right triangles commutes!
-			}
-		\end{tcolorbox}
-	}
-	\only<11>{
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The left square and right triangle commute!
-			}
-		\end{tcolorbox}
-	}
-	\only<12>{
-		\vspace{-.75em}
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The central pentagon commutes!
-			}
-		\end{tcolorbox}
-	\vfill
-		\vspace{-.75em}
-		\begin{center}
-		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
-			\alert{
-			\faQuestionCircle \qquad
-				{What happens in the higher (n-plectic) case?}
-			\qquad \faQuestionCircle		
-			}
-		}
-		\end{center}
-	}
-	\end{minipage}
-	%
-\end{frame}
-\note[itemize]{
-	\item The horizontal embedding is  $f \mapsto (v_f,f)$;
-	\item Vertical maps are also known as \emph{Gauge transformations}
-	\item upshot: 
-	\begin{enumerate}
-		\item 
-	\end{enumerate}
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
-	Consider now $\omega$ \alert{$n$-plectic}
-	\vfill
-	\begin{center}
-		\includestandalone[width=.8\textwidth]{Pictures/Frame_Embedding_Diagram_k-plectic_V1}
-	\end{center}
-	\vfill
-	\only<1-3>{
-	\begin{itemize}
-		\item<2-> Higher analogue of the Courant algebroid $\rightsquigarrow$ \alert{\emph{Vinogradov algebroid}}
-			\begin{displaymath}
-			E^n = \left(TM\oplus\bigwedge^{n-1}T^\ast M \right)
-			\end{displaymath}
-		\item<3->  Vin. alg.oids are $NQ$-manifolds ($L_\infty$-algebroids).
-		\\ Associated $L_\infty$-algebra on the graded vector space
-		\begin{displaymath}\label{eq:VSpace}
-			{\mathcal{V}^k} =
-			\begin{cases}
-				\mathfrak{X}(M)\oplus \Omega^{n-1}(M)  &\quad k=0,\\
-				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
-			\end{cases}
-		\end{displaymath}
-	\end{itemize}
-	}
-
-	\only<4->{
-	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2021}.]
-	\begin{itemize}[leftmargin=0pt]
-		\item[$\cdot$]<4-> 
-			consider the graded vector subspace $\mathcal{A}$
-			\begin{displaymath}
-			\mathclap{
-			{\mathcal{A}^k} =
-			\begin{cases}
-		\left.\left\lbrace
-		\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
-		~ \right\vert ~
-		\iota_X \omega = -d \alpha\right\rbrace
-&\quad k=0,\\
-				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
-			\end{cases}			
-			}
-			\end{displaymath}						
-		\item[$\cdot$]<5-> 
-			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
-		\item[$\cdot$]<6->
-
-			$L_\infty(M,\omega) \cong 
-				(\mathcal{A},\pi) \color{blue}\cong\color{black}
-				(\mathcal{A},\mu) \hookrightarrow
-				L_\infty(E^n,\omega)$
-	\end{itemize}
-	\end{thmblock}
-	}
-	\only<6->{
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!1,draw=orange!30,anchor=base]            
-            	 (base) at ($(current page.east)-(2.25,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
-            	 Complete proof\\
-            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
-            	 }}};
-		}			
-	}
-
-\end{frame}
-\note{}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Compatibility with Gauge transformations}
-	Consider now $\omega$ \alert{n-plectic} \quad and \alert{$\tilde{\omega}=\omega + d B$}:
-	\vfill
-	%
-	\begin{center}
-		\includestandalone[width=.8\textwidth]{Pictures/Frame_Gauge_Diagram_k-plectic}
-	\end{center}	
-	%
-	\vfill
-	%
-
-	\begin{itemize}
-	\only<1-3>{
-		\item<2-> Vinogradov alg.oids w.r.t cohomologous twisting closed forms are isomorphic.
-		\item<3-> Induced isomorphism at the level of $L_\infty$-algebras
-	}
-	\only<4->{
-		\item<4-> Consider a Lie algebra action $\mathfrak{g}\to \mathfrak{X}(M)$ admitting HCMM w.r.t $\omega$ and $\tilde{\omega}$
-	}
-	\end{itemize}
-
-	\vfill
-	\tcbset{colback=white,
-		colbacktitle=white,
-		colframe=blue!70!black,
-		boxrule=1pt,
-		colupper=blue!70!black,
-		arc=15pt,
-		}
-	\onslide<5->{
-	\begin{tcolorbox}[sidebyside,righthand width=.75\linewidth]
-		Thm: \cite{Miti2021}
-		\tcblower
-		\color{blue}
-The central square commutes. 
-			\\\emph{(On the nose, not "up to homotopies")}.
-	\end{tcolorbox}	
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!1,draw=orange!30,anchor=base]            
-            	 (base) at ($(current page.east)-(1.75,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
-            	 Complete proof\\
-            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
-            	 }}};
-		}
-
-	}
-
-\end{frame}
-\note[itemize]{
-	\item Our results can be seen as a tiny step toward  undestanding the analogue of prequantization in the setting of multisymplectic geometry (hence field theory).
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
+%------------------------------------------------------------------------------------------------
 \end{document}

### 2021-07-06 msgauge-intro.tex
Slides, first version.

--- 2021-07-05 msgauge-temp.tex
@@
 %- D0cum3nt ----------------------------------------------------------------------------------------------
-%\documentclass[beamer,10pt]{standalone}   
-\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
+\documentclass[beamer,10pt]{standalone}   
+%\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
 
@@
 
-%- Packages ----------------------------------------------------------------------------------------------
+%- Packages -------------------------------------------------------------------------------------------
 \usepackage{custom-style}
@@
 \usepackage{multicol}
+\usepackage{stmaryrd}
 
-%--Beamer Style-----------------------------------------------------------------------------------------------
+%--Beamer Style----------------------------------------------------------------------------------------
 \usetheme{toninus}
@@
 \begin{document}
-
+\outline
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Symplectic geometry}
+\begin{frame}{Symplectic geometry (mechanical perspective)}
 \begin{columns}[T]
@@
 		\begin{columns}
-			\begin{column}{.50\linewidth}
+			\begin{column}{.60\linewidth}
 				\begin{center}
-					\includegraphics[width=0.8\linewidth]{Pictures/pendulum13}			
+					\includegraphics[width=0.6\linewidth]{Pictures/pendulum13}			
 				\end{center}
 			\end{column}	
-			\begin{column}{.50\linewidth}
+			\begin{column}{.40\linewidth}
 				\begin{center}
@@
 		\begin{defblock}[Symplectic Manifold]
-			\includestandalone[width=0.95\textwidth]{Pictures/Figure_sym}	
+			\vspace{-1em}
+			\includestandalone[width=1\textwidth]{Pictures/Figure_sym}	
 		\end{defblock}
 		%
+		\pause
 		\begin{exblock}[$M = T^\ast Q$ is symplectic]
@@
 		\end{exblock}
+		%
+		\pause
+		\vspace{1em}
+		\centering
+		\textit{ based on the notion of "states".}		
 	\end{column}
-	\vrule{}
+	\onslide<1->{\vrule{}}
 	\pause
@@
 		\textit{ "algebraic approach" to mechanics \dots}
-		\vspace{1em}	
+		\vspace{.5em}	
 		\begin{defblock}[Classical Observables]
@@
 		%
-		\vspace{1em}
+		\vspace{.5em}
 		\pause
@@
 		\end{defblock}
+		%
+		\pause
+		\vspace{.8em}
+		\centering
+		\textit{ based on the notion of "meaurable quantities".}						
 	\end{column}
@@
 	\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)
+
+	\item take away message: geometric (based on "states") vs algebraic (based on "measurable quantities").7
 }
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Multisymplectic geometry in a nutshell}
+\begin{frame}{From Symplectic to MultiSymplectic (mechanical perspective)}
 	\begin{block}{Historical motivation}
 		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
+		\begin{itemize}
+		 \item[•] Kijowski and W. Tulczyjew \cite{Kijowski1979}; %(1979)
+		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
+		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
+		 \\ $\cdots$
+		\end{itemize}
 	\end{block}
 	\vfill
-	\begin{table}
-		\only<2>{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &  \multicolumn{1}{@{}c@{}}{}              \\
-		\end{tabular}
+	\begin{center}
+	\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
+		\alert{
+		\faWarning \qquad
+			{The lack of a satisfactory notion of observables hindered the spread of this formalism.}	
+		\qquad \faWarning		
+		}
+	}
+	\end{center}
 
+	\vfill
+	\begin{center}
+	\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
+		\alert{
+		\faQuestionCircle \qquad
+			{Why observables are so crucial?\qquad \qquad Quantization!}	
+		\qquad \faQuestionCircle		
 		}
-		\onslide<3->{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting 
-			\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!10,draw=orange!30,anchor=base]            
-            			(target) {homotopy comomentum map};
 	}
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &
-            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
-               \\
-		\end{tabular}
-		}
-	\end{table}		
-	\vfill
-	\onslide<4->{
-
-	\begin{block}{Scope of the thesis}
-		\begin{itemize}
-			\item[$\bullet$] Develop theory of 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!10,draw=orange!30,anchor=base]            
-            			(base) {homotopy comomentum maps};
-            	}
-            \item[$\bullet$] produce new meaningful examples.
-		\end{itemize}
-	\end{block}
-
-                    \begin{tikzpicture}[overlay,remember picture]
-                    \path[->]<4-> (base.north east) edge[bend right](target.south east);
-                    \end{tikzpicture}
-	}
+	\end{center}
 
@@
 manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics} 
+	\item Forger and Romero say: \emph{"The multisymplectic formalism is manifestly consistent with the basic principles of field theory, preserving full covariance, and it is mathematically rigorous because it uses well established methods from calculus on finite-dimensional manifolds.
+On the other hand, it does not seem to permit any obvious definition of the Poisson bracket between observables.
+Even the question of what mathematical objects should represent physical observables is not totally clear and has in fact been the subject of much debate in the literature.
+Moreover, the introduction of n conjugate momenta for each coordinate obscures the usual duality between canonically con- jugate variables (such as momenta and positions), which plays a fundamental role in all known methods of quantization.A definite solution to these problems has yet to be found."}
 
-	\item General ideas basic parallelisms with caveats
-	\item caveat: points in multiphase spaces are not states
-	\item the table hides the duality between geometric and algebraic approaches to the problem.
-	\item 
 }
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Multisymplectic manifolds} %Fragile -->workaround tikzcd
-	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)}]
-	\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
-	\end{defblock}
+\begin{frame}{Observables in $n$-plectic geometry}
 	%
-	\begin{defblock}[Non-degenerate $(n+1)$-form]
-		\begin{columns}
-			\begin{column}{.45\linewidth}
-				\centering{
-				The $\omega^\flat$ (flat) bundle map is injective.
-				}
-			\end{column}
-			\begin{column}{.5\linewidth}
-						\vspace{-.5em}
-				\[
-				\begin{tikzcd}[column sep= small,row sep=0ex,
-				/tikz/column 1/.append style={anchor=base east}]
-				    \omega^\flat \colon T M \ar[r]& \Lambda^n T^\ast M \\
-  						 (x,u) \ar[r, mapsto]& (x,\iota_{u} \omega_x)						
-				\end{tikzcd}	
-				\]
-			\end{column}
-		\end{columns}
-	\end{defblock}
-	%
-	\pause
 	\begin{defblock}[Hamiltonian $(n-1)$-forms]
@@
 	\end{defblock}
-	%
-	%
+
 	\pause
@@
                  fill=orange!5,draw=orange!30,anchor=base]
-            	 (base) at ($(current page.east)-(2.25,1.8)$) [rotate=-0,text width=4cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
+            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
 		}	
 	\begin{tikzpicture}[overlay,remember picture]
-    	\path[->] (base.west) edge[bend left,red](target.south west);
+    	\path[->] (base.south) edge[bend right,red](target.north);
     \end{tikzpicture}
+	%
+	\vspace{-2em}
+	\begin{columns}[T]
 		\pause
-	\vfill
+		\begin{column}{.50\linewidth}
 			%
-	\begin{block}{Examples:}
+			\begin{thmblock}[Observables $L_\infty$-algebra]
+				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
 				\vspace{-.5em}
-		\setbeamercovered{transparent}
-		\begin{itemize}[<+->]
-			\item[$\bullet$] $n=1$ \qquad\qquad\qquad $\Rightarrow$\quad $\omega$ is a symplectic form
-			\item[$\bullet$]  $n=(dim(M)-1)$ \quad$\Rightarrow$\quad $\omega$ is a volume form
-			%Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
-			%\item[$\bullet$] Let $G$ a semisimple Lie group and $\langle\cdot,\cdot \rangle$  its killing form.
-Then $\langle [\cdot,\cdot],\cdot \rangle$ extends to a biinvariant multisymplectic form $\omega$.
-			\item[$\bullet$] Let $Q$ a smooth manifold, the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.%
-			\quad
-			\textit{(cfr, \href{https://arxiv.org/abs/physics/9801019}{GIMMSY} construction for classical field theories)}
+				\begin{displaymath}
+					\lbrace \sigma_1, \sigma_2 \rbrace =			
+					~ - \iota_{\mathscr{v}_1}\iota_{\mathscr{v}_2} \omega 
+				\end{displaymath}			
+				\vspace{.4em}
+				can be "completed" to a \\ $L_\infty-algebra$.
+			\end{thmblock}
+			%
+			\pause
+			\begin{itemize}
+				\item[\cmark] Skew-symmetric;
+				\item[\xmark] multiplication of observables;
+				\item[\xmark] Jacobi equation;
+				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
+				\item[\smark] Jacobi equation \emph{up to homotopies}.
 			\end{itemize}				
-	\end{block}
-
+		\end{column}	
 		%
-\end{frame}
-\note[itemize]{
-	\item Multisymplectic ($n$-plectic) geometry is a generalization of symplectic geometry where a closed, non degenerate $n+1$-form $(n\geq 1)$  takes the place of the symplectic 2-form
-
-	\item multisymplectic means \emph{going higher} in the degree of $\omega$
-
-	\item non degeneracy means $\iota_v\omega = 0 \Leftrightarrow v=0$.
-
-	\item examples 
+		\onslide<1->{\vrule{}}
+		%
+		\pause
+		\begin{column}{.50\linewidth}
+			\begin{thmblock}[Observables Leibniz algebra]
+				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
+				\vspace{-.5em}
+			\begin{displaymath}
+				\llbracket \sigma_1, \sigma_2 \rrbracket =
+				~ \mathcal{L}_{\mathscr{v}_1} \sigma_2
+				~.					
+			\end{displaymath}		
+				\vspace{.4em}
+				can be "completed" to a \\ DG-Leibniz algebra.
+			\end{thmblock}	
+			%
+			\pause
 			\begin{itemize}
-			\item[$\bullet$] 1-plectic $=$ symplectic
-			\item[$\bullet$] Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
-			\item[$\bullet$] The multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.
-		\end{itemize}
-
-	\item We recognize the special class of forms, called Hamiltonian, determining the Hamiltonian vector fields. 
-	Not every $n-1$ form admits an Hamiltonian vector field.
-	When it exists, non degeneracy guarantees unicity.
-
-	\item Observe also that, by degree reason, when $n$ is equal to $1$ or $dim(M)+1$ an injective flat map $\flat$ is also bijective.
-
-	\item It is important to stress that mechanical systems are not the only source instances of this class of of structures. 
-				e.g. any semisimple Lie groups has associated a 2-plectic structure and any oriented $n+1$ dimensional manifold is naturally $n$-plectic.
-
-}
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Lie $\infty$-algebra of Observables}
-\begin{frame}[fragile,t]{Lie $\infty$-algebra of Observables (higher observables) }
-	Let be $(M,\omega)$ a $n$-plectic manifold.
-	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)}]
-		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
-		\vspace{-2.5em}
-		\begin{center}
-		\ifHandout
-			\includestandalone{Pictures/Figure_Observables}	
-		\else
-			\includestandalone{Pictures/Frame_Observables}
-		\fi				
-		\end{center}
-		\onslide<2->{
-			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
-			\vspace{-1.5em}
-			\begin{center}
-				\includestandalone{Pictures/Equation_Multibracket}	
-			\end{center}
-		}
-		%
-	\end{defblock}
-  	\vfill
-	\onslide<3->{
-		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
-	\vfill
-	\begin{columns}
-		\hfill
-		\begin{column}{.11\linewidth}	
-			If $n>1$:
-
-		\end{column}	
-		\begin{column}{.8\linewidth}
-		\begin{itemize}
-			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
-			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
-			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
-			\hspace*{4.25em}
-			 Jacobi equation \emph{up to homotopies}.
+				\item[\xmark] Skew-symmetric;
+				\item[\xmark] multiplication of observables;
+				\item[\cmark] Jacobi equation;
+				\item[\smark] Skew-symmetric \emph{up to homotopies}.
 			\end{itemize}	
@@
 	\end{columns}
-	}
 \end{frame}
 \note[itemize]{
-	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
- 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
-	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
-	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
- 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
- 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
-	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
- 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
- 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
- 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
-  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$
- 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
-  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
- }
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Homotopy comomentum maps}\label{frame:hcmm-main}
-\begin{frame}[fragile]{Homotopy comomentum maps}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
-	\vfill
-	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)}]
-		\ifHandout
-			\includestandalone{Pictures/Figure_Lifting}
-		\else
-			\includestandalone{Pictures/Frame_Lifting}
-		\fi					
-	\end{defblock}
-	\onslide<4->{
-	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
-			%
-			HCMM is a sequence of (graded-skew) multilinear maps:
-			\begin{displaymath}
-				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
-				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
-			\end{displaymath}
-			\emph{fulfilling:}%\emph{such that:}
-			\begin{itemize}
-				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
-				\item<6-> $d f_k (p) = f_{k-1} (
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=green!5,draw=green!30,anchor=base]            
-            			(target) {$\partial $ };
-            	}				
-				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
-				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
-			\end{itemize}
-		\onslide<7->{
-			\tikz[overlay,remember picture]
-			{
-				\node[rounded corners,
-	                 draw=green!30,anchor=base]            
-	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
-			}	
-		\begin{tikzpicture}[overlay,remember picture]
-	    	\path[->] (base.west) edge[bend right,green](target.north east);
-	    \end{tikzpicture}
-	    }
-	\end{lemblock}	
-	}
-	\vfill
-\end{frame}
-\note[itemize]{
-	\item  An infinitesimal symmetry is a lie algebra morphism such that $\mathcal{L}_{v_x} \omega = 0 ~ \forall x \in \mathfrak{g}$.
-	\\ (It is also call an infinitesimal multisymplectic action and $v_x$ is the infinitesimal generator of the action, corresponding to $x \in \mathfrak g$.) 
-	\item Essentially, admitting a comoment maps mean that $v$ acts via Hamiltonian vector fields.
-	\item In mechanical terms, a moment map is a tool associated with a Hamiltonian action of a Lie group on a symplectic manifold, used to construct conserved quantities for the action.(see \ref{frame:HCMMandConserved} in appendix.
+ \item See \cite[\S 7.2]{Rogers2010} about the comparison of these two algebraic structures.
 }
@@
 
-\begin{frame}[fragile]{Compatibility between gauge transformations and comoment maps}
+%------------------------------------------------------------------------------------------------------
+\begin{frame}{Scope of the talk}
 	%
-	Consider $(M,\omega)$ \alert{symplectic mfd.}
-	\only<5-11>{ and \alert{\underline{prequantizable}} ($S^1$-bundle $P$, connection $\theta$)}
-	%
-	\begin{center}
-			\includestandalone[width=.8\textwidth]{Pictures/Frame_BigDiagram_symplectic}
-	\end{center}
-	%
-	\vspace{-2em}
-	\begin{minipage}[t][1.7cm][t]{\textwidth}
-	\begin{itemize}
-		\only<1-4>{
-			\item<2-> Given a Symp. mfd. $(M,\omega)$ there is a naturally associated Poisson algebra ...
-			\item<3-> .\alert<+>{... and also a Lie Algebroid}.
-			\item<4-> A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra;
-		}
-		\only<5-6>{
-			\item<5-> Prequantization Bundle $S^1\hookrightarrow P \to M$ with connection $\theta$,
-			\item<5-> "infinitesimal quantomorphisms" $Q(P,\theta):=\lbrace Y \in \mathfrak{X}(P)~|~ \mathcal{L}_Y \theta =0 \}$.
-		}
-		\only<7-11>{
-		\item<7-> Consider a deformed structure $\tilde{\omega}= \omega + d B$ with $B\in C^\infty(M)$;
-		\item<9-> There is a natural isomorphism in the Lie Alg.oids category,
-		\item<11-> Considering $\mathfrak{g}\circlearrowleft M$ preserving $\omega$ and $\tilde{\omega}$ ...
-		}
-		\item<12-> Neglect the prequantization...
-		\vspace{-1em} 
-			\begin{displaymath}
-				\begin{tikzcd}
-					\Psi~:&[-1em] C^{\infty}(M)_\omega \ar[r,"\Psi"]& \Gamma(TM\oplus \mathbb{R})_\omega
-					\\[-2em]
-					& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
-				\end{tikzcd}
-			\end{displaymath}
-	\end{itemize}
-	\end{minipage}
+	\centering
+	\begin{tikzpicture}
+		\node [draw,ellipse callout, minimum height=10em,minimum width=33em,callout relative pointer={(-2,-.5)}] (L1) {};
+		\node [text width=25em,text centered] (L2) {
+			Broad general question:\\
+			What is the corresponding	 "correct" notion of observables in multisymplectic geometry?	
+		};
+	\end{tikzpicture}
 	\vfill
-	\tcbset{colback=white,
-	colbacktitle=white,
-	colframe=red!70!black,
-	boxrule=1pt,
-	colupper=red!70!black,
-	arc=15pt,
-	}
-	\begin{minipage}[t][1.7cm][t]{\textwidth}
-	\only<6>{ 
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The left square and right triangles commutes!
-			}
-		\end{tcolorbox}
-	}
-	\only<11>{
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The left square and right triangle commute!
-			}
-		\end{tcolorbox}
-	}
-	\only<12>{
-		\vspace{-.75em}
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The central pentagon commutes!
-			}
-		\end{tcolorbox}
-	\vfill
-		\vspace{-.75em}
-		\begin{center}
-		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
-			\alert{
-			\faQuestionCircle \qquad
-				{What happens in the higher (n-plectic) case?}
-			\qquad \faQuestionCircle		
-			}
-		}
-		\end{center}
-	}
-	\end{minipage}
-	%
+	\begin{tikzpicture}
+		\node [draw,ellipse callout, minimum height=10em,minimum width=33em,callout relative pointer={(2,-.5)}] (L1) {};
+		\node [text width=25em,text centered] (L2) {
+			Specific focused question:
+			\\
+			To what extent the compatibility diagram between gauge transformation and comomentum maps extend to the $n$-plectic case?
+		};
+	\end{tikzpicture}
 \end{frame}
 \note[itemize]{
-	\item The horizontal embedding is  $f \mapsto (v_f,f)$;
-	\item Vertical maps are also known as \emph{Gauge transformations}
-	\item upshot: 
-	\begin{enumerate}
 	\item
-	\end{enumerate}
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
-	Consider now $\omega$ \alert{$n$-plectic}
-	\vfill
-	\begin{center}
-		\includestandalone[width=.8\textwidth]{Pictures/Frame_Embedding_Diagram_k-plectic_V1}
-	\end{center}
-	\vfill
-	\only<1-3>{
-	\begin{itemize}
-		\item<2-> Higher analogue of the Courant algebroid $\rightsquigarrow$ \alert{\emph{Vinogradov algebroid}}
-			\begin{displaymath}
-			E^n = \left(TM\oplus\bigwedge^{n-1}T^\ast M \right)
-			\end{displaymath}
-		\item<3->  Vin. alg.oids are $NQ$-manifolds ($L_\infty$-algebroids).
-		\\ Associated $L_\infty$-algebra on the graded vector space
-		\begin{displaymath}\label{eq:VSpace}
-			{\mathcal{V}^k} =
-			\begin{cases}
-				\mathfrak{X}(M)\oplus \Omega^{n-1}(M)  &\quad k=0,\\
-				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
-			\end{cases}
-		\end{displaymath}
-	\end{itemize}
-	}
-
-	\only<4->{
-	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2021}.]
-	\begin{itemize}[leftmargin=0pt]
-		\item[$\cdot$]<4-> 
-			consider the graded vector subspace $\mathcal{A}$
-			\begin{displaymath}
-			\mathclap{
-			{\mathcal{A}^k} =
-			\begin{cases}
-		\left.\left\lbrace
-		\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
-		~ \right\vert ~
-		\iota_X \omega = -d \alpha\right\rbrace
-&\quad k=0,\\
-				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
-			\end{cases}			
-			}
-			\end{displaymath}						
-		\item[$\cdot$]<5-> 
-			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
-		\item[$\cdot$]<6->
-
-			$L_\infty(M,\omega) \cong 
-				(\mathcal{A},\pi) \color{blue}\cong\color{black}
-				(\mathcal{A},\mu) \hookrightarrow
-				L_\infty(E^n,\omega)$
-	\end{itemize}
-	\end{thmblock}
-	}
-	\only<6->{
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!1,draw=orange!30,anchor=base]            
-            	 (base) at ($(current page.east)-(2.25,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
-            	 Complete proof\\
-            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
-            	 }}};
-		}			
-	}
-
-\end{frame}
-\note{}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Compatibility with Gauge transformations}
-	Consider now $\omega$ \alert{n-plectic} \quad and \alert{$\tilde{\omega}=\omega + d B$}:
-	\vfill
-	%
-	\begin{center}
-		\includestandalone[width=.8\textwidth]{Pictures/Frame_Gauge_Diagram_k-plectic}
-	\end{center}	
-	%
-	\vfill
-	%
-
-	\begin{itemize}
-	\only<1-3>{
-		\item<2-> Vinogradov alg.oids w.r.t cohomologous twisting closed forms are isomorphic.
-		\item<3-> Induced isomorphism at the level of $L_\infty$-algebras
-	}
-	\only<4->{
-		\item<4-> Consider a Lie algebra action $\mathfrak{g}\to \mathfrak{X}(M)$ admitting HCMM w.r.t $\omega$ and $\tilde{\omega}$
-	}
-	\end{itemize}
-
-	\vfill
-	\tcbset{colback=white,
-		colbacktitle=white,
-		colframe=blue!70!black,
-		boxrule=1pt,
-		colupper=blue!70!black,
-		arc=15pt,
-		}
-	\onslide<5->{
-	\begin{tcolorbox}[sidebyside,righthand width=.75\linewidth]
-		Thm: \cite{Miti2021}
-		\tcblower
-		\color{blue}
-The central square commutes. 
-			\\\emph{(On the nose, not "up to homotopies")}.
-	\end{tcolorbox}	
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!1,draw=orange!30,anchor=base]            
-            	 (base) at ($(current page.east)-(1.75,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
-            	 Complete proof\\
-            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
-            	 }}};
-		}
-
-	}
-
-\end{frame}
-\note[itemize]{
-	\item Our results can be seen as a tiny step toward  undestanding the analogue of prequantization in the setting of multisymplectic geometry (hence field theory).
 }

### 2021-07-06 msgauge-multisym.tex
Slides, first version.

--- 2021-07-05 msgauge-temp.tex
@@
 \begin{document}
-
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Symplectic geometry}
-\begin{columns}[T]
-	\begin{column}{.50\linewidth}
-		\centering
-		\textit{ "geometric approach" to mechanics \dots}
-		%
-		\begin{columns}
-			\begin{column}{.50\linewidth}
-				\begin{center}
-					\includegraphics[width=0.8\linewidth]{Pictures/pendulum13}			
-				\end{center}
-			\end{column}	
-			\begin{column}{.50\linewidth}
-				\begin{center}
-					\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
-				\end{center}
-			\end{column}	
-		\end{columns}
-		%
-		\begin{defblock}[Symplectic Manifold]
-			\includestandalone[width=0.95\textwidth]{Pictures/Figure_sym}	
-		\end{defblock}
-		%
-		\begin{exblock}[$M = T^\ast Q$ is symplectic]
-			$\omega = d \theta $ with
-			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
-		\end{exblock}
-	\end{column}
-	\vrule{}
-	\pause
-	\begin{column}{.50\linewidth}
-		\centering
-		\textit{ "algebraic approach" to mechanics \dots}
-		\vspace{1em}	
-		\begin{defblock}[Classical Observables]
-			Unital, associative, commutative algebra $C^\infty(M)$.
-		\end{defblock}
-		%
-		\vspace{1em}
-		\pause
-		\begin{defblock}[Hamiltonian vector fields]
-			$v_f \in \mathfrak{X}(M)$ such that:
-			$$\iota_{v_f} \omega = -df \quad \text{(exact)}$$ %$\in B^1(M)$
-			\small$v_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.
-		\end{defblock}
-		%
-		\begin{defblock}[Poisson Algebra of Observables]
-			$C^\infty(M)$ is a Poisson algebra with
-			$$\{f,g\} = \iota_{v_g} \iota_{v_f} \omega = \omega(v_f,v_g) ~.$$
-		\end{defblock}
-	\end{column}
-\end{columns}
-\end{frame}
-\note[itemize]{
-	\footnotesize
-
-	\item We work in the framework of multisymplectic geometry which is one of the possible generalizations of the well-established field of symplectic geometry.
-
-	\item To recall what symplectic geometry is let me assume a particular point of view: mechanics.
-	\\
-	Idea:"
-	Symplectic geometry is a branch of differential geometry studying symplectic manifolds; it originated as a formalization of the mathematical apparatus of classical mechanics and geometric optics."{\href{https://ncatlab.org/nlab/show/symplectic+geometry}{nlab}}
-
-	Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, ordinary, classical, mechanical systems.
-
-	\item $\theta$ = \emph{tautological 1-form}.
-		$\theta$ evaluated at $p\in T^*Q$ in the fibre of $q\in Q$ and contracted with $v$ coincides with the form $p$ evaluated at $q$ and contracted with the push forward of $v$.
-
-	\item We identify a special class of vector fields.
-		Out of them one can define a Lie bracket.
-
-	\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Multisymplectic geometry in a nutshell}
-	\begin{block}{Historical motivation}
-		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-	\end{block}
-	\vfill	
-	\begin{table}
-		\only<2>{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &  \multicolumn{1}{@{}c@{}}{}              \\
-		\end{tabular}
-
-		}
-		\onslide<3->{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting 
-			\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!10,draw=orange!30,anchor=base]            
-            			(target) {homotopy comomentum map};
-            }
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &
-            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
-               \\
-		\end{tabular}
-		}
-	\end{table}		
-	\vfill
-	\onslide<4->{
-
-	\begin{block}{Scope of the thesis}
-		\begin{itemize}
-			\item[$\bullet$] Develop theory of 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!10,draw=orange!30,anchor=base]            
-            			(base) {homotopy comomentum maps};
-            	}
-            \item[$\bullet$] produce new meaningful examples.
-		\end{itemize}
-	\end{block}
-
-                    \begin{tikzpicture}[overlay,remember picture]
-                    \path[->]<4-> (base.north east) edge[bend right](target.south east);
-                    \end{tikzpicture}
-	}
-
-\end{frame}
-\note[itemize]{
-	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
-	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
-point-like particle constrained to some manifold), it is possible to associate a multisymplectic
-manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}
-
-	\item General ideas basic parallelisms with caveats
-	\item caveat: points in multiphase spaces are not states
-	\item the table hides the duality between geometric and algebraic approaches to the problem.
-	\item 
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Multisymplectic manifolds} %Fragile -->workaround tikzcd
-	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)}]
-	\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
-	\end{defblock}
-	%
-	\begin{defblock}[Non-degenerate $(n+1)$-form]
-		\begin{columns}
-			\begin{column}{.45\linewidth}
-				\centering{
-				The $\omega^\flat$ (flat) bundle map is injective.
-				}
-			\end{column}
-			\begin{column}{.5\linewidth}
-						\vspace{-.5em}
-				\[
-				\begin{tikzcd}[column sep= small,row sep=0ex,
-				/tikz/column 1/.append style={anchor=base east}]
-				    \omega^\flat \colon T M \ar[r]& \Lambda^n T^\ast M \\
-  						 (x,u) \ar[r, mapsto]& (x,\iota_{u} \omega_x)						
-				\end{tikzcd}	
-				\]
-			\end{column}
-		\end{columns}
-	\end{defblock}
-	%
-	\pause
-	\begin{defblock}[Hamiltonian $(n-1)$-forms]
-		\begin{displaymath}
-			\Omega^{n-1}_{ham}(M,\omega) 	:=
-			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
-				\exists \mathscr{v}_\sigma \in \mathfrak{X}(M) ~:~ 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!5,draw=orange!30,anchor=base]            
-            			(target) {$d \sigma = -\iota_{\mathscr{v}_\sigma} \omega$ };
-            	}				
-				~\biggr\} 
-			\end{displaymath}
-	\end{defblock}
-	%
-	%
-	\pause
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!5,draw=orange!30,anchor=base]            
-            	 (base) at ($(current page.east)-(2.25,1.8)$) [rotate=-0,text width=4cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
-		}	
-	\begin{tikzpicture}[overlay,remember picture]
-    	\path[->] (base.west) edge[bend left,red](target.south west);
-    \end{tikzpicture}	
-	\pause
-	\vfill
-	%
-	\begin{block}{Examples:}
-		\vspace{-.5em}
-		\setbeamercovered{transparent}
-		\begin{itemize}[<+->]
-			\item[$\bullet$] $n=1$ \qquad\qquad\qquad $\Rightarrow$\quad $\omega$ is a symplectic form
-			\item[$\bullet$]  $n=(dim(M)-1)$ \quad$\Rightarrow$\quad $\omega$ is a volume form
-			%Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
-			%\item[$\bullet$] Let $G$ a semisimple Lie group and $\langle\cdot,\cdot \rangle$  its killing form.
-Then $\langle [\cdot,\cdot],\cdot \rangle$ extends to a biinvariant multisymplectic form $\omega$.
-			\item[$\bullet$] Let $Q$ a smooth manifold, the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.%
-			\quad
-			\textit{(cfr, \href{https://arxiv.org/abs/physics/9801019}{GIMMSY} construction for classical field theories)}
-		\end{itemize}
-	\end{block}
-
-%
-\end{frame}
-\note[itemize]{
-	\item Multisymplectic ($n$-plectic) geometry is a generalization of symplectic geometry where a closed, non degenerate $n+1$-form $(n\geq 1)$  takes the place of the symplectic 2-form
-
-	\item multisymplectic means \emph{going higher} in the degree of $\omega$
-
-	\item non degeneracy means $\iota_v\omega = 0 \Leftrightarrow v=0$.
-
-	\item examples 
-		\begin{itemize}
-			\item[$\bullet$] 1-plectic $=$ symplectic
-			\item[$\bullet$] Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
-			\item[$\bullet$] The multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.
-		\end{itemize}
-
-	\item We recognize the special class of forms, called Hamiltonian, determining the Hamiltonian vector fields. 
-	Not every $n-1$ form admits an Hamiltonian vector field.
-	When it exists, non degeneracy guarantees unicity.
-
-	\item Observe also that, by degree reason, when $n$ is equal to $1$ or $dim(M)+1$ an injective flat map $\flat$ is also bijective.
-
-	\item It is important to stress that mechanical systems are not the only source instances of this class of of structures. 
-				e.g. any semisimple Lie groups has associated a 2-plectic structure and any oriented $n+1$ dimensional manifold is naturally $n$-plectic.
-
-}
-%---------------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 	\item In mechanical terms, a moment map is a tool associated with a Hamiltonian action of a Lie group on a symplectic manifold, used to construct conserved quantities for the action.(see \ref{frame:HCMMandConserved} in appendix.
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-\begin{frame}[fragile]{Compatibility between gauge transformations and comoment maps}
-	%
-	Consider $(M,\omega)$ \alert{symplectic mfd.}
-	\only<5-11>{ and \alert{\underline{prequantizable}} ($S^1$-bundle $P$, connection $\theta$)}
-	%
-	\begin{center}
-			\includestandalone[width=.8\textwidth]{Pictures/Frame_BigDiagram_symplectic}
-	\end{center}
-	%
-	\vspace{-2em}
-	\begin{minipage}[t][1.7cm][t]{\textwidth}
-	\begin{itemize}
-		\only<1-4>{
-			\item<2-> Given a Symp. mfd. $(M,\omega)$ there is a naturally associated Poisson algebra ...
-			\item<3-> .\alert<+>{... and also a Lie Algebroid}.
-			\item<4-> A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra;
-		}
-		\only<5-6>{
-			\item<5-> Prequantization Bundle $S^1\hookrightarrow P \to M$ with connection $\theta$,
-			\item<5-> "infinitesimal quantomorphisms" $Q(P,\theta):=\lbrace Y \in \mathfrak{X}(P)~|~ \mathcal{L}_Y \theta =0 \}$.
-		}
-		\only<7-11>{
-		\item<7-> Consider a deformed structure $\tilde{\omega}= \omega + d B$ with $B\in C^\infty(M)$;
-		\item<9-> There is a natural isomorphism in the Lie Alg.oids category,
-		\item<11-> Considering $\mathfrak{g}\circlearrowleft M$ preserving $\omega$ and $\tilde{\omega}$ ...
-		}
-		\item<12-> Neglect the prequantization...
-		\vspace{-1em} 
-			\begin{displaymath}
-				\begin{tikzcd}
-					\Psi~:&[-1em] C^{\infty}(M)_\omega \ar[r,"\Psi"]& \Gamma(TM\oplus \mathbb{R})_\omega
-					\\[-2em]
-					& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
-				\end{tikzcd}
-			\end{displaymath}
-	\end{itemize}
-	\end{minipage}
-	\vfill
-	\tcbset{colback=white,
-	colbacktitle=white,
-	colframe=red!70!black,
-	boxrule=1pt,
-	colupper=red!70!black,
-	arc=15pt,
-	}
-	\begin{minipage}[t][1.7cm][t]{\textwidth}
-	\only<6>{ 
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The left square and right triangles commutes!
-			}
-		\end{tcolorbox}
-	}
-	\only<11>{
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The left square and right triangle commute!
-			}
-		\end{tcolorbox}
-	}
-	\only<12>{
-		\vspace{-.75em}
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The central pentagon commutes!
-			}
-		\end{tcolorbox}
-	\vfill
-		\vspace{-.75em}
-		\begin{center}
-		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
-			\alert{
-			\faQuestionCircle \qquad
-				{What happens in the higher (n-plectic) case?}
-			\qquad \faQuestionCircle		
-			}
-		}
-		\end{center}
-	}
-	\end{minipage}
-	%
-\end{frame}
-\note[itemize]{
-	\item The horizontal embedding is  $f \mapsto (v_f,f)$;
-	\item Vertical maps are also known as \emph{Gauge transformations}
-	\item upshot: 
-	\begin{enumerate}
-		\item 
-	\end{enumerate}
 }
@@
 
+%-------------------------------------------------------------------------------------------------------------------------------------------------
 \end{document}

### 2021-07-06 msgauge-temp.tex
Slides, first version.

@@
 
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Symplectic geometry}
-\begin{columns}[T]
-	\begin{column}{.50\linewidth}
-		\centering
-		\textit{ "geometric approach" to mechanics \dots}
-		%
-		\begin{columns}
-			\begin{column}{.50\linewidth}
-				\begin{center}
-					\includegraphics[width=0.8\linewidth]{Pictures/pendulum13}			
-				\end{center}
-			\end{column}	
-			\begin{column}{.50\linewidth}
-				\begin{center}
-					\includegraphics[width=0.45\linewidth]{Pictures/pendulum-phase-space}			
-				\end{center}
-			\end{column}	
-		\end{columns}
-		%
-		\begin{defblock}[Symplectic Manifold]
-			\includestandalone[width=0.95\textwidth]{Pictures/Figure_sym}	
-		\end{defblock}
-		%
-		\begin{exblock}[$M = T^\ast Q$ is symplectic]
-			$\omega = d \theta $ with
-			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
-		\end{exblock}
-	\end{column}
-	\vrule{}
-	\pause
-	\begin{column}{.50\linewidth}
-		\centering
-		\textit{ "algebraic approach" to mechanics \dots}
-		\vspace{1em}	
-		\begin{defblock}[Classical Observables]
-			Unital, associative, commutative algebra $C^\infty(M)$.
-		\end{defblock}
-		%
-		\vspace{1em}
-		\pause
-		\begin{defblock}[Hamiltonian vector fields]
-			$v_f \in \mathfrak{X}(M)$ such that:
-			$$\iota_{v_f} \omega = -df \quad \text{(exact)}$$ %$\in B^1(M)$
-			\small$v_f$ = \emph{Ham.v.f. pertaining to $f\in C^\infty(M)$}.
-		\end{defblock}
-		%
-		\begin{defblock}[Poisson Algebra of Observables]
-			$C^\infty(M)$ is a Poisson algebra with
-			$$\{f,g\} = \iota_{v_g} \iota_{v_f} \omega = \omega(v_f,v_g) ~.$$
-		\end{defblock}
-	\end{column}
-\end{columns}
-\end{frame}
-\note[itemize]{
-	\footnotesize
-
-	\item We work in the framework of multisymplectic geometry which is one of the possible generalizations of the well-established field of symplectic geometry.
-
-	\item To recall what symplectic geometry is let me assume a particular point of view: mechanics.
-	\\
-	Idea:"
-	Symplectic geometry is a branch of differential geometry studying symplectic manifolds; it originated as a formalization of the mathematical apparatus of classical mechanics and geometric optics."{\href{https://ncatlab.org/nlab/show/symplectic+geometry}{nlab}}
-
-	Namely, a sym. mfd. is the geometric structure encoding the phase space of conservative, ordinary, classical, mechanical systems.
-
-	\item $\theta$ = \emph{tautological 1-form}.
-		$\theta$ evaluated at $p\in T^*Q$ in the fibre of $q\in Q$ and contracted with $v$ coincides with the form $p$ evaluated at $q$ and contracted with the push forward of $v$.
-
-	\item We identify a special class of vector fields.
-		Out of them one can define a Lie bracket.
-
-	\item Poisson is a Lie algebra with the extra property of compatibility with the associative product (Leibniz rule)
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Multisymplectic geometry in a nutshell}
-	\begin{block}{Historical motivation}
-		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-	\end{block}
-	\vfill	
-	\begin{table}
-		\only<2>{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &  \multicolumn{1}{@{}c@{}}{}              \\
-		\end{tabular}
-
-		}
-		\onslide<3->{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting 
-			\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!10,draw=orange!30,anchor=base]            
-            			(target) {homotopy comomentum map};
-            }
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &
-            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
-               \\
-		\end{tabular}
-		}
-	\end{table}		
-	\vfill
-	\onslide<4->{
-
-	\begin{block}{Scope of the thesis}
-		\begin{itemize}
-			\item[$\bullet$] Develop theory of 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!10,draw=orange!30,anchor=base]            
-            			(base) {homotopy comomentum maps};
-            	}
-            \item[$\bullet$] produce new meaningful examples.
-		\end{itemize}
-	\end{block}
-
-                    \begin{tikzpicture}[overlay,remember picture]
-                    \path[->]<4-> (base.north east) edge[bend right](target.south east);
-                    \end{tikzpicture}
-	}
-
-\end{frame}
-\note[itemize]{
-	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
-	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
-point-like particle constrained to some manifold), it is possible to associate a multisymplectic
-manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}
-
-	\item General ideas basic parallelisms with caveats
-	\item caveat: points in multiphase spaces are not states
-	\item the table hides the duality between geometric and algebraic approaches to the problem.
-	\item 
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Multisymplectic manifolds} %Fragile -->workaround tikzcd
-	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)}]
-	\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
-	\end{defblock}
-	%
-	\begin{defblock}[Non-degenerate $(n+1)$-form]
-		\begin{columns}
-			\begin{column}{.45\linewidth}
-				\centering{
-				The $\omega^\flat$ (flat) bundle map is injective.
-				}
-			\end{column}
-			\begin{column}{.5\linewidth}
-						\vspace{-.5em}
-				\[
-				\begin{tikzcd}[column sep= small,row sep=0ex,
-				/tikz/column 1/.append style={anchor=base east}]
-				    \omega^\flat \colon T M \ar[r]& \Lambda^n T^\ast M \\
-  						 (x,u) \ar[r, mapsto]& (x,\iota_{u} \omega_x)						
-				\end{tikzcd}	
-				\]
-			\end{column}
-		\end{columns}
-	\end{defblock}
-	%
-	\pause
-	\begin{defblock}[Hamiltonian $(n-1)$-forms]
-		\begin{displaymath}
-			\Omega^{n-1}_{ham}(M,\omega) 	:=
-			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
-				\exists \mathscr{v}_\sigma \in \mathfrak{X}(M) ~:~ 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!5,draw=orange!30,anchor=base]            
-            			(target) {$d \sigma = -\iota_{\mathscr{v}_\sigma} \omega$ };
-            	}				
-				~\biggr\} 
-			\end{displaymath}
-	\end{defblock}
-	%
-	%
-	\pause
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!5,draw=orange!30,anchor=base]            
-            	 (base) at ($(current page.east)-(2.25,1.8)$) [rotate=-0,text width=4cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
-		}	
-	\begin{tikzpicture}[overlay,remember picture]
-    	\path[->] (base.west) edge[bend left,red](target.south west);
-    \end{tikzpicture}	
-	\pause
-	\vfill
-	%
-	\begin{block}{Examples:}
-		\vspace{-.5em}
-		\setbeamercovered{transparent}
-		\begin{itemize}[<+->]
-			\item[$\bullet$] $n=1$ \qquad\qquad\qquad $\Rightarrow$\quad $\omega$ is a symplectic form
-			\item[$\bullet$]  $n=(dim(M)-1)$ \quad$\Rightarrow$\quad $\omega$ is a volume form
-			%Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
-			%\item[$\bullet$] Let $G$ a semisimple Lie group and $\langle\cdot,\cdot \rangle$  its killing form.
-Then $\langle [\cdot,\cdot],\cdot \rangle$ extends to a biinvariant multisymplectic form $\omega$.
-			\item[$\bullet$] Let $Q$ a smooth manifold, the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.%
-			\quad
-			\textit{(cfr, \href{https://arxiv.org/abs/physics/9801019}{GIMMSY} construction for classical field theories)}
-		\end{itemize}
-	\end{block}
-
-%
-\end{frame}
-\note[itemize]{
-	\item Multisymplectic ($n$-plectic) geometry is a generalization of symplectic geometry where a closed, non degenerate $n+1$-form $(n\geq 1)$  takes the place of the symplectic 2-form
-
-	\item multisymplectic means \emph{going higher} in the degree of $\omega$
-
-	\item non degeneracy means $\iota_v\omega = 0 \Leftrightarrow v=0$.
-
-	\item examples 
-		\begin{itemize}
-			\item[$\bullet$] 1-plectic $=$ symplectic
-			\item[$\bullet$] Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
-			\item[$\bullet$] The multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.
-		\end{itemize}
-
-	\item We recognize the special class of forms, called Hamiltonian, determining the Hamiltonian vector fields. 
-	Not every $n-1$ form admits an Hamiltonian vector field.
-	When it exists, non degeneracy guarantees unicity.
-
-	\item Observe also that, by degree reason, when $n$ is equal to $1$ or $dim(M)+1$ an injective flat map $\flat$ is also bijective.
-
-	\item It is important to stress that mechanical systems are not the only source instances of this class of of structures. 
-				e.g. any semisimple Lie groups has associated a 2-plectic structure and any oriented $n+1$ dimensional manifold is naturally $n$-plectic.
-
-}
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Lie $\infty$-algebra of Observables}
-\begin{frame}[fragile,t]{Lie $\infty$-algebra of Observables (higher observables) }
-	Let be $(M,\omega)$ a $n$-plectic manifold.
-	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)}]
-		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
-		\vspace{-2.5em}
-		\begin{center}
-		\ifHandout
-			\includestandalone{Pictures/Figure_Observables}	
-		\else
-			\includestandalone{Pictures/Frame_Observables}
-		\fi				
-		\end{center}
-		\onslide<2->{
-			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
-			\vspace{-1.5em}
-			\begin{center}
-				\includestandalone{Pictures/Equation_Multibracket}	
-			\end{center}
-		}
-		%
-	\end{defblock}
-  	\vfill
-	\onslide<3->{
-		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
-	\vfill
-	\begin{columns}
-		\hfill
-		\begin{column}{.11\linewidth}	
-			If $n>1$:
-
-		\end{column}	
-		\begin{column}{.8\linewidth}
-		\begin{itemize}
-			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
-			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
-			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
-			\hspace*{4.25em}
-			 Jacobi equation \emph{up to homotopies}.
-		\end{itemize}		
-		\end{column}		
-	\end{columns}
-	}
-  \end{frame}
- \note[itemize]{
-	\item if symplectic manifolds are the symmetric take on mechanics, Poisson algebras are the algebraic counterpart.
- 	\item A Lie algebra is associated to an ordinary symplectic manifold (its Poisson algebra).
-	%(Underlying this is a Lie algebra, whose Lie bracket is the Poisson bracket.)
-	Similarly, one associates an Lie-$n$ algebra to any $n$-plectic manifold.
- 	% https://ncatlab.org/nlab/show/n-plectic+geometry 	 
- 	 %https://ncatlab.org/nlab/show/Poisson+bracket+Lie+n-algebra
-	 \item Basically, the higher observables algebra is a chunk of the de Rham complex of $M$ with inverted grading( convention employed here) and an extra structure called "multibrackets".
- 	\item ( In the 1-plectic case it reduces to the corresponding Poisson algebra of classical observables)
- 	\item Rogers associated to any n-plectic mfd a $L\-\infty$ algebra, Zambon generalized it to the pre-n-plectic case.
- 	\item Recognize in the definition of $\{\cdot,\ldots,\cdot\}_k$ the contraction with hamiltonian fields $v_\sigma$ w.r.t. $\sigma$.
-  	\item Note $	\iota_{v_{\sigma_1}}\cdots\iota_{v_{\sigma_k}} = (-)^{(k-1)+(k-2)+\dots+1}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}} = (-)^{\frac{k(k-1)}{2}}\iota_{v_{\sigma_k}}\cdots\iota_{v_{\sigma_1}}$
- 	The definition usually find in literature of Rogers multibrackets involves the coefficient $ (-)^{\frac{k(k-1)}{2}} = -\varsigma(k-1) = (-)^{k+1} \varsigma(k)$.
-  \item higher observables is Special instance of a more general object  called $L\-\infty$ Algebra...
- }
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Homotopy comomentum maps}\label{frame:hcmm-main}
-\begin{frame}[fragile]{Homotopy comomentum maps}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
-	\vfill
-	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)}]
-		\ifHandout
-			\includestandalone{Pictures/Figure_Lifting}
-		\else
-			\includestandalone{Pictures/Frame_Lifting}
-		\fi					
-	\end{defblock}
-	\onslide<4->{
-	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
-			%
-			HCMM is a sequence of (graded-skew) multilinear maps:
-			\begin{displaymath}
-				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
-				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
-			\end{displaymath}
-			\emph{fulfilling:}%\emph{such that:}
-			\begin{itemize}
-				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
-				\item<6-> $d f_k (p) = f_{k-1} (
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=green!5,draw=green!30,anchor=base]            
-            			(target) {$\partial $ };
-            	}				
-				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
-				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
-			\end{itemize}
-		\onslide<7->{
-			\tikz[overlay,remember picture]
-			{
-				\node[rounded corners,
-	                 draw=green!30,anchor=base]            
-	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
-			}	
-		\begin{tikzpicture}[overlay,remember picture]
-	    	\path[->] (base.west) edge[bend right,green](target.north east);
-	    \end{tikzpicture}
-	    }
-	\end{lemblock}	
-	}
-	\vfill
-\end{frame}
-\note[itemize]{
-	\item  An infinitesimal symmetry is a lie algebra morphism such that $\mathcal{L}_{v_x} \omega = 0 ~ \forall x \in \mathfrak{g}$.
-	\\ (It is also call an infinitesimal multisymplectic action and $v_x$ is the infinitesimal generator of the action, corresponding to $x \in \mathfrak g$.) 
-	\item Essentially, admitting a comoment maps mean that $v$ acts via Hamiltonian vector fields.
-	\item In mechanical terms, a moment map is a tool associated with a Hamiltonian action of a Lie group on a symplectic manifold, used to construct conserved quantities for the action.(see \ref{frame:HCMMandConserved} in appendix.
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-\begin{frame}[fragile]{Compatibility between gauge transformations and comoment maps}
-	%
-	Consider $(M,\omega)$ \alert{symplectic mfd.}
-	\only<5-11>{ and \alert{\underline{prequantizable}} ($S^1$-bundle $P$, connection $\theta$)}
-	%
-	\begin{center}
-			\includestandalone[width=.8\textwidth]{Pictures/Frame_BigDiagram_symplectic}
-	\end{center}
-	%
-	\vspace{-2em}
-	\begin{minipage}[t][1.7cm][t]{\textwidth}
-	\begin{itemize}
-		\only<1-4>{
-			\item<2-> Given a Symp. mfd. $(M,\omega)$ there is a naturally associated Poisson algebra ...
-			\item<3-> .\alert<+>{... and also a Lie Algebroid}.
-			\item<4-> A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra;
-		}
-		\only<5-6>{
-			\item<5-> Prequantization Bundle $S^1\hookrightarrow P \to M$ with connection $\theta$,
-			\item<5-> "infinitesimal quantomorphisms" $Q(P,\theta):=\lbrace Y \in \mathfrak{X}(P)~|~ \mathcal{L}_Y \theta =0 \}$.
-		}
-		\only<7-11>{
-		\item<7-> Consider a deformed structure $\tilde{\omega}= \omega + d B$ with $B\in C^\infty(M)$;
-		\item<9-> There is a natural isomorphism in the Lie Alg.oids category,
-		\item<11-> Considering $\mathfrak{g}\circlearrowleft M$ preserving $\omega$ and $\tilde{\omega}$ ...
-		}
-		\item<12-> Neglect the prequantization...
-		\vspace{-1em} 
-			\begin{displaymath}
-				\begin{tikzcd}
-					\Psi~:&[-1em] C^{\infty}(M)_\omega \ar[r,"\Psi"]& \Gamma(TM\oplus \mathbb{R})_\omega
-					\\[-2em]
-					& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
-				\end{tikzcd}
-			\end{displaymath}
-	\end{itemize}
-	\end{minipage}
-	\vfill
-	\tcbset{colback=white,
-	colbacktitle=white,
-	colframe=red!70!black,
-	boxrule=1pt,
-	colupper=red!70!black,
-	arc=15pt,
-	}
-	\begin{minipage}[t][1.7cm][t]{\textwidth}
-	\only<6>{ 
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The left square and right triangles commutes!
-			}
-		\end{tcolorbox}
-	}
-	\only<11>{
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The left square and right triangle commute!
-			}
-		\end{tcolorbox}
-	}
-	\only<12>{
-		\vspace{-.75em}
-		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-			\color{blue}{
-			The central pentagon commutes!
-			}
-		\end{tcolorbox}
-	\vfill
-		\vspace{-.75em}
-		\begin{center}
-		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
-			\alert{
-			\faQuestionCircle \qquad
-				{What happens in the higher (n-plectic) case?}
-			\qquad \faQuestionCircle		
-			}
-		}
-		\end{center}
-	}
-	\end{minipage}
-	%
-\end{frame}
-\note[itemize]{
-	\item The horizontal embedding is  $f \mapsto (v_f,f)$;
-	\item Vertical maps are also known as \emph{Gauge transformations}
-	\item upshot: 
-	\begin{enumerate}
-		\item 
-	\end{enumerate}
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
-	Consider now $\omega$ \alert{$n$-plectic}
-	\vfill
-	\begin{center}
-		\includestandalone[width=.8\textwidth]{Pictures/Frame_Embedding_Diagram_k-plectic_V1}
-	\end{center}
-	\vfill
-	\only<1-3>{
-	\begin{itemize}
-		\item<2-> Higher analogue of the Courant algebroid $\rightsquigarrow$ \alert{\emph{Vinogradov algebroid}}
-			\begin{displaymath}
-			E^n = \left(TM\oplus\bigwedge^{n-1}T^\ast M \right)
-			\end{displaymath}
-		\item<3->  Vin. alg.oids are $NQ$-manifolds ($L_\infty$-algebroids).
-		\\ Associated $L_\infty$-algebra on the graded vector space
-		\begin{displaymath}\label{eq:VSpace}
-			{\mathcal{V}^k} =
-			\begin{cases}
-				\mathfrak{X}(M)\oplus \Omega^{n-1}(M)  &\quad k=0,\\
-				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
-			\end{cases}
-		\end{displaymath}
-	\end{itemize}
-	}
-
-	\only<4->{
-	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2021}.]
-	\begin{itemize}[leftmargin=0pt]
-		\item[$\cdot$]<4-> 
-			consider the graded vector subspace $\mathcal{A}$
-			\begin{displaymath}
-			\mathclap{
-			{\mathcal{A}^k} =
-			\begin{cases}
-		\left.\left\lbrace
-		\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
-		~ \right\vert ~
-		\iota_X \omega = -d \alpha\right\rbrace
-&\quad k=0,\\
-				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
-			\end{cases}			
-			}
-			\end{displaymath}						
-		\item[$\cdot$]<5-> 
-			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
-		\item[$\cdot$]<6->
-
-			$L_\infty(M,\omega) \cong 
-				(\mathcal{A},\pi) \color{blue}\cong\color{black}
-				(\mathcal{A},\mu) \hookrightarrow
-				L_\infty(E^n,\omega)$
-	\end{itemize}
-	\end{thmblock}
-	}
-	\only<6->{
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!1,draw=orange!30,anchor=base]            
-            	 (base) at ($(current page.east)-(2.25,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
-            	 Complete proof\\
-            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
-            	 }}};
-		}			
-	}
-
-\end{frame}
-\note{}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Compatibility with Gauge transformations}
-	Consider now $\omega$ \alert{n-plectic} \quad and \alert{$\tilde{\omega}=\omega + d B$}:
-	\vfill
-	%
-	\begin{center}
-		\includestandalone[width=.8\textwidth]{Pictures/Frame_Gauge_Diagram_k-plectic}
-	\end{center}	
-	%
-	\vfill
-	%
-
-	\begin{itemize}
-	\only<1-3>{
-		\item<2-> Vinogradov alg.oids w.r.t cohomologous twisting closed forms are isomorphic.
-		\item<3-> Induced isomorphism at the level of $L_\infty$-algebras
-	}
-	\only<4->{
-		\item<4-> Consider a Lie algebra action $\mathfrak{g}\to \mathfrak{X}(M)$ admitting HCMM w.r.t $\omega$ and $\tilde{\omega}$
-	}
-	\end{itemize}
-
-	\vfill
-	\tcbset{colback=white,
-		colbacktitle=white,
-		colframe=blue!70!black,
-		boxrule=1pt,
-		colupper=blue!70!black,
-		arc=15pt,
-		}
-	\onslide<5->{
-	\begin{tcolorbox}[sidebyside,righthand width=.75\linewidth]
-		Thm: \cite{Miti2021}
-		\tcblower
-		\color{blue}
-The central square commutes. 
-			\\\emph{(On the nose, not "up to homotopies")}.
-	\end{tcolorbox}	
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!1,draw=orange!30,anchor=base]            
-            	 (base) at ($(current page.east)-(1.75,4)$) [rotate=-0,text width=3cm,align=center] { \footnotesize{\color{red}{
-            	 Complete proof\\
-            	 \faWarning ~ up to $n\geq 4$! ~ \faWarning 
-            	 }}};
-		}
-
-	}
-
-\end{frame}
-\note[itemize]{
-	\item Our results can be seen as a tiny step toward  undestanding the analogue of prequantization in the setting of multisymplectic geometry (hence field theory).
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
 \end{document}

### 2021-07-07 msgauge-intro.tex
Slight modifications to side notes.

@@
 %- D0cum3nt ----------------------------------------------------------------------------------------------
-\documentclass[beamer,10pt]{standalone}   
-%\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
+%\documentclass[beamer,10pt]{standalone}   
+\documentclass[beamer,10pt,handout]{standalone}  \Handouttrue
 
@@
 \usetikzlibrary{shapes}
+
+%--Custom command----------------------------------------------------------------------------------------
+\providecommand{\pairing}{\langle\cdot,\cdot\rangle}
+\providecommand{\vHam}{\mathscr{v}}
 
@@
 			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
-				\exists \mathscr{v}_\sigma \in \mathfrak{X}(M) ~:~ 
+				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
 				\tikz[baseline,remember picture]{\node[rounded corners,
                         fill=orange!5,draw=orange!30,anchor=base]            
-            			(target) {$d \sigma = -\iota_{\mathscr{v}_\sigma} \omega$ };
+            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
             	}				
@@
 					\lbrace \sigma_1, \sigma_2 \rbrace =			
-					~ - \iota_{\mathscr{v}_1}\iota_{\mathscr{v}_2} \omega 
+					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
 				\end{displaymath}			
@@
 				\llbracket \sigma_1, \sigma_2 \rrbracket =
-				~ \mathcal{L}_{\mathscr{v}_1} \sigma_2
+				~ \mathcal{L}_{\vHam_1} \sigma_2
 				~.					
@@
  \item See \cite[\S 7.2]{Rogers2010} about the comparison of these two algebraic structures.
+ \item Notice that the failure of skew-symmetricity is measured by
+ \begin{align*}
+ 	A(\sigma_1,\sigma_2) 
+ 	=&~
+ 	 2~\llbracket \sigma_1, \sigma_2\rrbracket +  \llbracket \sigma_2, \sigma_1\rrbracket
+ 	 \\
+ 	 =&~ d \circ\langle\sigma_1,\sigma_2\rangle_+
+ \end{align*}
+ (Compare with the \href{https://en.wikipedia.org/wiki/Courant_bracket\#Dorfman_bracket}{Dorfmann bracket}.)
+
+ \item Notice that the antisymmetrization of $\llbracket \cdot, \cdot \rrbracket$ equates $\lbrace \cdot,\cdot \rbrace$ modulo homotopy:
+ \begin{align*}
+  \llbracket \sigma_1,\sigma_2 \rrbracket  \circ 	\mathcal{A}
+  =&~
+  \frac{\mathcal{L}_{\vHam_1}\sigma_2 - \mathcal{L}_{\vHam_2}\sigma_1}{2} 
+  \\
+  =&~ 
+  \frac{1}{2}( d (\iota_{\vHam_1}{\sigma_2} - \iota_{\vHam_2}{\sigma_1} )
+  +\frac{1}{2}(-\iota_{\vHam_1}\iota_{\vHam_2}\omega + \iota_{\vHam_2}\iota_{\vHam_1}\omega) 
+  \\
+  =&~
+  \lbrace \sigma_1, \sigma_2 \rbrace + d \circ \langle\sigma_1,\sigma_2\rangle_-
+  \\
+  =&~
+  [\sigma_1,\sigma_2]_\omega
+ \end{align*}
+ where the last bracket is given by the Vinogradov algebroid Binary bracket.
 }
@@
 	\begin{tikzpicture}
-		\node [draw,ellipse callout, minimum height=10em,minimum width=33em,callout relative pointer={(-2,-.5)}] (L1) {};
+		\node [draw,ellipse callout,red, minimum height=10em,minimum width=30em,callout relative pointer={(-2,-.5)}] (L1) {};
 		\node [text width=25em,text centered] (L2) {
-			Broad general question:\\
+			\textcolor{red}{Broad \emph{general} question:}
+			\\
+			\medskip
 			What is the corresponding	 "correct" notion of observables in multisymplectic geometry?	
@@
 	\begin{tikzpicture}
-		\node [draw,ellipse callout, minimum height=10em,minimum width=33em,callout relative pointer={(2,-.5)}] (L1) {};
+		\node [draw,blue,ellipse callout, minimum height=10em,minimum width=30em,callout relative pointer={(2,-.5)}] (L1) {};
 		\node [text width=25em,text centered] (L2) {
-			Specific focused question:
+			\textcolor{blue}{Specific \emph{technical} question}:
 			\\
-			To what extent the compatibility diagram between gauge transformation and comomentum maps extend to the $n$-plectic case?
+			\medskip
+			How the compatibility diagram between \emph{gauge transformation}
+			and \emph{comomentum maps} extends to the $n$-plectic case?
 		};

### 2021-07-07 msgauge-intro.tex
Section 1 almost done.

@@
 		\begin{exblock}[$M = T^\ast Q$ is symplectic]
-			$\omega = d \theta $ with
+			with $\omega = d \theta $ given by
 			$$ \left.\theta\right\vert_{(q,p)} (v) = p (\pi_\ast v) ~.$$
@@
 	\vfill
+	\pause
+	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]
+		\color{red}
+		\begin{columns}[T]
+			\begin{column}{.20\linewidth}
 				\begin{center}
-	\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
-		\alert{
-		\faWarning \qquad
-			{The lack of a satisfactory notion of observables hindered the spread of this formalism.}	
-		\qquad \faWarning		
-		}
-	}
+					\huge
+					\faWarning
 				\end{center}
-
+			\end{column}			
+			\begin{column}{.60\linewidth}
+				\begin{center}
+					The lack of a satisfactory notion of observables hindered the spread of this formalism.
+				\end{center}
+			\end{column}			
+			\begin{column}{.20\linewidth}
+				\begin{center}
+					\huge
+					\faWarning
+				\end{center}
+			\end{column}			
+		\end{columns}
+	\end{tcolorbox}
 	\vfill
+	\pause
+	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue,dashed}]
+		\color{blue}
+		\begin{columns}[T]
+			\begin{column}{.20\linewidth}
 				\begin{center}
-	\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
-		\alert{
-		\faQuestionCircle \qquad
+					\huge
+					\faQuestionCircle
+				\end{center}
+			\end{column}			
+			\begin{column}{.60\linewidth}
+				\begin{center}
 					{Why observables are so crucial?\qquad \qquad Quantization!}	
-		\qquad \faQuestionCircle		
-		}
-	}
 				\end{center}
+			\end{column}			
+			\begin{column}{.20\linewidth}
+				\begin{center}
+					\huge
+					\faQuestionCircle
+				\end{center}
+			\end{column}			
+		\end{columns}
+	\end{tcolorbox}
 

### 2021-07-08 msgauge-multisym.tex
Section 3, first draft.

@@
 \usepackage{multicol}
+\DeclareMathOperator{\varv}{\mathscr{v}}
 
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Vinogradov Algebroids}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}{Vinogradov Algebroids}
+	\begin{defblock}[Vinogradov algebroid (higher Courant)]
+		\includestandalone[width=0.95\textwidth]{Pictures/Figure_vinogradov}	
+	\end{defblock}
+
+	\begin{itemize}
+		\item $(n=1) ~ \Rightarrow$ standard twisted \emph{Lie algebroid};
+		\item $(n=2) ~ \Rightarrow$ standard twisted \emph{Courant algebroid};
+	\end{itemize}
+
+\end{frame}
+\note[itemize]{
+\item Att, questa definizione sarebbe lo standard twisted. E' possibile trovare in letteratura definizioni piu' generali corrispondenti alla nozione di Courant algebroid in astratto.
+}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}{Vinogradov $L_\infty$-algebra}
+	Vin. alg.oids are $NQ$-manifolds ($L_\infty$-algebroids).
+	$\quad\Rightarrow\quad$ 
+	Associated $L_\infty$-algebra.
+
+	\begin{defblock}[Vinogradov $L_\infty$-algebra \cite{Zambon2012}]
+		\includestandalone[width=0.95\textwidth]{Pictures/Figure_vinogradov-Linfty}	
+	\end{defblock}
+	\vfill
+	\only<6->{
+		\tikz[overlay,remember picture]
+		{
+			\node[rounded corners,
+                 fill=gray!1,draw=gray!30,anchor=base]            
+            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] { \footnotesize{\color{gray}{
+            	 $e_i = \pair{X_i}{\alpha_i} \in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)$ 
+            	 \quad~,\qquad
+            	 $f_i \in \bigoplus_{k=0}^{n-2}\Omega^k(M)$.
+            	 }}};
+		}			
+	}
+
+\end{frame}
+\note[itemize]{
+	\item The actions of non vanishing multi-brackets (up to permutations of the entries) on arbitrary vectors
+are given in the slide.
+	\item $\mu_2 \left(e_1,e_2\right) 	= [e_1,e_2]_\omega 
+			= \pair{[X_1,X_2]}{\dd \langle e_1, e_2\rangle_- 
+			+ (\iota_{X_1}\dd\alpha_2 - \iota_{X_2}\dd\alpha_1 + \iota_{X_1}\iota_{X_2}\omega)}$
+	\item $				\mu_2 \left(e_1,f_2\right) = -\mu_2(f_2,e_1) = 
+				\frac{1}{2} \mathcal{L}_{X_1} f_2 = \langle e_1, \dd f_2 \rangle_-$
+	\item $k$-ary bracket for $k \ge 3$ an \emph{odd} integer:	 
+		\begin{equation}\label{eq:VinoMultibrakAllaZambon_1}
+			\begin{split}
+				\mu_k(\varv_0,\cdots,\varv_{k-1})
+				=&
+				\left(\sum_{i=0}^{k-1} {(-)^{i-1}\mu_k(f_i+\alpha_i,X_0,\dots,\widehat{X_i},\dots,X_{k-1})}\right)
+				+\\
+				&+(-)^{\frac{k+1}{2}} \cdot k \cdot B_{k-1} \cdot 
+				\iota_{X_{k-1}}	\dots \iota_{X_{0}} \omega			
+				~;
+			\end{split}
+		\end{equation}
+		where 
+		\begin{equation}\label{eq:VinoMultibrakAllaZambon_2}
+			\begin{split}
+			\mu_k&(f_0+\alpha_0,X_1,\dots,X_{n-1}) =
+			\\
+			&=
+			~c_k
+			\sum_{1\le i<j\le k-1}(-1)^{i+j+1}\iota_{X_{k-1}}\dots   
+  			\widehat{\iota_{X_{j}}}\dots \widehat{\iota_{X_{i}}}\dots
+				\iota_{X_{1}} ~ [f_0+\alpha_0,X_i,X_j]_3~.
+			\end{split}
+		\end{equation}			
+In the above formula,		$[\cdot,\cdot,\cdot]_3 = -T_0$ denotes the ternary bracket %$\mu_3$ 
+associated to the untwisted ($\omega=0$) Vinogradov Algebroid, and $c_k$ is a numerical constant
+		\begin{equation}\label{eq:UglyCoefficient}
+			c_k= (-)^{\frac{k+1}{2}}\frac{12~B_{k-1}}{(k-1)(k-2)}.
+		\end{equation}
+}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Rogers embedding}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
 \begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
@@
 	\only<1-3>{
-	\begin{itemize}
-		\item<2-> Higher analogue of the Courant algebroid $\rightsquigarrow$ \alert{\emph{Vinogradov algebroid}}
-			\begin{displaymath}
-			E^n = \left(TM\oplus\bigwedge^{n-1}T^\ast M \right)
-			\end{displaymath}
-		\item<3->  Vin. alg.oids are $NQ$-manifolds ($L_\infty$-algebroids).
-		\\ Associated $L_\infty$-algebra on the graded vector space
-		\begin{displaymath}\label{eq:VSpace}
-			{\mathcal{V}^k} =
-			\begin{cases}
-				\mathfrak{X}(M)\oplus \Omega^{n-1}(M)  &\quad k=0,\\
-				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
-			\end{cases}
-		\end{displaymath}
-	\end{itemize}
+		.
 	}
@@
 
+\subsection{Compatibility with Gauge transformations}
 %-------------------------------------------------------------------------------------------------------------------------------------------------

### 2021-07-09 msgauge-multisym.tex
Bibliography tidied up.

@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
+\begin{frame}[fragile,t]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
 	Consider now $\omega$ \alert{$n$-plectic}
@@
 	\vfill
-	\only<1-3>{
-		.
-	}
-
+	\begin{minipage}[t][8.5em][t]{\textwidth}
 	\only<4->{
@@
 	}
-
+	\end{minipage}
 \end{frame}
-\note{}
+\note[itemize]{
+	\item this is the "work in progress" part of the preprint.
+	\begin{itemize}
+		\item[-] In the 1-plectic case is extremely simple to check.
+		\item[-] The 2-plectic case has been constructed by Rogers in \cite{Rogers2010}.
+		\item[-] Argument about existence by Ritter and Saemann \cite{Ritter2015}.
+	\end{itemize}
+}
 %-------------------------------------------------------------------------------------------------------------------------------------------------

### 2021-07-09 msgauge-intro.tex
Bibliography tidied up.
Refinenments...

@@
 \outline
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{(Multi)-symplectic: mechanical perspective}
 %-------------------------------------------------------------------------------------------------------------------------------------------------
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{From Symplectic to MultiSymplectic (mechanical perspective)}
+\begin{frame}[t]{From Symplectic to MultiSymplectic (mechanical perspective)}
 	\begin{block}{Historical motivation}
@@
 		\begin{itemize}
-		 \item[•] Kijowski and W. Tulczyjew \cite{Kijowski1979}; %(1979)
+		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
 		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
@@
 	\pause
+	\tcbset{colback=white,
+		colbacktitle=white,
+		colframe=red!70!black,
+		boxrule=1pt,
+		colupper=red!70!black,
+		arc=15pt}
 	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]
@@
 			\begin{column}{.60\linewidth}
+				\vspace{-.4em}
 				\begin{center}
@@
 				\begin{center}
+					\vspace{-.4em}
 					{Why observables are so crucial?\qquad \qquad Quantization!}	
@@
 
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Observability}
 %-------------------------------------------------------------------------------------------------------------------------------------------------
@@
 		\pause
+		\setlength{\belowdisplayskip}{5pt}
 		\begin{column}{.50\linewidth}
@@
 				\end{displaymath}			
-				\vspace{.4em}
 				can be "completed" to a \\ $L_\infty-algebra$.
@@
 			\end{displaymath}		
-				\vspace{.4em}
 				can be "completed" to a \\ DG-Leibniz algebra.
@@
 	\vfill
+	\pause
 	\begin{tikzpicture}
@@
 \note[itemize]{
-	\item
+	\item Non ho una risposta soddifacente alla domanda generale. Bisogna procedere per gradi.
+	\item l'obbiettivo di questo lavoro con Marco è di stabilire quanto della seguente situazione si estende nel caso multisimplettico.
+	\item It is possible to relate the observables algebras of two gauge-related multisymplectic structures (in he same cohomology class)
 }

### 2021-07-09 msgauge-multisym.tex
Refinenments...

@@
 	\vfill
-	\only<6->{
+	\only<2->{
 		\tikz[overlay,remember picture]
@@
 \begin{frame}[fragile,t]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
-	Consider now $\omega$ \alert{$n$-plectic}
+	Consider now $\omega$ \alert{$n$-plectic}~.
 	\vfill
@@
 \note[itemize]{
-	\item this is the "work in progress" part of the preprint.
+	\item Esiste un embedding tale per cui il pentagono commuta?
+	\item this is the "work in progress" part of the preprint. Previous partial results:
 	\begin{itemize}
@@
 \begin{frame}{Compatibility with Gauge transformations}
-	Consider now $\omega$ \alert{n-plectic} \quad and \alert{$\tilde{\omega}=\omega + d B$}:
+	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega + d B$}:
 	\vfill

### 2021-12-12 Pictures/hyb-Frame_Diagram_checkpoint.tex
Talk - Hybrid version complete up to spell check.

%+------------------------------------------------------------------------+
%| Diagram: Kiddo Diagram - k-plectic case
%| Author: Antonio miti
%+------------------------------------------------------------------------+

\documentclass[beamer,handout]{standalone}
\usepackage{tikz-cd}
\usepackage{mathtools}
\usepackage{amsfonts}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{cd, fit}

	%Credit: https://tex.stackexchange.com/questions/99119/beamer-problematic-use-of-visible-and-only-in-combination-with-tikz-to-draw-a
  \tikzset{
    invisible/.style={opacity=0},
    visible on/.style={alt=#1{}{invisible}},
    alt/.code args={<#1>#2#3}{%
      \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}} % \pgfkeysalso doesn't change the path
    },
  }
\definecolor{grey}{rgb}{0.30, 0.30, 0.30}

\begin{document}
	\begin{tikzcd}[
		column sep= small,row sep=small,
		/tikz/execute at end picture={
    		\node (large) [rectangle,dashed, draw, fit=(A1) (A2) (A3),label=below:{\scriptsize$L_\infty$-algebras cat.}] {};
  		}]		
		|[visible on=<1>]| \color{grey}{(M,\omega)} 
		\ar[drr,grey,visible on=<1>,rightsquigarrow,"\text{observables}"]
		\ar[rrrr,grey,visible on=<1>,rightsquigarrow,"\text{twisted standard Vinogradov algebroid}"]
		\ar[dddd,grey,visible on=<1>,rightsquigarrow,sloped,"\text{gauge transf.}"']
		&[-1.5em] & &[2em] 
		&[-3em] |[visible on=<1>]| \color{grey}{(E^n,\rho,\langle\cdot,\cdot\rangle,[\cdot,\cdot]_\omega)}
		\ar[dl,grey,visible on=<1>,rightsquigarrow]
%		\ar[dddd,grey,visible on=<4->,sloped,"\cong","\text{B-transf.}"']
%
	\\
%
		& \phantom{\big(}
		& |[visible on=<1->,alias=A1]| L_{\infty}(M,\omega)
		\ar[r,visible on=<3->,line width=0.8pt,color=blue!60!black,"\Psi"]
		\ar[ddr,visible on=<5->,phantom,sloped,line width=0.8pt,color=red!60!black,"\mathbf\circlearrowright"]
		& |[visible on=<1->]| L_{\infty}\big(E^n,\omega\big)
		\ar[dd,sloped,line width=0.8pt,color=green!60!black,"\cong", visible on=<4->]
		&
%		 
	\\
%
		&|[alias=A2]|\mathfrak{g} \ar[ur,visible on=<1->,sloped,"(f)"]\ar[dr,visible on=<1->,sloped,"(\tilde{f})"']& & & 
%
	\\
%
		& &|[visible on=<1->]| L_{\infty}(M,\tilde{\omega})
		\ar[r,visible on=<3->,line width=0.8pt,color=blue!60!black,"\Psi"]& 
		|[visible on=<1->,alias=A3]| L_{\infty}\big(E^n,{\tilde{\omega}}\big)
		&
%		
	\\
%	
		|[visible on=<1>]| \color{grey}{(M,\tilde{\omega})}
		\ar[rrrr,grey,visible on=<1>,rightsquigarrow,"\text{ }"]
		\ar[urr,grey,visible on=<1>,rightsquigarrow,"\text{ }"]
		& \phantom{\big(} & & 
		& |[visible on=<1>]| \color{grey}{(E^n,[\cdot,\cdot]_{\tilde{\omega}})}
		\ar[ul,grey,visible on=<1>,rightsquigarrow]
 	\end{tikzcd}

\end{document}

		\only<6->{(M,\tilde{\omega}) \ar[rrrr,rightsquigarrow,"\text{}"]
		\ar[urr,rightsquigarrow,"\text{observables}"] }
		& \phantom{\big(} & & 
		& \only<6->{(TM\oplus\bigwedge^{k-1}T^\ast M,\rho,\langle\cdot,\cdot\rangle,[\cdot,\cdot]_{\tilde{\omega}}) \ar[ul,rightsquigarrow] }
 	\end{tikzcd}

### 2021-12-22 abstract.tex
Added abstract - submitted to UMI phd day.

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{hyperref}

\title{
Gauge transformations of multisymplectic manifolds and $L_\infty$ observables
}
\author{\href{https://dmf.unicatt.it/miti/}{Antonio Michele Miti}}
\date{
	Max Planck Institute for Mathematics
	\\[.2em]
	\today
}

\begin{document}

\maketitle
\begin{abstract}
Multisymplectic manifolds are a straightforward generalization of symplectic manifolds where closed non-degenerate k-forms are considered in place of 2-forms.
A natural theme that arises when dealing with both symplectic and multisymplectic structures is investigating the relationship between gauge-related multisymplectic manifolds, i.e. endowed with different multisymplectic forms lying in the same cohomology class.

This talk will focus on the L-infinity algebras of observables associated with a pair of gauge-related multisymplectic manifolds.
To date, no canonical correspondence is known between two gauge-related observables algebras.
However, it can be possible to exhibit a compatibility relation between those observables that are momenta of corresponding homotopy moment maps (the higher analogue of a moment map in the multisymplectic setting).

Although this construction is essentially algebraic in nature, it also admits a geometric interpretation when declined to the particular case of pre-quantizable symplectic forms. The latter case provides some evidence that this construction may be related to the higher analogue of geometric quantization for integral multisymplectic forms.

This talk is based on ongoing joint work with Marco Zambon.
\end{abstract}

\end{document}

### 2024-02-19 msgauge-Caprarola.tex
Revision for Caprarola 24- Todo slides.

%+----------------------------------------------------------------------------+
%| SLIDES: 
%|
%| Contents:	- 60 minutes, 
%|
%| Author: Antonio miti
%| Place: Caprarola, VT
%| Date: 2/3/24
%+----------------------------------------------------------------------------+

%- D0cum3nt ----------------------------------------------------------------------------------------------
\documentclass[10pt]{beamer}

%- Packages -------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usepackage{multicol}
\usepackage{stmaryrd}
\usepackage{animate}
\usetikzlibrary{positioning, arrows}
\usetikzlibrary{shapes}
\usepackage{fontawesome}

%--Beamer Style----------------------------------------------------------------------------------------
\usetheme{toninus}
\setbeamertemplate{section in toc}[sections numbered]

%-- Macros ----------------------------------------------------------------------------------------

\providecommand{\pairing}{\langle\cdot,\cdot\rangle}
\providecommand{\vHam}{\mathscr{v}}
\renewcommand{\checkpoint}[0]{
	\setcounter{tocdepth}{1}
	\addtocounter{framenumber}{-1}
 	\begin{frame}[t]{Outline}
  		%\tableofcontents[currentsection,currentsubsection]
  		%
  		\tableofcontents[currentsection]
		%
		\begin{center}
			\includegraphics[width=3.5cm]{Pictures/Figure_pentagondiagm_page}
		\end{center}
	\end{frame}
}

%- T1tle P4g3 -------------------------------------------------------------------------------------------
\title{
Multisymplectic observables and higher Courant algebroids
}
\subtitle{\href{https://arxiv.org/abs/2209.05836}{arXiv:2209.05836} (j.w. Marco Zambon)}
\author[AMM]{\href{https://dmf.unicatt.it/miti/}{Antonio Michele Miti}}
\institute[SUR]{
	Sapienza Università di Roma,	Rome, Italy 	\\
	\vspace{.5em}
  \begin{tabular}[h]{ccc}
      \href{https://dipartimenti.unicatt.it/dmf-home?rdeLocaleAttr=it}{\includegraphics[width=6cm]{./Logos/Sur_logo}} & & 
      \href{https://wis.kuleuven.be/english}{\includegraphics[width=3cm]{Logos/Civis_logo}}
  \end{tabular}    
}

\date[Template_21] % (optional, should be abbreviation of conference name)
{	
	{\vskip 1ex}
	Caprarola,
	\\
	February 2, 2024
}

%---------------------------------------------------------------------------------------------------------------------------------------------------
%- D0cum3nt ----------------------------------------------------------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------------------------------------------------------------------------

\begin{frame}  % Alternative: \maketitle outside of frame
	\titlepage
	\ifHandout
		\tikz[overlay,remember picture]
		{
	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
	    	\node[        
	    		draw,
	    		shape border rotate=90,
			isosceles triangle,
			isosceles triangle apex angle=90,
			fill=yellow]
	        		at ($(current page.north east)-(1,1)$) [rotate=-45] {\textcolor{red}{Handout version}};
		}
	\fi
	% European Commission	
		\tikz[overlay,remember picture]
		{
	    	%	\node at ($(current page.west)+(1.5,0)$) [rotate=90] {\Huge\textcolor{gray}{\today}};
	    	\node[        
	    		text width = 3.5cm
			]
	        		at ($(current page.south west)+(1.85,.5)$) [rotate=0] {

					\href{https://dipartimenti.unicatt.it/dmf-home?rdeLocaleAttr=it}{\includegraphics[width=\textwidth]{./Logos/Eu-h2020}}

	        		};
		}
	\end{frame}
	\addtocounter{framenumber}{-1}
\note{
	%\textbf{\underline{OUTLINE}}:
	%\tableofcontents
	\textbf{Abstract:}
	\\
    Until end 2026 (1 year after the end of CIVIS3i)
	All dissemination of results (in any form, including electronic) must:
	(a) display the EU emblem (ie, logo)
	(b) include the text “This project has received funding from the European
		Union’s Horizon 2020 research and innovation programme under grant
		agreement N°101034324.”

}
%---------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\iffalse \section{Introduction}\fi
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t] % Hybrid format - Title Page
	%
	\begin{center}
	\color{UniGreen}
		\par\noindent\rule{\textwidth}{0.4pt}\\[.5em]	
		{\bf\Large\emph{Multisymplectic observables }}
		\\
		and 
		{\bf\Large\emph{higher Courant algebroids}}\\
		\par\noindent\rule{\textwidth}{0.4pt}			
	\end{center}
	\vfill

	\centering
	\begin{tikzpicture}
		\node [draw,ellipse callout,UniGreen, minimum height=16em,minimum width=33em,callout relative pointer={(0,1)}] (L1) {};
		\node [text width=28em,text centered] (L2) {
			\textcolor{UniGreen}{\textbf{Honest Goals} of the talk:}
			\\
			\medskip
			\begin{itemize}[<+->]
				\item[•] Recall a certain "gauge-compatibility" condition in \emph{symplectic} geometry 
				   \color{blue}\small (involving $\omega$-twisted Lie alg.oids)
				\item[•] Discuss how this condition extends to \emph{\textbf{multi}symplectic} geometry
				   \color{blue}\small (involving $\omega$-twisted higher Courant alg.oids)
				\item[•] Review certain multisymplectic constructions guided by the above problem.\\
			\end{itemize}
			\medskip
		};
	\end{tikzpicture}

\end{frame}
\addtocounter{framenumber}{-1}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%%-------------------------------------------------------------------------------------------------------------------------------------------------
%\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
%	Given a \alert{symplectic mfd.} $(M,\omega)$ ...
%	\vfill
%	\begin{center}
%		\includestandalone[width=.95\textwidth]{Pictures/Frame_Embedding_Diagram_symplectic}
%	\end{center}
%	\vspace{3em}
%	\vfill
%	\begin{minipage}[t][8.5em][t]{\textwidth}
%		\begin{itemize}
%			\item<1-> \alert<1>{... there is a naturally associated Poisson algebra ...}
%			\item<2-> \alert<2>{... and also a (standard twisted) Lie Algebroid}.
%			\item<3-> A Lie algebroid is a "controlled" \alert<3>{$\infty$-dimensional Lie algebra.}
%			\item[]<4->
%				\quad\\
%		\vspace{-.75em}
%		\tcbset{colback=white,
%		colbacktitle=white,
%		colframe=red!70!black,
%		boxrule=1pt,
%		colupper=red!70!black,
%		arc=15pt,
%		}
%		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
%			\color{blue}{
%			\textbf{Lemma}: There exists an embedding of Lie Algebras.
%			}
%		\end{tcolorbox}
%		\end{itemize}
%	\end{minipage}
%\end{frame}
%%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	Given a \alert{symplectic mfd.} $(M,\omega)$ ...
	\vfill
	\begin{center}
		\includestandalone[width=.95\textwidth]{Pictures/Frame_Embedding_Diagram_symplectic}
	\end{center}
	\vfill
	\begin{minipage}[t][8.5em][t]{\textwidth}
		\begin{itemize}
			\only<1-3>{
			\item<1-> \alert<1>{... there is a naturally associated Poisson algebra ...}
			\item<2-> \alert<2>{... and also a (standard twisted) Lie Algebroid}.
			\item<3-> A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra given (in this case) by
			\begin{displaymath}
					\left[\binom{x_1}{f_1},\binom{x_2}{f_2}\right]
					~=~
					\binom{[x_1,x_2]}{x_1(f_2)-x_2(f_1)-\omega(x_1,x_2)}
				\end{displaymath}
			}
			\item[]<4->
				\quad\\
				\begin{thmblock}[There exists an embedding of Lie algebras.]
					\begin{displaymath}
						\begin{tikzcd}
							\Psi~:&[-1em] C^{\infty}(M)_\omega \ar[r,"\Psi"]& \Gamma(TM\oplus \mathbb{R})_\omega
							\\[-2em]
							& f \ar[r,mapsto] & \binom{\mathscr{v}_f}{f}
						\end{tikzcd}		
					\end{displaymath}
				\end{thmblock}
		\end{itemize}
	\end{minipage}
\end{frame}
\note{}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	%
Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_BigDiagram_symplectic}
	\end{center}
		\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
		\begin{itemize}
			\only<3-4>{
				\item<3-> There is a natural \alert<3>{isomorphism in the Lie Alg.oids category} \emph{($B$-transformation)}
					\begin{displaymath}
						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
					\end{displaymath}~.
				\item<4-> It descends to an \alert<4>{isomorphism of Lie algebras}.
			}
			\only<6-8>{
				\item<6-> \vspace{-2em}Consider an infinitesimal \alert<6>{Hamiltonian group action} $\mathfrak{g}\circlearrowleft M$ w.r.t. both $\omega$ and $\tilde{\omega}$.
				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
				\begin{displaymath}
					\tilde{f}(\xi) = f(\xi) - \iota_{\underline{\xi}}B
				\end{displaymath}
				}
			\item[]						
		\end{itemize}
	\only<2>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we compare the two \emph{observables} algebras?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<5>{
		\vspace{-.75em}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{How can we close the left-hand side?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
	}
	\only<8->{
		\vspace{-.75em}
		\tcbset{colback=white,
		colbacktitle=white,
		colframe=red!70!black,
		boxrule=1pt,
		colupper=red!70!black,
		arc=15pt,
		}
		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
			\color{blue}{
			\textbf{Lemma}: The central pentagon commutes!
			}
		\end{tcolorbox}
	\vfill
	}
	\end{minipage}	
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%%-------------------------------------------------------------------------------------------------------------------------------------------------
%\begin{frame}[fragile]{Compatibility between gauge transformations and comoment maps}
%	%
%	Consider $(M,\omega)$ \alert{symplectic mfd.}
%	%
%	\begin{center}
%			\includestandalone[width=.8\textwidth]{Pictures/Frame_BigDiagram_symplectic}
%	\end{center}
%	%
%	\vspace{-1em}
%	\vfill
%	\begin{minipage}[t][8em][t]{\textwidth}
%		\begin{itemize}
%			\only<2>{
%				\item<2-> Consider a second gauge-related symplectic structure on $M$
%					\begin{displaymath}
%						\tilde{\omega} = \omega + d B \qquad \text{with} \quad B\in \Omega^1(M).
%					\end{displaymath}
%			}
%			\only<3-4>{
%				\item<3-> There is a natural isomorphism in the Lie Alg.oids category \emph{($B$-transformation)}
%					\begin{displaymath}
%						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
%					\end{displaymath}
%			}
%			\only<6-7>{
%				\item<6-> Consider an infinitesimal group action $\mathfrak{g}\circlearrowleft M$ which is Hamiltonian w.r.t. both $\omega$ and $\tilde{\omega}$.
%				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
%				\begin{displaymath}
%					\tilde{f}(\xi) = f(\xi) - \iota_{\underline{\xi}}B
%				\end{displaymath}
%				}
%			\item[]						
%		\end{itemize}
%	\only<5>{
%		\vspace{-.75em}
%		\begin{center}
%		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
%			\alert{
%			\faQuestionCircle \qquad
%				{How can we close the left-hand side?}
%			\qquad \faQuestionCircle		
%			}
%		}
%		\end{center}
%	}
%	\only<8->{
%		\vspace{-.75em}
%		\tcbset{colback=white,
%		colbacktitle=white,
%		colframe=red!70!black,
%		boxrule=1pt,
%		colupper=red!70!black,
%		arc=15pt,
%		}
%		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
%			\color{blue}{
%			Lemma: The central pentagon commutes!
%			}
%		\end{tcolorbox}
%	\vfill
%	}
%	\only<9->{
%		\vspace{-.75em}
%		\begin{center}
%		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
%			\alert{
%			\faQuestionCircle \qquad
%				{What happens in the higher (n-plectic) case?}
%			\qquad \faQuestionCircle		
%			}
%		}
%		\end{center}
%	}
%	\end{minipage}	
%\end{frame}
%\note[itemize]{
%	\item The horizontal embedding is  $f \mapsto (v_f,f)$;
%	\item Vertical maps are also known as \emph{Gauge transformations}
%	\item upshot: 
%	\begin{enumerate}
%		\item 
%	\end{enumerate}
%}
%%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Why we can't directly relate the two Poissons?
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
	%
Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
	%
	\begin{center}
			\includestandalone[width=.8\textwidth]{Pictures/hyb-image_BigDiagram_symplectic}
	\end{center}
	%
	\vfill
	\begin{minipage}[t][8em][t]{\textwidth}
	\centering
	\vspace{-2em}
	\begin{tikzpicture}
		\node [draw,cloud callout,cloud puffs=50,cloud puff arc=100,blue, minimum height=10em,minimum width=35em,callout relative pointer={(-2,-2)}] (L1) {};
		\node [text width=30em,text centered] (L2) {
			\textcolor{blue}{Why should we care about this?}
			\\
			\begin{itemize}
				\item<2->[•] It's a framework for comparing gauge-related observables.
				\item<3->[•] It has a geometric interpration when $\omega$ \alert{prequantizable}.
			\end{itemize}
			\medskip
		};
	\end{tikzpicture}
	\end{minipage}	
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Details on the prequantum side.
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Scope of the talk}
		\begin{center}
		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
			\alert{
			\faQuestionCircle \qquad
				{\bf  What happens in the (higher) $n$-plectic case?}
			\qquad \faQuestionCircle		
			}
		}
		\end{center}
		\vfill

	\only<2->{
		{
			\color{UniGreen}
			\par\noindent\rule{\textwidth}{0.4pt}	
			\\ {\bf  Outline of the talk:} \\[-.5em]
			\par\noindent\rule{\textwidth}{0.4pt}			
		}
		\vspace{-1.5em}
		\setcounter{tocdepth}{1}
		\tableofcontents
	}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{What is \textbf{multisymplectic geometry}?}
\checkpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

\begin{frame}[t, fragile]{Multisymplectic manifolds} %Fragile -->workaround tikzcd
	\begin{center}
		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
	\end{center}
	\pause
	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
	\end{defblock}
	%
	\vfill
	%
	%
	\pause
	\begin{block}{Examples:}
		\begin{itemize}
			\item[$\bullet$] 1-plectic $=$ symplectic
			\item[$\bullet$] Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
			\item[$\bullet$] The multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.
		\end{itemize}
	\end{block}			 
%
	\pause
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
	\end{block}
\end{frame}

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Details on the GIMMSY Construction

	Mention Blohmann for the higher case
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{What is the \textbf{higher analogue} of the \textbf{Poisson algebra}?}
\checkpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

\begin{frame}{Hamiltonian forms}
	\only<1>{
	\medskip
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			\centering \it
			$-$ symplectic case $-$
			\vspace{20em}		
		\end{column}	
		%
		\onslide{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			$-$ $n$-plectic case $-$
			\vspace{20em}		
		\end{column}	
	\end{columns}
	}
	\pause
	%
	\begin{defblock}[Hamiltonian $(n-1)$-forms]
		\begin{displaymath}
			\Omega^{n-1}_{ham}(M,\omega) 	:=
			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
				\tikz[baseline,remember picture]{\node[rounded corners,
                        fill=orange!5,draw=orange!30,anchor=base]            
            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
            	}				
				~\biggr\} 
			\end{displaymath}
	\end{defblock}
	%
	\onslide<2>{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=orange!5,draw=orange!30,anchor=base]
            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
		}	
		\begin{tikzpicture}[overlay,remember picture]
		    	\path[->] (base.south east) edge[bend left,red](target.east);
	    \end{tikzpicture}
	}
	%
	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			$-$ symplectic case $-$
			\onslide<3->{
			\begin{thmblock}[Observables Poisson algebra]
				$C^\infty(M,\omega)$ endowed with
				\vspace{-.5em}
				\begin{displaymath}
					\lbrace \sigma_1, \sigma_2 \rbrace =			
					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
					~= \mathcal{L}_{\vHam_1} \sigma_2
				\end{displaymath}			
				forms a Poisson algebra.
			\end{thmblock}
			}
			%
			\onslide<4->{
			\vspace{1em}
			\begin{itemize}
				\item[\cmark] Skew-symmetric;
				\item[\cmark] multiplication of observables;
				\item[\cmark] Leibniz Rule;
				\item[\cmark] Jacobi equation;
			\end{itemize}		
			}		
		\end{column}	
		%
		\onslide<1->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			$-$ $n$-plectic case $-$
			\onslide<5->{			
			\begin{thmblock}[Observables $L_\infty$-algebra]
				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
				\vspace{-.5em}
				\begin{displaymath}
					\lbrace \sigma_1, \sigma_2 \rbrace =			
					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
				\end{displaymath}			
				can be extended to a \\ $L_\infty-algebra$.
			\end{thmblock}
			}
			%
			\onslide<6->{
			\begin{itemize}
				\item[\cmark] Skew-symmetric;
				\item[\xmark] multiplication of observables;
				\item[\xmark] Jacobi equation;
				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
				\item[\smark] Jacobi equation \emph{up to homotopies}.
			\end{itemize}			
			}
		\end{column}	
	\end{columns}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}{Reminder: $L_\infty$ Algebras}

		\emph{
			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
		}
		\\
		\vspace{.5em}
		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
			\includestandalone{Pictures/Figure_Linfinitydef}
		\end{defblock}	
		%
		%
	\pause
%	\vfill
%	\begin{thmblock}[Rogers \cite{Rogers2010}]
%		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
%		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
%	\end{thmblock}

	\begin{itemize}
		\item<2-> You can construct a coalgebra out of $L$ 
			{\small \color{UniGreen} (the reduced cofree coalgebra $S^{\geq 1}(L[1]),\Delta)$)}.
		\item<3-> You can assemble all $\mu_k$ to get a coderivation $Q_\mu$
				{\small \color{UniGreen} (the unique lift to a coderivation of the decalage of $ \mu=	\mu_1+\mu_2 + \dots$ }.
		\item<4-> Higher Jacobi is tantamount to having $Q_\mu ^2 = 0$.

	\end{itemize}
\end{frame}
\note[itemize]{
	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.

	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
	\\
	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.

	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
	employing the so-called \emph{ Richardson-Nijenhuis product}
		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.

	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.

	\item more precisely this statement is a proposition/definition

}
%------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Lie $\infty$-algebra of Observables (higher observables) }
	Let be $(M,\omega)$ a $n$-plectic manifold.
	  	\vfill
	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} \cite{Rogers2010}]
		\medskip
		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
		\vspace{-1em}
		\begin{center}
			\includestandalone{Pictures/hyb-Frame_Observables}
		\end{center}
		\onslide<2->{
			\bigskip
			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
			\vspace{-1em}
			\onslide<3->{
				\begin{center}
					\includestandalone{Pictures/Equation_Multibracket}	
				\end{center}
			}
			\medskip
		}
		%
	\end{defblock}
%	\onslide<3->{
%		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
%	\vfill
%	\begin{columns}
%		\hfill
%		\begin{column}{.11\linewidth}	
%			If $n>1$:
%			
%		\end{column}	
%		\begin{column}{.8\linewidth}
%		\begin{itemize}
%			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
%			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
%			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
%			\hspace*{4.25em}
%			 Jacobi equation \emph{up to homotopies}.
%		\end{itemize}		
%		\end{column}		
%	\end{columns}
%	}
  \end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Details on the controversial notion

	pdv meccanico: sono misurabili?

	pdv matematico: perchè questa è preferibile a struttura di Leibniz (check che sia la stessa usata da gimsy e spagnoli)
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{What is the \textbf{higher analogue} of the \textbf{twisted Lie algebroid}?}
\checkpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Vinogradov Algebroids}
	\begin{defblock}[Vinogradov algebroid (higher Courant)]
		\includestandalone[width=0.95\textwidth]{Pictures/hyb-Frame_vinogradov}		
	\end{defblock}
	\vfill
	\begin{itemize}
		\item<7-> $(n=1) ~ \Rightarrow$ standard twisted \emph{Lie algebroid};
		\item<8-> $(n=2) ~ \Rightarrow$ standard twisted \emph{Courant algebroid};
	\end{itemize}

\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Vinogradov $L_\infty$-algebra}
	Vin. alg.oids 
	$\quad\simeq\quad$ 	
	$NQ$-manifolds {\small($L_\infty$-algebroids)}
	$\quad\Rightarrow\quad$ 
	{\small Associated} $L_\infty$-algebra
	%
	\pause
	\begin{defblock}[Vinogradov $L_\infty$-algebra (Zambon) \cite{Zambon2012}]
		\includestandalone[width=0.95\textwidth]{Pictures/hyb-Frame_vinogradov-Linfty}	
	\end{defblock}
	\vfill
	\only<5->{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=gray!1,draw=gray!30,anchor=base]            
            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] { \footnotesize{\color{gray}{
            	 $e_i = \binom{X_i}{\alpha_i} \in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)$ 
            	 \quad~,\qquad
            	 $f_i \in \bigoplus_{k=0}^{n-2}\Omega^k(M)$.
            	 }}};
		}			
	}

\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	Details sulla ricetta di Zambon per costruire questa Lie infinito algebra.
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{What is the \textbf{higher analogue} of the \textbf{comoment map}?}
\checkpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Comoment maps}
	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
	\vfill

	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<2->{
				$-$ symplectic case $-$
				\begin{defblock}[Comoment map pertaining to $v$]
					Lie algebra morphism
					$$ f: \mathfrak{g} \to C^\infty(M) $$
					such that
					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
				\end{defblock}
			}
		\end{column}	
		%
		\onslide<2->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<3->{			
				$-$ $n$-plectic case $-$
				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
					$L_\infty$-morphism 
					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
					such that
					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
				\end{defblock}	
			}
		\end{column}	
	\end{columns}	
	%
	\pause
	\vfill
	\centering 
	\onslide<4->{\textbf{-- Conserved quantities --}}
	%
	\vspace{-1em}
	\begin{columns}[T]
		\setlength{\belowdisplayskip}{5pt}
		\begin{column}{.50\linewidth}
			%
			\centering \it
			\onslide<4->{
			\begin{propblock}[Noether Theorem]
				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
			\end{propblock}
			}
		\end{column}	
		%
		\onslide<5->{\vrule{}}
		%
		\begin{column}{.50\linewidth}
			\centering \it
			\onslide<5->{			
			\begin{propblock}[RWZ16 Theorem]
				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
			\end{propblock}
			}
		\end{column}	
	\end{columns}		
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Gauge related multisymplectic manifolds and comoment maps}
	Consider $M$ smooth mfd.
	%
	\begin{defblock}[Gauge related $n$-plectic structures]
		\bigskip
		\begin{columns}[T]
			\setlength{\belowdisplayskip}{5pt}
			\begin{column}{.50\linewidth}
				%
				\centering \it
				\onslide<2->{
				$\quad\omega,~ \tilde{\omega}~ \in \Omega^{n+1}(M)$ multisymplectic,
				}
			\end{column}	
			%
			\begin{column}{.50\linewidth}
				\centering \it
				\onslide<3->{			
				such that $\omega = \tilde{\omega} - d B$
				}
			\end{column}	
		\end{columns}	
		\bigskip	
	\end{defblock}
	%
	\pause
	\vfill
	\par\noindent\rule{\textwidth}{0.4pt}	
	\vfill
	\pause
	%
	Consider \quad $v:\mathfrak{g} \to \mathfrak{X}(M)$ preserving $\omega$ and $\tilde{\omega}$,
	%\phantom{consider}\quad $\mathcal{L}_{v_\xi}\omega=\mathcal{L}_{v_\xi}\tilde{\omega} = 0 \quad \forall \xi \in \mathfrak{g}$
	\\
	let \qquad$f: \mathfrak{g}\to L_\infty(M,\omega)$ an \emph{homotopy comoment map} ~ w.r.t. $\mathfrak{g}\circlearrowleft (M,\omega)$
	\pause
	\begin{lemblock}[Also $(M,\tilde{\omega})$ admits HCMM $(\tilde{f})$]
		\medskip
		\begin{columns}
			\begin{column}{.325\linewidth}
					\onslide<5->{
						\begin{displaymath}
							\tilde{f}_k = f_k +	
								\tikz[baseline,remember picture]{\node[rounded corners,
	                        		fill=blue!5,draw=blue!30,anchor=base]            
	            					(target) {$\mathrm{b}_k$ };
	            					}	
						\end{displaymath}
					}		
			\end{column}
			\begin{column}{.625\linewidth}	
					\onslide<5->{
						\begin{displaymath}
						%
						\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
							|[alias=O]| 
							\tikz[baseline,remember picture]{\node[rounded corners,
	                        		fill=blue!2,draw=blue!30,align=center]            
	            					(base) {$\mathrm{b}_k$};}						
							~:\&[-3em] \Lambda^k\mathfrak{g} \ar[r]\& \Omega^{n-k}(M)
							\\[-2em]
							\& \xi_1\wedge\dots \xi_k \ar[r,mapsto] \&
							(-)^k \iota(v_{\xi_1})\dots \iota(v_{\xi_{x_k}}) B
						\end{tikzcd}		
						\end{displaymath}								
					}		
			\end{column}
		\end{columns}
		\bigskip
		\only<5->{
			\begin{tikzpicture}[overlay,remember picture]
			    	\path[->,opacity=0.3] (base.west) edge[bend left,blue](target.south east);
		    \end{tikzpicture}		
	    }
	\end{lemblock}
	%
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{What is the \textbf{higher pentagonal diagram}?}
\checkpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Checkpoint}
	We ends up with the following diagram \onslide<2->{\emph{in the $L_\infty$-algebras category}}
	\vfill
	%
	\only<2->{\vspace{-2em}}
	\begin{center}
		\includestandalone[width=.9\textwidth]{Pictures/hyb-Frame_Diagram_checkpoint}
	\end{center}	
	\vfill
	\vspace{-2em}
	\onslide\onslide<2->{Open questions:}
	\begin{itemize}
		\item<3->[-] Does {\color{blue!60!black}\textbf{Rogers} $L_\infty$ \textbf{embeds} into \textbf{Vinogradov}}?
		\item<4->[-] Are {\color{green!60!black} \textbf{gauge related Vinogradov} $L_\infty$-algebras \textbf{isomorphic}}?
		\item<5->[-] Does the {\color{red!60!black} pentagonal \textbf{diagram commute}}?
	\end{itemize}

\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Does Rogers $L_\infty$ embeds into Vinogradov?}
\subcheckpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile,t]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
	Consider now $\omega$ \alert{$n$-plectic}~.
	\vfill
	\only<4->{\vspace{-5em}}
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_Embedding_Diagram_k-plectic}
	\end{center}
	\vfill
	\begin{minipage}[t][8.5em][t]{\textwidth}
	\only<4->{
	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2022}.]
	\begin{itemize}[leftmargin=0pt]
		\item[$\cdot$]<5-> 
			consider the graded vector subspace $\mathcal{A}$
			\onslide<6->{
				\begin{displaymath}
				\mathclap{
				{\mathcal{A}^k} =
				\begin{cases}
			\left.\left\lbrace
			\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
			~ \right\vert ~
			\iota_X \omega = -d \alpha\right\rbrace
	&\quad k=0,\\
					\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
				\end{cases}			
				}
				\end{displaymath}	
			}					
		\item[$\cdot$]<6-> 
			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
		\item[$\cdot$]<7->

			$L_\infty(M,\omega) \cong 
				(\mathcal{A},\pi) \color{red}\cong\color{black}
				(\mathcal{A},\mu) \hookrightarrow
				L_\infty(E^n,\omega)$
	\end{itemize}
	\end{thmblock}
	}
	\end{minipage}
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Are gauge related Vinogradov $L_\infty$-algebras isomorphic?}
\subcheckpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{Higher $B$-transformation}
	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega + d B$}:
		\medskip
	\only<4->{\vspace{-2em}}			
	\begin{center}
		\includestandalone[width=.4\textwidth]{Pictures/hyb-Frame_multisym_B-transf}
	\end{center}
	\vfill
	\only<1>{
	\begin{itemize}
		\item Vinogradov alg.oids w.r.t cohomologous twisting closed forms are isomorphic.
		\\
		\small{(in a suitable sense)}
	\end{itemize}	
	}
	%	
	\onslide<3->{
		\vspace{-1em}
		\begin{thmblock}[There is a \textbf{strict} $L_\infty$-isomorphism.]	
				\begin{displaymath}
				%
				\only<3>{
				\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
					|[alias=O]| 
					(\varphi)				
					~:\&[-3em] L_\infty(E^n,\omega) \ar[r,"\sim"]\& L_\infty(E^n,\tilde{\omega})
				\end{tikzcd}	
				\vspace{3.5em}
				}
				\only<4->{
				\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
					|[alias=O]| 
					(\varphi)				
					~:\&[-3em] L_\infty(E^n,\omega) \ar[r,"\sim"]\& L_\infty(E^n,\tilde{\omega})
					\\[-1em]
					\varphi_1				
					~:\&[-3em] \left(\mathcal{V}^n\right)_0 \ar[r,"\sim"] \& (\widetilde{\mathcal{V}}^n)_0=\mathfrak{X}(M)\oplus\Omega^{n-1}(M)
					\\[-2em]
					\& \binom{x}{\alpha} \ar[r,mapsto] \&
					\binom{x}{\alpha +\iota_x B}
				\end{tikzcd}	
				}
				\end{displaymath}
			\vspace{-1em}		
		\end{thmblock}							
	}		
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Does the pentagonal \textbf{diagram commute}?}
\subcheckpoint	
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{The higher pentagonal diagram}
	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega + d B$}:
	\vfill
	%
	\only<2->{\vspace{-2em}}
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_Gauge_Diagram_k-plectic}
	\end{center}	
	%
	\only<2->{\vspace{-2em}}
	%
	\vfill
	%
	\begin{itemize}
		\item<2-> Vinogradov $L_\infty$-algebras w.r.t cohomologous twisting forms are isomorphic.
		\item<2-> Rogers $L_\infty$ embeds into Vinogradov $L_\infty$.
		\item<3-> Consider a Lie algebra action $\mathfrak{g}\to \mathfrak{X}(M)$ admitting HCMM w.r.t $\omega$ and $\tilde{\omega}$
	\end{itemize}

	\vfill
	\tcbset{colback=white,
		colbacktitle=white,
		colframe=blue!70!black,
		boxrule=1pt,
		colupper=blue!70!black,
		arc=15pt,
		}
	\onslide<4->{
	\begin{tcolorbox}[sidebyside,righthand width=.75\linewidth]
		Thm: \cite{Miti2022}
		\tcblower
		\color{blue}
The pentagon commutes. 
			\\\emph{(On the nose, not "up to homotopies")}.
	\end{tcolorbox}

	}

\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{TODO}
	OUTLOOK. La big picture. 
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

	\begin{frame}{}
	\label{frame:thankyouslide}
		\vfill
	  \centering 
	  {\Huge\color{red} 
	  \emph{Thank you for your attention!}}
		\vfill
		%
		\centering
		\fbox{\includegraphics[width=.4\textwidth]{Pictures/arxiv-cover}}
	\end{frame}

%------------------------------------------------------------------------------------------------
% APPENDIX
%------------------------------------------------------------------------------------------------
\appendix

%-------------------------------------------------------------------------------------------------------------------------------------------------
\section{Appendix}
%------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Homotopy comomentum maps}
	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
	\vfill
	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)} \cite{Callies2016}]
			\includestandalone{Pictures/Frame_Lifting}
	\end{defblock}
	\onslide<4->{
	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
			%
			HCMM is a sequence of (graded-skew) multilinear maps:
			\begin{displaymath}
				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
			\end{displaymath}
			\emph{fulfilling:}%\emph{such that:}
			\begin{itemize}
				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
				\item<6-> $d f_k (p) = f_{k-1} (
				\tikz[baseline,remember picture]{\node[rounded corners,
                        fill=green!5,draw=green!30,anchor=base]            
            			(target) {$\partial $ };
            	}				
				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
			\end{itemize}
		\onslide<7->{
			\tikz[overlay,remember picture]
			{
				\node[rounded corners,
	                 draw=green!30,anchor=base]            
	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
			}	
		\begin{tikzpicture}[overlay,remember picture]
	    	\path[->] (base.west) edge[bend right,green](target.north east);
	    \end{tikzpicture}
	    }
	\end{lemblock}	
	}
	\vfill
\end{frame}
%-------------------------------------------------------------------------------------------------------------------------------------------------

\begin{frame}[fragile]{Multisymplectic manifolds} %Fragile -->workaround tikzcd
	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
	\end{defblock}
	%
	\begin{defblock}[Non-degenerate $(n+1)$-form]
		\begin{columns}
			\begin{column}{.45\linewidth}
				\centering{
				The $\omega^\flat$ (flat) bundle map is injective.
				}
			\end{column}
			\begin{column}{.5\linewidth}
						\vspace{-.5em}
				\[
				\begin{tikzcd}[column sep= small,row sep=0ex,
				/tikz/column 1/.append style={anchor=base east}]
				    \omega^\flat \colon T M \ar[r]& \Lambda^n T^\ast M \\
  						 (x,u) \ar[r, mapsto]& (x,\iota_{u} \omega_x)						
				\end{tikzcd}	
				\]
			\end{column}
		\end{columns}
	\end{defblock}
	%
	\vfill
	%
	\begin{block}{Examples:}
		\vspace{-.5em}
		\setbeamercovered{transparent}
		\begin{itemize}[<+->]
			\item[$\bullet$] $n=1$ \qquad\qquad\qquad $\Rightarrow$\quad $\omega$ is a symplectic form
			\item[$\bullet$]  $n=(dim(M)-1)$ \quad$\Rightarrow$\quad $\omega$ is a volume form
			%Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
			%\item[$\bullet$] Let $G$ a semisimple Lie group and $\langle\cdot,\cdot \rangle$  its killing form. Then $\langle [\cdot,\cdot],\cdot \rangle$ extends to a biinvariant multisymplectic form $\omega$.
			\item[$\bullet$] Let $Q$ a smooth manifold, the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.%
			\quad
			\textit{(cfr, \href{https://arxiv.org/abs/physics/9801019}{GIMMSY} construction for classical field theories)}
		\end{itemize}
	\end{block}

%
\end{frame}
\note[itemize]{
	\item Multisymplectic ($n$-plectic) geometry is a generalization of symplectic geometry where a closed, non degenerate $n+1$-form $(n\geq 1)$  takes the place of the symplectic 2-form

	\item multisymplectic means \emph{going higher} in the degree of $\omega$

	\item non degeneracy means $\iota_v\omega = 0 \Leftrightarrow v=0$.

	\item examples: 
	\\1-plectic $=$ symplectic, 
	\\any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form
	\\the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic (see frame extra-\ref{Frame:Ms-Field-Mechanics})

	\item Observe also that, by degree reason, when $n$ is equal to $1$ or $dim(M)+1$ an injective flat map $\flat$ is also bijective.

	\item It is important to stress that mechanical systems are not the only source instances of this class of of structures. 
				e.g. any semisimple Lie groups has associated a 2-plectic structure and any oriented $n+1$ dimensional manifold is naturally $n$-plectic.

}
%---------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{From symplectic to {multi}symplectic} 
	%
	\begin{center}
		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
	\end{center}
	\pause
	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
	\end{defblock}
	%
	\pause
		\begin{table}
			\begin{tabular}{c c c}
				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
			\end{tabular}
		\end{table}

	\vfill
	\pause
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
	\end{block}
	%
	\begin{table}
		\ifHandout
		%
		\else
		\only<4>{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
            \\
            \hline
  \multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &  \multicolumn{1}{@{}c@{}}{}              \\
		\end{tabular}
		}
		\fi
		\onslide<5->{
		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
            \hline
            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
            \\
            \hline
  			\multicolumn{1}{c}{}
            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
            &
            \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$} 
               \\
		\end{tabular}
		}
	\end{table}

\end{frame}
\note[itemize]{
	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
point-like particle constrained to some manifold), it is possible to associate a multisymplectic
manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics}

	\item General ideas basic parallelisms with caveats
	\item caveat: points in multiphase spaces are not states
	\item the table hides the duality between geometric and algebraic approaches to the problem.
	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{MS geometry and classical field mechanics}\label{Frame:Ms-Field-Mechanics}
		Consider a smooth manifold $Y$,
		\begin{columns}
			\hfill
			\begin{column}{.5\linewidth}
				\emph{Multicotangent bundle} $\bigwedge = \bigwedge^n T^\ast Y$\\
				is naturally $n$-plectic
			\end{column}
			\begin{column}{.4\linewidth}
				\[
				\begin{tikzcd}
					\Lambda \ar[d,"\pi"'] & T \Lambda \ar[d,"T \pi"] \ar[l] \\
					Y								& T Y \ar[l]
				\end{tikzcd}	
				\]
			\end{column}
		\end{columns}
	\pause
	\begin{defblock}[Tautological $n$-form]
		$\theta \in \Omega^n(\Lambda)$ such that:
		\begin{displaymath}
		\begin{split}
			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
			&= \iota_{(T \pi)_\ast u_1 \wedge \ldots \wedge (T \pi)_\ast u_n} \eta \\
			&= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
			\qquad \qquad \forall \eta \in \Lambda \, , \: \forall u_i \in T_\eta \Lambda 		
		\end{split}
		\end{displaymath}
	\end{defblock}
	\vfill
	\begin{columns}
		\begin{column}{.6\linewidth}
			\begin{defblock}[Tautological (multisymplectic) (n+1)-form]
				$$\omega := d \theta$$
			\end{defblock}
		\end{column}
		\begin{column}{.4\linewidth}
		 	\begin{claimblock}$\omega$ is not degenerate.\end{claimblock}	
		\end{column}
	\end{columns}	
	\pause
	\begin{keywordblock}
		\begin{tabular}{|c|c|c|}
			\hline 
			point-particles mechanics & $\rightsquigarrow$ & classical fields mechanics \\
			%(finite discrete DOF) & & (finite dimensional continuous DOF) \\
			\hline 
			symplectic & $\rightsquigarrow$ & multisymplectic \\ 
			\hline 
			Observables (Poisson) algebra & $\rightsquigarrow$ & Observables $L-\infty$ algebra
			 \\ 
			\hline 
			Co-moment map & $\rightsquigarrow$ & Homotopy co-momentum map \\ 
			\hline 
		\end{tabular} 
	\end{keywordblock}

\end{frame}
\note[itemize]{
	\item This example is significant from the perspective of geometric classical field theory:
		\begin{displaymath}
			\frac{\text{classical mechanics}}{\text{symplectic geo.}} =
			\frac{\text{classical field mechanics}}{\text{multisymplectic geo.}}
		\end{displaymath}
	\item Multicotangent bundle is the \emph{Higher analogue} of the cotangent bundle.
	(but it is not yet the analogue of a \emph{phase space}.)
\item The multiphase space is the sub-bundle of $n$-forms vanishing when contracted with 2 vertical fields.
  	\item The reason why this sub-bundle has a particular role is that it can be proved to be isomorphic to a suitable dual of the first Jet bundle.
  	\item For further details see Gotay et al. \href{https://arxiv.org/abs/physics/9801019}{arXiv:physics/9801019}. For a pictorial representation of all the structures involved in the geometric mechanics of I order classical field theories see appendix, pag: \ref{frame:Gimmsy}.
}
%------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Leibniz-algebra of Observables}
\begin{frame}[fragile,t]{Leibniz-algebra of Observables}

	\begin{defblock}[Leibniz algebra of observables]
		\hspace{.25em} $Leib(M,\omega)$ is given by:
		\begin{itemize}
			\item[•] the vector space $$\Omega_{ham}^{n-1}(M,\omega)$$
			\item[•] with the binary bracket 
			\begin{center}
				\includestandalone{Pictures/Equation_Leibbracket}	
			\end{center}
		\end{itemize}	
	\end{defblock}
	\vfill
	\pause
	%
	\begin{propblock}
		\begin{itemize}
			\setlength\itemsep{1em}
			\item[i.] $\vHam_{\llbracket \alpha, \beta \rrbracket} = [\vHam_\alpha,\vHam_\beta]$
			\item[ii.] $\llbracket \sigma, \llbracket \alpha, \beta \rrbracket \rrbracket =
			\llbracket\llbracket \sigma, \alpha \rrbracket, \beta \rrbracket
			+
			\llbracket \alpha, \llbracket \sigma, \beta \rrbracket \rrbracket$
			\item[iii.] $\llbracket \alpha, \beta \rrbracket + \llbracket \beta,\alpha \rrbracket = d \left( \iota_{\vHam_\alpha} \beta + \iota_{\vHam_\beta} \alpha\right)$
		\end{itemize}
	\end{propblock}

\end{frame}
\note[itemize]{
	\item in addition to being extendable to an $L_\infty$-algebra, the space $\Omega^{n-1}_{ham}(M)$ also carries the structure of a Leibniz algebra. This structure is very important for multisymplectic reduction procedures.
	\item 
	\item Take away: Two brackets on $\Omega_H^{k-1}(M)$, ${\color{red}\llbracket\alpha,\beta\rrbracket = \mathcal{L}_{X_\alpha} \beta}$ and ${\color{green}\{\alpha,\beta\}=\iota_{X_\alpha}\d\beta}$,
	Equal up to a coboundary: ${\color{red}\mathcal{L}_{X_\alpha}\beta} = {\color{green}\iota_{X_\alpha}\d\beta} + \d\hspace{1pt}\iota_{X_\alpha}\beta$
}
%---------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[t]{From Symplectic to MultiSymplectic (mechanical perspective)}
	\begin{block}{Historical motivation}
		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
		\begin{itemize}
		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
		 \\ $\cdots$
		\end{itemize}
	\end{block}
	\vfill
	\pause
	\tcbset{colback=white,
		colbacktitle=white,
		colframe=red!70!black,
		boxrule=1pt,
		colupper=red!70!black,
		arc=15pt}
	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]
		\color{red}
		\begin{columns}[T]
			\begin{column}{.20\linewidth}
				\begin{center}
					\huge
					\faWarning
				\end{center}
			\end{column}			
			\begin{column}{.60\linewidth}
				\vspace{-.4em}
				\begin{center}
					The lack of a satisfactory notion of observables hindered the spread of this formalism.
				\end{center}
			\end{column}			
			\begin{column}{.20\linewidth}
				\begin{center}
					\huge
					\faWarning
				\end{center}
			\end{column}			
		\end{columns}
	\end{tcolorbox}
	\vfill
	\pause
	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue,dashed}]
		\color{blue}
		\begin{columns}[T]
			\begin{column}{.20\linewidth}
				\begin{center}
					\huge
					\faQuestionCircle
				\end{center}
			\end{column}			
			\begin{column}{.60\linewidth}
				\begin{center}
					\vspace{-.4em}
					{Why observables are so crucial?\qquad \qquad Quantization!}	
				\end{center}
			\end{column}			
			\begin{column}{.20\linewidth}
				\begin{center}
					\huge
					\faQuestionCircle
				\end{center}
			\end{column}			
		\end{columns}
	\end{tcolorbox}

\end{frame}
\note[itemize]{
	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
point-like particle constrained to some manifold), it is possible to associate a multisymplectic
manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics} 
	\item Forger and Romero say: \emph{"The multisymplectic formalism is manifestly consistent with the basic principles of field theory, preserving full covariance, and it is mathematically rigorous because it uses well established methods from calculus on finite-dimensional manifolds. On the other hand, it does not seem to permit any obvious definition of the Poisson bracket between observables. Even the question of what mathematical objects should represent physical observables is not totally clear and has in fact been the subject of much debate in the literature. Moreover, the introduction of n conjugate momenta for each coordinate obscures the usual duality between canonically con- jugate variables (such as momenta and positions), which plays a fundamental role in all known methods of quantization.A definite solution to these problems has yet to be found."}

}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
% https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
\begin{frame}[t,allowframebreaks]{Extended Bibliography}
	\bibliographystyle{alpha}
	\bibliography{bibfile}
\end{frame}
%------------------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------------------
\end{document}

### 2024-02-20 msgauge-Caprarola.tex
Lento incedere - caprarola Talk.

@@
 			\begin{displaymath}
-					\left[\binom{x_1}{f_1},\binom{x_2}{f_2}\right]
+					\left[\binom{x_1}{f_1},\binom{x_2}{f_2}\right]_\omega
 					~=~
@@
 	%
-	\vfill
-	%
-	%
-	\pause
-	\begin{block}{Examples:}
-		\begin{itemize}
-			\item[$\bullet$] 1-plectic $=$ symplectic
-			\item[$\bullet$] Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
-			\item[$\bullet$] The multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.
-		\end{itemize}
-	\end{block}			 
-%
-	\pause
-	\begin{block}{Historical motivation}
-		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-		\begin{itemize}
-		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
-		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
-		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
-		 \\ $\cdots$
-		\end{itemize}
-	\end{block}
-\end{frame}
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	Details on the GIMMSY Construction
-
-	Mention Blohmann for the higher case
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{What is the \textbf{higher analogue} of the \textbf{Poisson algebra}?}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-\begin{frame}{Hamiltonian forms}
-	\only<1>{
-	\medskip
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			\centering \it
-			$-$ symplectic case $-$
-			\vspace{20em}		
-		\end{column}	
-		%
-		\onslide{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			$-$ $n$-plectic case $-$
-			\vspace{20em}		
-		\end{column}	
-	\end{columns}
-	}
-	\pause
-	%
-	\begin{defblock}[Hamiltonian $(n-1)$-forms]
-		\begin{displaymath}
-			\Omega^{n-1}_{ham}(M,\omega) 	:=
-			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
-				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=orange!5,draw=orange!30,anchor=base]            
-            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
-            	}				
-				~\biggr\} 
-			\end{displaymath}
-	\end{defblock}
-	%
-	\onslide<2>{
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=orange!5,draw=orange!30,anchor=base]
-            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
-		}	
-		\begin{tikzpicture}[overlay,remember picture]
-		    	\path[->] (base.south east) edge[bend left,red](target.east);
-	    \end{tikzpicture}
-	}
-	%
-	\vspace{-1em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			$-$ symplectic case $-$
-			\onslide<3->{
-			\begin{thmblock}[Observables Poisson algebra]
-				$C^\infty(M,\omega)$ endowed with
-				\vspace{-.5em}
-				\begin{displaymath}
-					\lbrace \sigma_1, \sigma_2 \rbrace =			
-					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
-					~= \mathcal{L}_{\vHam_1} \sigma_2
-				\end{displaymath}			
-				forms a Poisson algebra.
-			\end{thmblock}
-			}
-			%
-			\onslide<4->{
-			\vspace{1em}
-			\begin{itemize}
-				\item[\cmark] Skew-symmetric;
-				\item[\cmark] multiplication of observables;
-				\item[\cmark] Leibniz Rule;
-				\item[\cmark] Jacobi equation;
-			\end{itemize}		
-			}		
-		\end{column}	
-		%
-		\onslide<1->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			$-$ $n$-plectic case $-$
-			\onslide<5->{			
-			\begin{thmblock}[Observables $L_\infty$-algebra]
-				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
-				\vspace{-.5em}
-				\begin{displaymath}
-					\lbrace \sigma_1, \sigma_2 \rbrace =			
-					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
-				\end{displaymath}			
-				can be extended to a \\ $L_\infty-algebra$.
-			\end{thmblock}
-			}
-			%
-			\onslide<6->{
-			\begin{itemize}
-				\item[\cmark] Skew-symmetric;
-				\item[\xmark] multiplication of observables;
-				\item[\xmark] Jacobi equation;
-				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
-				\item[\smark] Jacobi equation \emph{up to homotopies}.
-			\end{itemize}			
-			}
-		\end{column}	
-	\end{columns}
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%------------------------------------------------------------------------------------------------
-\begin{frame}{Reminder: $L_\infty$ Algebras}
-
-		\emph{
-			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
-		}
-		\\
-		\vspace{.5em}
-		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
-			\includestandalone{Pictures/Figure_Linfinitydef}
-		\end{defblock}	
-		%
-		%
-	\pause
-%	\vfill
-%	\begin{thmblock}[Rogers \cite{Rogers2010}]
-%		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
-%		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
-%	\end{thmblock}
-
-	\begin{itemize}
-		\item<2-> You can construct a coalgebra out of $L$ 
-			{\small \color{UniGreen} (the reduced cofree coalgebra $S^{\geq 1}(L[1]),\Delta)$)}.
-		\item<3-> You can assemble all $\mu_k$ to get a coderivation $Q_\mu$
-				{\small \color{UniGreen} (the unique lift to a coderivation of the decalage of $ \mu=	\mu_1+\mu_2 + \dots$ }.
-		\item<4-> Higher Jacobi is tantamount to having $Q_\mu ^2 = 0$.
-
-	\end{itemize}
-\end{frame}
-\note[itemize]{
-	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
-	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.
-
-	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
-	\\
-	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.
-
-	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
-	employing the so-called \emph{ Richardson-Nijenhuis product}
-		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
-		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.
-
-	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.
-
-	\item more precisely this statement is a proposition/definition
-
-}
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Lie $\infty$-algebra of Observables (higher observables) }
-	Let be $(M,\omega)$ a $n$-plectic manifold.
-	  	\vfill
-	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} \cite{Rogers2010}]
-		\medskip
-		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
-		\vspace{-1em}
-		\begin{center}
-			\includestandalone{Pictures/hyb-Frame_Observables}
-		\end{center}
-		\onslide<2->{
-			\bigskip
-			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
-			\vspace{-1em}
-			\onslide<3->{
-				\begin{center}
-					\includestandalone{Pictures/Equation_Multibracket}	
-				\end{center}
-			}
-			\medskip
-		}
-		%
-	\end{defblock}
-%	\onslide<3->{
-%		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
-%	\vfill
-%	\begin{columns}
-%		\hfill
-%		\begin{column}{.11\linewidth}	
-%			If $n>1$:
-%			
-%		\end{column}	
-%		\begin{column}{.8\linewidth}
-%		\begin{itemize}
-%			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
-%			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
-%			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
-%			\hspace*{4.25em}
-%			 Jacobi equation \emph{up to homotopies}.
-%		\end{itemize}		
-%		\end{column}		
-%	\end{columns}
-%	}
-  \end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	Details on the controversial notion
-
-	pdv meccanico: sono misurabili?
-
-	pdv matematico: perchè questa è preferibile a struttura di Leibniz (check che sia la stessa usata da gimsy e spagnoli)
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{What is the \textbf{higher analogue} of the \textbf{twisted Lie algebroid}?}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[t]{Vinogradov Algebroids}
-	\begin{defblock}[Vinogradov algebroid (higher Courant)]
-		\includestandalone[width=0.95\textwidth]{Pictures/hyb-Frame_vinogradov}		
-	\end{defblock}
-	\vfill
-	\begin{itemize}
-		\item<7-> $(n=1) ~ \Rightarrow$ standard twisted \emph{Lie algebroid};
-		\item<8-> $(n=2) ~ \Rightarrow$ standard twisted \emph{Courant algebroid};
-	\end{itemize}
-
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Vinogradov $L_\infty$-algebra}
-	Vin. alg.oids 
-	$\quad\simeq\quad$ 	
-	$NQ$-manifolds {\small($L_\infty$-algebroids)}
-	$\quad\Rightarrow\quad$ 
-	{\small Associated} $L_\infty$-algebra
-	%
-	\pause
-	\begin{defblock}[Vinogradov $L_\infty$-algebra (Zambon) \cite{Zambon2012}]
-		\includestandalone[width=0.95\textwidth]{Pictures/hyb-Frame_vinogradov-Linfty}	
-	\end{defblock}
-	\vfill
-	\only<5->{
-		\tikz[overlay,remember picture]
-		{
-			\node[rounded corners,
-                 fill=gray!1,draw=gray!30,anchor=base]            
-            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] { \footnotesize{\color{gray}{
-            	 $e_i = \binom{X_i}{\alpha_i} \in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)$ 
-            	 \quad~,\qquad
-            	 $f_i \in \bigoplus_{k=0}^{n-2}\Omega^k(M)$.
-            	 }}};
-		}			
-	}
-
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	Details sulla ricetta di Zambon per costruire questa Lie infinito algebra.
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{What is the \textbf{higher analogue} of the \textbf{comoment map}?}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[t]{Comoment maps}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
-	\vfill
-
-	\vspace{-1em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<2->{
-				$-$ symplectic case $-$
-				\begin{defblock}[Comoment map pertaining to $v$]
-					Lie algebra morphism
-					$$ f: \mathfrak{g} \to C^\infty(M) $$
-					such that
-					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}
-			}
-		\end{column}	
-		%
-		\onslide<2->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<3->{			
-				$-$ $n$-plectic case $-$
-				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
-					$L_\infty$-morphism 
-					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
-					such that
-					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
-				\end{defblock}	
-			}
-		\end{column}	
-	\end{columns}	
-	%
-	\pause
-	\vfill
-	\centering 
-	\onslide<4->{\textbf{-- Conserved quantities --}}
-	%
-	\vspace{-1em}
-	\begin{columns}[T]
-		\setlength{\belowdisplayskip}{5pt}
-		\begin{column}{.50\linewidth}
-			%
-			\centering \it
-			\onslide<4->{
-			\begin{propblock}[Noether Theorem]
-				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
-				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
-			\end{propblock}
-			}
-		\end{column}	
-		%
-		\onslide<5->{\vrule{}}
-		%
-		\begin{column}{.50\linewidth}
-			\centering \it
-			\onslide<5->{			
-			\begin{propblock}[RWZ16 Theorem]
-				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
-				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
-			\end{propblock}
-			}
-		\end{column}	
-	\end{columns}		
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Gauge related multisymplectic manifolds and comoment maps}
-	Consider $M$ smooth mfd.
-	%
-	\begin{defblock}[Gauge related $n$-plectic structures]
-		\bigskip
-		\begin{columns}[T]
-			\setlength{\belowdisplayskip}{5pt}
-			\begin{column}{.50\linewidth}
-				%
-				\centering \it
-				\onslide<2->{
-				$\quad\omega,~ \tilde{\omega}~ \in \Omega^{n+1}(M)$ multisymplectic,
-				}
-			\end{column}	
-			%
-			\begin{column}{.50\linewidth}
-				\centering \it
-				\onslide<3->{			
-				such that $\omega = \tilde{\omega} - d B$
-				}
-			\end{column}	
-		\end{columns}	
-		\bigskip	
-	\end{defblock}
-	%
-	\pause
-	\vfill
-	\par\noindent\rule{\textwidth}{0.4pt}	
-	\vfill
-	\pause
-	%
-	Consider \quad $v:\mathfrak{g} \to \mathfrak{X}(M)$ preserving $\omega$ and $\tilde{\omega}$,
-	%\phantom{consider}\quad $\mathcal{L}_{v_\xi}\omega=\mathcal{L}_{v_\xi}\tilde{\omega} = 0 \quad \forall \xi \in \mathfrak{g}$
-	\\
-	let \qquad$f: \mathfrak{g}\to L_\infty(M,\omega)$ an \emph{homotopy comoment map} ~ w.r.t. $\mathfrak{g}\circlearrowleft (M,\omega)$
-	\pause
-	\begin{lemblock}[Also $(M,\tilde{\omega})$ admits HCMM $(\tilde{f})$]
-		\medskip
-		\begin{columns}
-			\begin{column}{.325\linewidth}
-					\onslide<5->{
-						\begin{displaymath}
-							\tilde{f}_k = f_k +	
-								\tikz[baseline,remember picture]{\node[rounded corners,
-	                        		fill=blue!5,draw=blue!30,anchor=base]            
-	            					(target) {$\mathrm{b}_k$ };
-	            					}	
-						\end{displaymath}
-					}		
-			\end{column}
-			\begin{column}{.625\linewidth}	
-					\onslide<5->{
-						\begin{displaymath}
-						%
-						\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
-							|[alias=O]| 
-							\tikz[baseline,remember picture]{\node[rounded corners,
-	                        		fill=blue!2,draw=blue!30,align=center]            
-	            					(base) {$\mathrm{b}_k$};}						
-							~:\&[-3em] \Lambda^k\mathfrak{g} \ar[r]\& \Omega^{n-k}(M)
-							\\[-2em]
-							\& \xi_1\wedge\dots \xi_k \ar[r,mapsto] \&
-							(-)^k \iota(v_{\xi_1})\dots \iota(v_{\xi_{x_k}}) B
-						\end{tikzcd}		
-						\end{displaymath}								
-					}		
-			\end{column}
-		\end{columns}
-		\bigskip
-		\only<5->{
-			\begin{tikzpicture}[overlay,remember picture]
-			    	\path[->,opacity=0.3] (base.west) edge[bend left,blue](target.south east);
-		    \end{tikzpicture}		
-	    }
-	\end{lemblock}
-	%
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{What is the \textbf{higher pentagonal diagram}?}
-\checkpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{Checkpoint}
-	We ends up with the following diagram \onslide<2->{\emph{in the $L_\infty$-algebras category}}
-	\vfill
-	%
-	\only<2->{\vspace{-2em}}
-	\begin{center}
-		\includestandalone[width=.9\textwidth]{Pictures/hyb-Frame_Diagram_checkpoint}
-	\end{center}	
-	\vfill
-	\vspace{-2em}
-	\onslide\onslide<2->{Open questions:}
-	\begin{itemize}
-		\item<3->[-] Does {\color{blue!60!black}\textbf{Rogers} $L_\infty$ \textbf{embeds} into \textbf{Vinogradov}}?
-		\item<4->[-] Are {\color{green!60!black} \textbf{gauge related Vinogradov} $L_\infty$-algebras \textbf{isomorphic}}?
-		\item<5->[-] Does the {\color{red!60!black} pentagonal \textbf{diagram commute}}?
-	\end{itemize}
-
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Does Rogers $L_\infty$ embeds into Vinogradov?}
-\subcheckpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile,t]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
-	Consider now $\omega$ \alert{$n$-plectic}~.
-	\vfill
-	\only<4->{\vspace{-5em}}
-	\begin{center}
-		\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_Embedding_Diagram_k-plectic}
-	\end{center}
-	\vfill
-	\begin{minipage}[t][8.5em][t]{\textwidth}
-	\only<4->{
-	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2022}.]
-	\begin{itemize}[leftmargin=0pt]
-		\item[$\cdot$]<5-> 
-			consider the graded vector subspace $\mathcal{A}$
-			\onslide<6->{
-				\begin{displaymath}
-				\mathclap{
-				{\mathcal{A}^k} =
-				\begin{cases}
-			\left.\left\lbrace
-			\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
-			~ \right\vert ~
-			\iota_X \omega = -d \alpha\right\rbrace
-	&\quad k=0,\\
-					\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
-				\end{cases}			
-				}
-				\end{displaymath}	
-			}					
-		\item[$\cdot$]<6-> 
-			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
-		\item[$\cdot$]<7->
-
-			$L_\infty(M,\omega) \cong 
-				(\mathcal{A},\pi) \color{red}\cong\color{black}
-				(\mathcal{A},\mu) \hookrightarrow
-				L_\infty(E^n,\omega)$
-	\end{itemize}
-	\end{thmblock}
-	}
-	\end{minipage}
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Are gauge related Vinogradov $L_\infty$-algebras isomorphic?}
-\subcheckpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[t]{Higher $B$-transformation}
-	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega + d B$}:
-		\medskip
-	\only<4->{\vspace{-2em}}			
-	\begin{center}
-		\includestandalone[width=.4\textwidth]{Pictures/hyb-Frame_multisym_B-transf}
-	\end{center}
-	\vfill
-	\only<1>{
-	\begin{itemize}
-		\item Vinogradov alg.oids w.r.t cohomologous twisting closed forms are isomorphic.
-		\\
-		\small{(in a suitable sense)}
-	\end{itemize}	
-	}
-	%	
-	\onslide<3->{
-		\vspace{-1em}
-		\begin{thmblock}[There is a \textbf{strict} $L_\infty$-isomorphism.]	
-				\begin{displaymath}
-				%
-				\only<3>{
-				\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
-					|[alias=O]| 
-					(\varphi)				
-					~:\&[-3em] L_\infty(E^n,\omega) \ar[r,"\sim"]\& L_\infty(E^n,\tilde{\omega})
-				\end{tikzcd}	
-				\vspace{3.5em}
-				}
-				\only<4->{
-				\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
-					|[alias=O]| 
-					(\varphi)				
-					~:\&[-3em] L_\infty(E^n,\omega) \ar[r,"\sim"]\& L_\infty(E^n,\tilde{\omega})
-					\\[-1em]
-					\varphi_1				
-					~:\&[-3em] \left(\mathcal{V}^n\right)_0 \ar[r,"\sim"] \& (\widetilde{\mathcal{V}}^n)_0=\mathfrak{X}(M)\oplus\Omega^{n-1}(M)
-					\\[-2em]
-					\& \binom{x}{\alpha} \ar[r,mapsto] \&
-					\binom{x}{\alpha +\iota_x B}
-				\end{tikzcd}	
-				}
-				\end{displaymath}
-			\vspace{-1em}		
-		\end{thmblock}							
-	}		
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Does the pentagonal \textbf{diagram commute}?}
-\subcheckpoint	
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{The higher pentagonal diagram}
-	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega + d B$}:
-	\vfill
-	%
-	\only<2->{\vspace{-2em}}
-	\begin{center}
-		\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_Gauge_Diagram_k-plectic}
-	\end{center}	
-	%
-	\only<2->{\vspace{-2em}}
-	%
-	\vfill
-	%
-	\begin{itemize}
-		\item<2-> Vinogradov $L_\infty$-algebras w.r.t cohomologous twisting forms are isomorphic.
-		\item<2-> Rogers $L_\infty$ embeds into Vinogradov $L_\infty$.
-		\item<3-> Consider a Lie algebra action $\mathfrak{g}\to \mathfrak{X}(M)$ admitting HCMM w.r.t $\omega$ and $\tilde{\omega}$
-	\end{itemize}
-
-	\vfill
-	\tcbset{colback=white,
-		colbacktitle=white,
-		colframe=blue!70!black,
-		boxrule=1pt,
-		colupper=blue!70!black,
-		arc=15pt,
-		}
-	\onslide<4->{
-	\begin{tcolorbox}[sidebyside,righthand width=.75\linewidth]
-		Thm: \cite{Miti2022}
-		\tcblower
-		\color{blue}
-The pentagon commutes. 
-			\\\emph{(On the nose, not "up to homotopies")}.
-	\end{tcolorbox}
-
-	}
-
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	OUTLOOK. La big picture. 
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-	\begin{frame}{}
-	\label{frame:thankyouslide}
-		\vfill
-	  \centering 
-	  {\Huge\color{red} 
-	  \emph{Thank you for your attention!}}
-		\vfill
-		%
-		\centering
-		\fbox{\includegraphics[width=.4\textwidth]{Pictures/arxiv-cover}}
-	\end{frame}
-
-%------------------------------------------------------------------------------------------------
-% APPENDIX
-%------------------------------------------------------------------------------------------------
-\appendix
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Appendix}
-%------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Homotopy comomentum maps}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
-	\vfill
-	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)} \cite{Callies2016}]
-			\includestandalone{Pictures/Frame_Lifting}
-	\end{defblock}
-	\onslide<4->{
-	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
-			%
-			HCMM is a sequence of (graded-skew) multilinear maps:
-			\begin{displaymath}
-				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
-				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
-			\end{displaymath}
-			\emph{fulfilling:}%\emph{such that:}
-			\begin{itemize}
-				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
-				\item<6-> $d f_k (p) = f_{k-1} (
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=green!5,draw=green!30,anchor=base]            
-            			(target) {$\partial $ };
-            	}				
-				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
-				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
-			\end{itemize}
-		\onslide<7->{
-			\tikz[overlay,remember picture]
-			{
-				\node[rounded corners,
-	                 draw=green!30,anchor=base]            
-	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
-			}	
-		\begin{tikzpicture}[overlay,remember picture]
-	    	\path[->] (base.west) edge[bend right,green](target.north east);
-	    \end{tikzpicture}
-	    }
-	\end{lemblock}	
-	}
-	\vfill
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-\begin{frame}[fragile]{Multisymplectic manifolds} %Fragile -->workaround tikzcd
-	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
-		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
-	\end{defblock}
+	\pause
 	%
@@
 	\end{defblock}		
-	%
-	\vfill
-	%
+	\vfill
+	%
+	%
+	\pause
 	\begin{block}{Examples:}
-		\vspace{-.5em}
-		\setbeamercovered{transparent}
-		\begin{itemize}[<+->]
-			\item[$\bullet$] $n=1$ \qquad\qquad\qquad $\Rightarrow$\quad $\omega$ is a symplectic form
-			\item[$\bullet$]  $n=(dim(M)-1)$ \quad$\Rightarrow$\quad $\omega$ is a volume form
-			%Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
-			%\item[$\bullet$] Let $G$ a semisimple Lie group and $\langle\cdot,\cdot \rangle$  its killing form.
-Then $\langle [\cdot,\cdot],\cdot \rangle$ extends to a biinvariant multisymplectic form $\omega$.
-			\item[$\bullet$] Let $Q$ a smooth manifold, the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.%
-			\quad
-			\textit{(cfr, \href{https://arxiv.org/abs/physics/9801019}{GIMMSY} construction for classical field theories)}
+		\begin{itemize}
+			\item[$\bullet$] 1-plectic $=$ symplectic
+			\item[$\bullet$] Any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form.
+			\item[$\bullet$] The multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic.
 		\end{itemize}
 	\end{block}			 
-
-%
-\end{frame}
-\note[itemize]{
-	\item Multisymplectic ($n$-plectic) geometry is a generalization of symplectic geometry where a closed, non degenerate $n+1$-form $(n\geq 1)$  takes the place of the symplectic 2-form
-
-	\item multisymplectic means \emph{going higher} in the degree of $\omega$
-
-	\item non degeneracy means $\iota_v\omega = 0 \Leftrightarrow v=0$.
-
-	\item examples: 
-	\\1-plectic $=$ symplectic, 
-	\\any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form
-	\\the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic (see frame extra-\ref{Frame:Ms-Field-Mechanics})
-
-	\item Observe also that, by degree reason, when $n$ is equal to $1$ or $dim(M)+1$ an injective flat map $\flat$ is also bijective.
-
-	\item It is important to stress that mechanical systems are not the only source instances of this class of of structures. 
-				e.g. any semisimple Lie groups has associated a 2-plectic structure and any oriented $n+1$ dimensional manifold is naturally $n$-plectic.
-
-}
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}{From symplectic to {multi}symplectic} 
-	%
-	\begin{center}
-		$-$ \emph{multisymplectic means \textbf{going higher} in the degree of $\omega$} $-$
-	\end{center}
-	\pause
-	\begin{defblock}[$n$-plectic manifold ~\emph{(Cantrijn, Ibort, De Le\'on)} \cite{Cantrun2017}]
-		\includestandalone[width=0.95\textwidth]{Pictures/Figure_multisym}	
-	\end{defblock}
-	%
-	\pause
-		\begin{table}
-			\begin{tabular}{c c c}
-				symplectic forms \small($n=1$) & $\leftrightsquigarrow$ & volume forms \small($n= \text{dim}(M)-1$)
-			\end{tabular}
-		\end{table}
-
-	\vfill
-	\pause
+%
+
+\end{frame}
+
+\begin{frame}[fragile]{Multisymplectic manifolds - motivations} %Fragile -->workaround tikzcd
 	\begin{block}{Historical motivation}
 		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
+		\begin{itemize}
+		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
+		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
+		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
+		 \\ $\cdots$
+		\end{itemize}
 	\end{block}
 	%
+	\pause
 	\begin{table}
@@
 		\else
-		\only<4>{
+		\only<2>{
 		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
@@
 		\fi
-		\onslide<5->{
+		\onslide<3->{
 		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
@@
 
+%
+\end{frame}
+\note[itemize]{
+	\item Multisymplectic ($n$-plectic) geometry is a generalization of symplectic geometry where a closed, non degenerate $n+1$-form $(n\geq 1)$  takes the place of the symplectic 2-form
+
+	\item multisymplectic means \emph{going higher} in the degree of $\omega$
+
+	\item non degeneracy means $\iota_v\omega = 0 \Leftrightarrow v=0$.
+
+	\item examples: 
+	\\1-plectic $=$ symplectic, 
+	\\any oriented $(n+1)$-dimensional manifold is $n$-plectic w.r.t. the volume form
+	\\the multicotangent bundle $\Lambda^n T^\ast Q$ is naturally $n$-plectic (see frame extra-\ref{Frame:Ms-Field-Mechanics})
+
+	\item Observe also that, by degree reason, when $n$ is equal to $1$ or $dim(M)+1$ an injective flat map $\flat$ is also bijective.
+
+	\item It is important to stress that mechanical systems are not the only source instances of this class of of structures. 
+				e.g. any semisimple Lie groups has associated a 2-plectic structure and any oriented $n+1$ dimensional manifold is naturally $n$-plectic.
+
+}
+%---------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{TODO}
+	Details on the GIMMSY Construction
+
+	Mention Blohmann for the higher case
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\section{What is the \textbf{higher analogue} of the \textbf{Poisson algebra}?}
+\checkpoint	
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+\begin{frame}{Hamiltonian forms}
+	\begin{defblock}[Hamiltonian $(n-1)$-forms]
+		\begin{displaymath}
+			\Omega^{n-1}_{ham}(M,\omega) 	:=
+			\biggr\{ \sigma \in  \Omega^{n-1}(M) \; \biggr\vert \; 
+				\exists \vHam_\sigma \in \mathfrak{X}(M) ~:~ 
+				\tikz[baseline,remember picture]{\node[rounded corners,
+                        fill=orange!5,draw=orange!30,anchor=base]            
+            			(target) {$d \sigma = -\iota_{\vHam_\sigma} \omega$ };
+            	}				
+				~\biggr\} 
+			\end{displaymath}
+	\end{defblock}
+	\pause
+	%
+
+	%
+	\onslide<2>{
+		\tikz[overlay,remember picture]
+		{
+			\node[rounded corners,
+                 fill=orange!5,draw=orange!30,anchor=base]
+            	 (base) at ($(current page.north east)-(2,1)$) [rotate=-0,text width=3.5cm,align=center] {\footnotesize{\textcolor{red}{Hamilton-DeDonder-Weyl \\equation}}};
+		}	
+		\begin{tikzpicture}[overlay,remember picture]
+		    	\path[->] (base.south east) edge[bend left,red](target.east);
+	    \end{tikzpicture}
+	}
+	%
+	\vspace{-1em}
+	\begin{columns}[T]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\centering \it
+			$-$ symplectic case $-$
+			\onslide<3->{
+			\begin{thmblock}[Observables Poisson algebra]
+				$C^\infty(M,\omega)$ endowed with
+				\vspace{-.5em}
+				\begin{displaymath}
+					\lbrace \sigma_1, \sigma_2 \rbrace =			
+					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
+					~= \mathcal{L}_{\vHam_1} \sigma_2
+				\end{displaymath}			
+				forms a Poisson algebra.
+			\end{thmblock}
+			}
+			%
+			\onslide<4->{
+			\vspace{1em}
+			\begin{itemize}
+				\item[\cmark] Skew-symmetric;
+				\item[\cmark] multiplication of observables;
+				\item[\cmark] Leibniz Rule;
+				\item[\cmark] Jacobi equation;
+			\end{itemize}		
+			}		
+		\end{column}	
+		%
+		\onslide<1->{\vrule{}}
+		%
+		\begin{column}{.50\linewidth}
+			\centering \it
+			$-$ $n$-plectic case $-$
+			\onslide<5->{			
+			\begin{thmblock}[Observables $L_\infty$-algebra]
+				$\Omega^{n-1}_{ham}(M,\omega)$ endowed with
+				\vspace{-.5em}
+				\begin{displaymath}
+					\lbrace \sigma_1, \sigma_2 \rbrace =			
+					~ - \iota_{\vHam_1}\iota_{\vHam_2} \omega 
+				\end{displaymath}			
+				can be extended to a \\ $L_\infty-algebra$.
+			\end{thmblock}
+			}
+			%
+			\onslide<6->{
+			\begin{itemize}
+				\item[\cmark] Skew-symmetric;
+				\item[\xmark] multiplication of observables;
+				\item[\xmark] Jacobi equation;
+				%\\ \hspace*{4.25em} full-fledged Jacobi equation;
+				\item[\smark] Jacobi equation \emph{up to homotopies}.
+			\end{itemize}			
+			}
+		\end{column}	
+	\end{columns}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%------------------------------------------------------------------------------------------------
+\begin{frame}{Reminder: $L_\infty$ Algebras}
+
+		\emph{
+			$L_\infty$-algebra is the notion that one obtains from a Lie algebra when one requires the Jacobi identity to be satisfied only up to a higher coherent chain homotopy.
+		}
+		\\
+		\vspace{.5em}
+		\begin{defblock}[$L_\infty$-algebra ~\emph{(Lada, Markl)} ~\cite{Lada1995}]
+			\includestandalone{Pictures/Figure_Linfinitydef}
+		\end{defblock}	
+		%
+		%
+	\pause
+%	\vfill
+%	\begin{thmblock}[Rogers \cite{Rogers2010}]
+%		The \emph{higher observable algebra} $L_{\infty}(M,\omega)$ 	forms an honest $L_\infty$ algebra.
+%		\footnotetext{ Take $\mu_1 = \text{d}$, $\mu_k=\lbrace\dots\rbrace_k$, $L$ is a shifted truncation of the de Rham complex.}
+%	\end{thmblock}
+
+	\begin{itemize}
+		\item<2-> You can construct a coalgebra out of $L$ 
+			{\small \color{UniGreen} (the reduced cofree coalgebra $S^{\geq 1}(L[1]),\Delta)$)}.
+		\item<3-> You can assemble all $\mu_k$ to get a coderivation $Q_\mu$
+				{\small \color{UniGreen} (the unique lift to a coderivation of the decalage of $ \mu=	\mu_1+\mu_2 + \dots$ }.
+		\item<4-> Higher Jacobi is tantamount to having $Q_\mu ^2 = 0$.
+
+	\end{itemize}
+\end{frame}
+\note[itemize]{
+	\item $L_\infty$-algebra is the notion obtained from a Lie algebra requiring that the Jacobi identity is satisfied only up to a higher coherent chain homotopy.
+	\item The Lie-n algebra mentioned before is a $L_\infty$ algebra with underlying graded vector space concentrated in degrees $0,1...n$.
+
+	\item Definition. We say that a permutation $\sigma \in S_n$ is a $(j,n-j)$-unshuffle, $0\leq j \le1 n$  if $\sigma(1)< \dots < \sigma(j)$ and $\sigma(j+1)<\dots<\sigma(n)$.
+	\\
+	You can also say that $\sigma$ is a $(j,n-j)$-unshuffle if $\sigma(i)< \sigma(i+1)$ when $i\neq j$.
+
+	\item 	Alternatively, the Jacobiators can be also denoted as $$\displaystyle J_m=\sum_{i+j=m+1} 	\mu_i \triangleleft \mu_j = 0$$
+	employing the so-called \emph{ Richardson-Nijenhuis product}
+		 $$\mu_i\circ \mu_j := (-)^{i(j+1)}\frac{1}{j!(i-1)!}\mu_i \triangleleft \mu_j\otimes \mathbb{1}_{i-1} \circ \mathcal{A}~,$$
+		 where $\mathcal{A}$ denotes the (graded) total skew-symmetrizator.
+
+	\item see frame extra-\ref{Frame:unwapping-Jacobi} for a slightly demystification of the higher Jacobi equations.
+
+	\item more precisely this statement is a proposition/definition
+
+}
+%------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Lie $\infty$-algebra of Observables (higher observables) }
+	Let be $(M,\omega)$ a $n$-plectic manifold.
+	  	\vfill
+	\begin{defblock}[$L_\infty$-algebra of observables ~\emph{(Rogers)} \cite{Rogers2010}]
+		\medskip
+		\hspace{.25em} Is a cochain-complex $(L,\{\cdot\}_1)$ \\
+		\vspace{-1em}
+		\begin{center}
+			\includestandalone{Pictures/Frame_Observables}
+		\end{center}
+		\onslide<2->{
+			\bigskip
+			\hspace{.25em} with $n$ (skew-symmetric) multibrackets $(2 \leq k \leq n+1)$\\
+			\vspace{-1em}
+			\onslide<3->{
+				\begin{center}
+					\includestandalone{Pictures/Equation_Multibracket}	
+				\end{center}
+			}
+			\medskip
+		}
+		%
+	\end{defblock}
+%	\onslide<3->{
+%		\emph{Higher analogue} of the \emph{Poisson algebra structure} associated to a symplectic mfd.
+%	\vfill
+%	\begin{columns}
+%		\hfill
+%		\begin{column}{.11\linewidth}	
+%			If $n>1$:
+%			
+%		\end{column}	
+%		\begin{column}{.8\linewidth}
+%		\begin{itemize}
+%			\item[\xmark] \textcolor{red}{we lose} :\quad multiplication of observables, Jacobi equation;
+%			%\\ \hspace*{4.25em} full-fledged Jacobi equation;
+%			\item[\cmark] \textcolor{green}{we gain} :\quad brackets with arities different than two,\\
+%			\hspace*{4.25em}
+%			 Jacobi equation \emph{up to homotopies}.
+%		\end{itemize}		
+%		\end{column}		
+%	\end{columns}
+%	}
+  \end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{TODO}
+	Details on the controversial notion
+
+	pdv meccanico: sono misurabili?
+
+	pdv matematico: perchè questa è preferibile a struttura di Leibniz (check che sia la stessa usata da gimsy e spagnoli)
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\section{What is the \textbf{higher analogue} of the \textbf{twisted Lie algebroid}?}
+\checkpoint	
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[t]{Vinogradov Algebroids}
+	\begin{defblock}[Vinogradov algebroid (higher Courant)]
+		\includestandalone[width=0.95\textwidth]{Pictures/Frame_vinogradov}		
+	\end{defblock}
+	\vfill
+	\begin{itemize}
+		\item<6-> $(n=1) ~ \Rightarrow$ standard twisted \emph{Lie algebroid};
+		\item<7-> $(n=2) ~ \Rightarrow$ standard twisted \emph{Courant algebroid};
+	\end{itemize}
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Vinogradov $L_\infty$-algebra}
+	Vin. alg.oids 
+	$\quad\simeq\quad$ 	
+	$NQ$-manifolds {\small($L_\infty$-algebroids)}
+	$\quad\Rightarrow\quad$ 
+	{\small Associated} $L_\infty$-algebra
+	%
+	\pause
+	\begin{defblock}[Vinogradov $L_\infty$-algebra (Zambon) \cite{Zambon2012}]
+		\includestandalone[width=0.95\textwidth]{Pictures/Frame_vinogradov-Linfty}	
+	\end{defblock}
+	\vfill
+	\only<6->{
+		\tikz[overlay,remember picture]
+		{
+			\node[rounded corners,
+                 fill=gray!1,draw=gray!30,anchor=base]            
+            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] { \footnotesize{\color{gray}{
+            	 $e_i = \binom{X_i}{\alpha_i} \in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)$ 
+            	 \quad~,\qquad
+            	 $f_i \in \bigoplus_{k=0}^{n-2}\Omega^k(M)$.
+            	 }}};
+		}			
+	}
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{TODO}
+	Details sulla ricetta di Zambon per costruire questa Lie infinito algebra.
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\section{What is the \textbf{higher analogue} of the \textbf{comoment map}?}
+\checkpoint	
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[t]{Comoment maps}
+	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
+	\vfill
+
+	\vspace{-1em}
+	\begin{columns}[T]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\centering \it
+			\onslide<2->{
+				$-$ symplectic case $-$
+				\begin{defblock}[Comoment map pertaining to $v$]
+					Lie algebra morphism
+					$$ f: \mathfrak{g} \to C^\infty(M) $$
+					such that
+					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
+				\end{defblock}
+			}
+		\end{column}	
+		%
+		\onslide<2->{\vrule{}}
+		%
+		\begin{column}{.50\linewidth}
+			\centering \it
+			\onslide<3->{			
+				$-$ $n$-plectic case $-$
+				\begin{defblock}[Homotopy comoment map \tiny (HCMM)]
+					$L_\infty$-morphism 
+					$$ (f_k) : \mathfrak{g} \to L_\infty (M,\omega)$$
+					such that
+					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
+				\end{defblock}	
+			}
+		\end{column}	
+	\end{columns}	
+	%
+	\pause
+	\vfill
+	\centering 
+	\onslide<4->{\textbf{-- Conserved quantities --}}
+	%
+	\vspace{-1em}
+	\begin{columns}[T]
+		\setlength{\belowdisplayskip}{5pt}
+		\begin{column}{.50\linewidth}
+			%
+			\centering \it
+			\onslide<4->{
+			\begin{propblock}[Noether Theorem]
+				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
+				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
+			\end{propblock}
+			}
+		\end{column}	
+		%
+		\onslide<5->{\vrule{}}
+		%
+		\begin{column}{.50\linewidth}
+			\centering \it
+			\onslide<5->{			
+			\begin{propblock}[RWZ16 Theorem]
+				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
+				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
+			\end{propblock}
+			}
+		\end{column}	
+	\end{columns}		
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}{Gauge related multisymplectic manifolds and comoment maps}
+	Consider $M$ smooth mfd.
+	%
+	\begin{defblock}[Gauge related $n$-plectic structures]
+		\bigskip
+		\begin{columns}[T]
+			\setlength{\belowdisplayskip}{5pt}
+			\begin{column}{.50\linewidth}
+				%
+				\centering \it
+				\onslide<2->{
+				$\quad\omega,~ \tilde{\omega}~ \in \Omega^{n+1}(M)$ multisymplectic,
+				}
+			\end{column}	
+			%
+			\begin{column}{.50\linewidth}
+				\centering \it
+				\onslide<3->{			
+				such that $\omega = \tilde{\omega} - d B$
+				}
+			\end{column}	
+		\end{columns}	
+		\bigskip	
+	\end{defblock}
+	%
+	\pause
+	\vfill
+	\par\noindent\rule{\textwidth}{0.4pt}	
+	\vfill
+	\pause
+	%
+	Consider \quad $v:\mathfrak{g} \to \mathfrak{X}(M)$ preserving $\omega$ and $\tilde{\omega}$,
+	%\phantom{consider}\quad $\mathcal{L}_{v_\xi}\omega=\mathcal{L}_{v_\xi}\tilde{\omega} = 0 \quad \forall \xi \in \mathfrak{g}$
+	\\
+	let \qquad$f: \mathfrak{g}\to L_\infty(M,\omega)$ an \emph{homotopy comoment map} ~ w.r.t. $\mathfrak{g}\circlearrowleft (M,\omega)$
+	\pause
+	\begin{lemblock}[Also $(M,\tilde{\omega})$ admits HCMM $(\tilde{f})$]
+		\medskip
+		\begin{columns}
+			\begin{column}{.325\linewidth}
+					\onslide<5->{
+						\begin{displaymath}
+							\tilde{f}_k = f_k +	
+								\tikz[baseline,remember picture]{\node[rounded corners,
+	                        		fill=blue!5,draw=blue!30,anchor=base]            
+	            					(target) {$\mathrm{b}_k$ };
+	            					}	
+						\end{displaymath}
+					}		
+			\end{column}
+			\begin{column}{.625\linewidth}	
+					\onslide<5->{
+						\begin{displaymath}
+						%
+						\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
+							|[alias=O]| 
+							\tikz[baseline,remember picture]{\node[rounded corners,
+	                        		fill=blue!2,draw=blue!30,align=center]            
+	            					(base) {$\mathrm{b}_k$};}						
+							~:\&[-3em] \Lambda^k\mathfrak{g} \ar[r]\& \Omega^{n-k}(M)
+							\\[-2em]
+							\& \xi_1\wedge\dots \xi_k \ar[r,mapsto] \&
+							(-)^k \iota(v_{\xi_1})\dots \iota(v_{\xi_{x_k}}) B
+						\end{tikzcd}		
+						\end{displaymath}								
+					}		
+			\end{column}
+		\end{columns}
+		\bigskip
+		\only<5->{
+			\begin{tikzpicture}[overlay,remember picture]
+			    	\path[->,opacity=0.3] (base.west) edge[bend left,blue](target.south east);
+		    \end{tikzpicture}		
+	    }
+	\end{lemblock}
+	%
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\section{What is the \textbf{higher pentagonal diagram}?}
+\checkpoint	
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}{Checkpoint}
+	We ends up with the following diagram \onslide<2->{\emph{in the $L_\infty$-algebras category}}
+	\vfill
+	%
+	\only<2->{\vspace{-2em}}
+	\begin{center}
+		\includestandalone[width=.9\textwidth]{Pictures/hyb-Frame_Diagram_checkpoint}
+	\end{center}	
+	\vfill
+	\vspace{-2em}
+	\onslide\onslide<2->{Open questions:}
+	\begin{itemize}
+		\item<3->[-] Does {\color{blue!60!black}\textbf{Rogers} $L_\infty$ \textbf{embeds} into \textbf{Vinogradov}}?
+		\item<4->[-] Are {\color{green!60!black} \textbf{gauge related Vinogradov} $L_\infty$-algebras \textbf{isomorphic}}?
+		\item<5->[-] Does the {\color{red!60!black} pentagonal \textbf{diagram commute}}?
+	\end{itemize}
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Does Rogers $L_\infty$ embeds into Vinogradov?}
+\subcheckpoint	
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile,t]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
+	Consider now $\omega$ \alert{$n$-plectic}~.
+	\vfill
+	\only<4->{\vspace{-5em}}
+	\begin{center}
+		\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_Embedding_Diagram_k-plectic}
+	\end{center}
+	\vfill
+	\begin{minipage}[t][8.5em][t]{\textwidth}
+	\only<4->{
+	\begin{thmblock}[Embedding of $L_\infty$-algebras  $\Psi:L_\infty(M,\omega)\hookrightarrow L_{\infty}(E^n,\omega)$\quad \cite{Miti2022}.]
+	\begin{itemize}[leftmargin=0pt]
+		\item[$\cdot$]<5-> 
+			consider the graded vector subspace $\mathcal{A}$
+			\onslide<5->{
+				\begin{displaymath}
+				\mathclap{
+				{\mathcal{A}^k} =
+				\begin{cases}
+			\left.\left\lbrace
+			\binom{X}{\alpha}\in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)
+			~ \right\vert ~
+			\iota_X \omega = -d \alpha\right\rbrace
+	&\quad k=0,\\
+					\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
+				\end{cases}			
+				}
+				\end{displaymath}	
+			}					
+		\item[$\cdot$]<6-> 
+			restrict the two $L_\infty$-structures to $\pi$ and $\mu$ on $\mathcal{A}$
+		\item[$\cdot$]<7->
+
+			$L_\infty(M,\omega) \cong 
+				(\mathcal{A},\pi) \color{red}\cong\color{black}
+				(\mathcal{A},\mu) \hookrightarrow
+				L_\infty(E^n,\omega)$
+	\end{itemize}
+	\end{thmblock}
+	}
+	\end{minipage}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Are gauge related Vinogradov $L_\infty$-algebras isomorphic?}
+\subcheckpoint	
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[t]{Higher $B$-transformation}
+	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega + d B$}:
+		\medskip
+	\only<4->{\vspace{-2em}}			
+	\begin{center}
+		\includestandalone[width=.4\textwidth]{Pictures/hyb-Frame_multisym_B-transf}
+	\end{center}
+	\vfill
+	\only<1>{
+	\begin{itemize}
+		\item Vinogradov alg.oids w.r.t cohomologous twisting closed forms are isomorphic.
+		\\
+		\small{(in a suitable sense)}
+	\end{itemize}	
+	}
+	%	
+	\onslide<3->{
+		\vspace{-1em}
+		\begin{thmblock}[There is a \textbf{strict} $L_\infty$-isomorphism.]	
+				\begin{displaymath}
+				%
+				\only<3>{
+				\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
+					|[alias=O]| 
+					(\varphi)				
+					~:\&[-3em] L_\infty(E^n,\omega) \ar[r,"\sim"]\& L_\infty(E^n,\tilde{\omega})
+				\end{tikzcd}	
+				\vspace{3.5em}
+				}
+				\only<4->{
+				\begin{tikzcd}[baseline=(O.base),ampersand replacement=\&]
+					|[alias=O]| 
+					(\varphi)				
+					~:\&[-3em] L_\infty(E^n,\omega) \ar[r,"\sim"]\& L_\infty(E^n,\tilde{\omega})
+					\\[-1em]
+					\varphi_1				
+					~:\&[-3em] \left(\mathcal{V}^n\right)_0 \ar[r,"\sim"] \& (\widetilde{\mathcal{V}}^n)_0=\mathfrak{X}(M)\oplus\Omega^{n-1}(M)
+					\\[-2em]
+					\& \binom{x}{\alpha} \ar[r,mapsto] \&
+					\binom{x}{\alpha +\iota_x B}
+				\end{tikzcd}	
+				}
+				\end{displaymath}
+			\vspace{-1em}		
+		\end{thmblock}							
+	}		
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Does the pentagonal \textbf{diagram commute}?}
+\subcheckpoint	
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}{The higher pentagonal diagram}
+	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega + d B$}:
+	\vfill
+	%
+	\only<2->{\vspace{-2em}}
+	\begin{center}
+		\includestandalone[width=.8\textwidth]{Pictures/hyb-Frame_Gauge_Diagram_k-plectic}
+	\end{center}	
+	%
+	\only<2->{\vspace{-2em}}
+	%
+	\vfill
+	%
+	\begin{itemize}
+		\item<2-> Vinogradov $L_\infty$-algebras w.r.t cohomologous twisting forms are isomorphic.
+		\item<2-> Rogers $L_\infty$ embeds into Vinogradov $L_\infty$.
+		\item<3-> Consider a Lie algebra action $\mathfrak{g}\to \mathfrak{X}(M)$ admitting HCMM w.r.t $\omega$ and $\tilde{\omega}$
+	\end{itemize}
+
+	\vfill
+	\tcbset{colback=white,
+		colbacktitle=white,
+		colframe=blue!70!black,
+		boxrule=1pt,
+		colupper=blue!70!black,
+		arc=15pt,
+		}
+	\onslide<4->{
+	\begin{tcolorbox}[sidebyside,righthand width=.75\linewidth]
+		Thm: \cite{Miti2022}
+		\tcblower
+		\color{blue}
+The pentagon commutes. 
+			\\\emph{(On the nose, not "up to homotopies")}.
+	\end{tcolorbox}
+
+	}
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{TODO}
+	OUTLOOK. La big picture. 
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+	\begin{frame}{}
+	\label{frame:thankyouslide}
+		\vfill
+	  \centering 
+	  {\Huge\color{red} 
+	  \emph{Thank you for your attention!}}
+		\vfill
+		%
+		\centering
+		\fbox{\includegraphics[width=.4\textwidth]{Pictures/arxiv-cover}}
+	\end{frame}
+
+%------------------------------------------------------------------------------------------------
+% APPENDIX
+%------------------------------------------------------------------------------------------------
+\appendix
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\section{Appendix}
+%------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Homotopy comomentum maps}
+	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
+	\vfill
+	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)} \cite{Callies2016}]
+			\includestandalone{Pictures/Frame_Lifting}
+	\end{defblock}
+	\onslide<4->{
+	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
+			%
+			HCMM is a sequence of (graded-skew) multilinear maps:
+			\begin{displaymath}
+				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
+				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
+			\end{displaymath}
+			\emph{fulfilling:}%\emph{such that:}
+			\begin{itemize}
+				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
+				\item<6-> $d f_k (p) = f_{k-1} (
+				\tikz[baseline,remember picture]{\node[rounded corners,
+                        fill=green!5,draw=green!30,anchor=base]            
+            			(target) {$\partial $ };
+            	}				
+				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
+				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
+			\end{itemize}
+		\onslide<7->{
+			\tikz[overlay,remember picture]
+			{
+				\node[rounded corners,
+	                 draw=green!30,anchor=base]            
+	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
+			}	
+		\begin{tikzpicture}[overlay,remember picture]
+	    	\path[->] (base.west) edge[bend right,green](target.north east);
+	    \end{tikzpicture}
+	    }
+	\end{lemblock}	
+	}
+	\vfill
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------------------------------------------------------
+\subsection{Leibniz-algebra of Observables}
+\begin{frame}[fragile,t]{Leibniz-algebra of Observables}
+
+	\begin{defblock}[Leibniz algebra of observables]
+		\hspace{.25em} $Leib(M,\omega)$ is given by:
+		\begin{itemize}
+			\item[•] the vector space $$\Omega_{ham}^{n-1}(M,\omega)$$
+			\item[•] with the binary bracket 
+			\begin{center}
+				\includestandalone{Pictures/Equation_Leibbracket}	
+			\end{center}
+		\end{itemize}	
+	\end{defblock}
+	\vfill
+	\pause
+	%
+	\begin{propblock}
+		\begin{itemize}
+			\setlength\itemsep{1em}
+			\item[i.] $\vHam_{\llbracket \alpha, \beta \rrbracket} = [\vHam_\alpha,\vHam_\beta]$
+			\item[ii.] $\llbracket \sigma, \llbracket \alpha, \beta \rrbracket \rrbracket =
+			\llbracket\llbracket \sigma, \alpha \rrbracket, \beta \rrbracket
+			+
+			\llbracket \alpha, \llbracket \sigma, \beta \rrbracket \rrbracket$
+			\item[iii.] $\llbracket \alpha, \beta \rrbracket + \llbracket \beta,\alpha \rrbracket = d \left( \iota_{\vHam_\alpha} \beta + \iota_{\vHam_\beta} \alpha\right)$
+		\end{itemize}
+	\end{propblock}
+
+\end{frame}
+\note[itemize]{
+	\item in addition to being extendable to an $L_\infty$-algebra, the space $\Omega^{n-1}_{ham}(M)$ also carries the structure of a Leibniz algebra.
+This structure is very important for multisymplectic reduction procedures.
+	\item 
+	\item Take away: Two brackets on $\Omega_H^{k-1}(M)$, ${\color{red}\llbracket\alpha,\beta\rrbracket = \mathcal{L}_{X_\alpha} \beta}$ and ${\color{green}\{\alpha,\beta\}=\iota_{X_\alpha}\d\beta}$,
+	Equal up to a coboundary: ${\color{red}\mathcal{L}_{X_\alpha}\beta} = {\color{green}\iota_{X_\alpha}\d\beta} + \d\hspace{1pt}\iota_{X_\alpha}\beta$
+}
+%---------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[t]{From Symplectic to MultiSymplectic (mechanical perspective)}
+	\begin{block}{Historical motivation}
+		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
+		\begin{itemize}
+		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
+		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
+		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
+		 \\ $\cdots$
+		\end{itemize}
+	\end{block}
+	\vfill
+	\pause
+	\tcbset{colback=white,
+		colbacktitle=white,
+		colframe=red!70!black,
+		boxrule=1pt,
+		colupper=red!70!black,
+		arc=15pt}
+	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]
+		\color{red}
+		\begin{columns}[T]
+			\begin{column}{.20\linewidth}
+				\begin{center}
+					\huge
+					\faWarning
+				\end{center}
+			\end{column}			
+			\begin{column}{.60\linewidth}
+				\vspace{-.4em}
+				\begin{center}
+					The lack of a satisfactory notion of observables hindered the spread of this formalism.
+				\end{center}
+			\end{column}			
+			\begin{column}{.20\linewidth}
+				\begin{center}
+					\huge
+					\faWarning
+				\end{center}
+			\end{column}			
+		\end{columns}
+	\end{tcolorbox}
+	\vfill
+	\pause
+	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue,dashed}]
+		\color{blue}
+		\begin{columns}[T]
+			\begin{column}{.20\linewidth}
+				\begin{center}
+					\huge
+					\faQuestionCircle
+				\end{center}
+			\end{column}			
+			\begin{column}{.60\linewidth}
+				\begin{center}
+					\vspace{-.4em}
+					{Why observables are so crucial?\qquad \qquad Quantization!}	
+				\end{center}
+			\end{column}			
+			\begin{column}{.20\linewidth}
+				\begin{center}
+					\huge
+					\faQuestionCircle
+				\end{center}
+			\end{column}			
+		\end{columns}
+	\end{tcolorbox}
+
 \end{frame}
@@
 manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics} 
-
-	\item General ideas basic parallelisms with caveats
-	\item caveat: points in multiphase spaces are not states
-	\item the table hides the duality between geometric and algebraic approaches to the problem.
-	\item	Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-		\begin{itemize}
-		 \item[-] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
-		 \item[-] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
-		 \item[-] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
-		 \\ $\cdots$
-		\end{itemize}
+	\item Forger and Romero say: \emph{"The multisymplectic formalism is manifestly consistent with the basic principles of field theory, preserving full covariance, and it is mathematically rigorous because it uses well established methods from calculus on finite-dimensional manifolds.
+On the other hand, it does not seem to permit any obvious definition of the Poisson bracket between observables.
+Even the question of what mathematical objects should represent physical observables is not totally clear and has in fact been the subject of much debate in the literature.
+Moreover, the introduction of n conjugate momenta for each coordinate obscures the usual duality between canonically con- jugate variables (such as momenta and positions), which plays a fundamental role in all known methods of quantization.A definite solution to these problems has yet to be found."}
+
 }
@@
 
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Leibniz-algebra of Observables}
-\begin{frame}[fragile,t]{Leibniz-algebra of Observables}
-
-	\begin{defblock}[Leibniz algebra of observables]
-		\hspace{.25em} $Leib(M,\omega)$ is given by:
-		\begin{itemize}
-			\item[•] the vector space $$\Omega_{ham}^{n-1}(M,\omega)$$
-			\item[•] with the binary bracket 
-			\begin{center}
-				\includestandalone{Pictures/Equation_Leibbracket}	
-			\end{center}
-		\end{itemize}	
-	\end{defblock}
-	\vfill
-	\pause
-	%
-	\begin{propblock}
-		\begin{itemize}
-			\setlength\itemsep{1em}
-			\item[i.] $\vHam_{\llbracket \alpha, \beta \rrbracket} = [\vHam_\alpha,\vHam_\beta]$
-			\item[ii.] $\llbracket \sigma, \llbracket \alpha, \beta \rrbracket \rrbracket =
-			\llbracket\llbracket \sigma, \alpha \rrbracket, \beta \rrbracket
-			+
-			\llbracket \alpha, \llbracket \sigma, \beta \rrbracket \rrbracket$
-			\item[iii.] $\llbracket \alpha, \beta \rrbracket + \llbracket \beta,\alpha \rrbracket = d \left( \iota_{\vHam_\alpha} \beta + \iota_{\vHam_\beta} \alpha\right)$
-		\end{itemize}
-	\end{propblock}
-
-\end{frame}
-\note[itemize]{
-	\item in addition to being extendable to an $L_\infty$-algebra, the space $\Omega^{n-1}_{ham}(M)$ also carries the structure of a Leibniz algebra.
-This structure is very important for multisymplectic reduction procedures.
-	\item 
-	\item Take away: Two brackets on $\Omega_H^{k-1}(M)$, ${\color{red}\llbracket\alpha,\beta\rrbracket = \mathcal{L}_{X_\alpha} \beta}$ and ${\color{green}\{\alpha,\beta\}=\iota_{X_\alpha}\d\beta}$,
-	Equal up to a coboundary: ${\color{red}\mathcal{L}_{X_\alpha}\beta} = {\color{green}\iota_{X_\alpha}\d\beta} + \d\hspace{1pt}\iota_{X_\alpha}\beta$
-}
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[t]{From Symplectic to MultiSymplectic (mechanical perspective)}
-	\begin{block}{Historical motivation}
-		Mechanics: geometrical foundations of \textit{(first-order)} field theories.
-		\begin{itemize}
-		 \item[•] Kijowski, W. Tulczyjew \cite{Kijowski1979}; %(1979)
-		 \item[•] Cariñena, Crampin, Ibort \cite{Carinena1991b};% (1991)
-		 \item[•] Gotay, Isenberg, Marsden, Montgomery \cite{Gimmsy1};%(1998)
-		 \\ $\cdots$
-		\end{itemize}
-	\end{block}
-	\vfill
-	\pause
-	\tcbset{colback=white,
-		colbacktitle=white,
-		colframe=red!70!black,
-		boxrule=1pt,
-		colupper=red!70!black,
-		arc=15pt}
-	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]
-		\color{red}
-		\begin{columns}[T]
-			\begin{column}{.20\linewidth}
-				\begin{center}
-					\huge
-					\faWarning
-				\end{center}
-			\end{column}			
-			\begin{column}{.60\linewidth}
-				\vspace{-.4em}
-				\begin{center}
-					The lack of a satisfactory notion of observables hindered the spread of this formalism.
-				\end{center}
-			\end{column}			
-			\begin{column}{.20\linewidth}
-				\begin{center}
-					\huge
-					\faWarning
-				\end{center}
-			\end{column}			
-		\end{columns}
-	\end{tcolorbox}
-	\vfill
-	\pause
-	\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue,dashed}]
-		\color{blue}
-		\begin{columns}[T]
-			\begin{column}{.20\linewidth}
-				\begin{center}
-					\huge
-					\faQuestionCircle
-				\end{center}
-			\end{column}			
-			\begin{column}{.60\linewidth}
-				\begin{center}
-					\vspace{-.4em}
-					{Why observables are so crucial?\qquad \qquad Quantization!}	
-				\end{center}
-			\end{column}			
-			\begin{column}{.20\linewidth}
-				\begin{center}
-					\huge
-					\faQuestionCircle
-				\end{center}
-			\end{column}			
-		\end{columns}
-	\end{tcolorbox}
-
-\end{frame}
-\note[itemize]{
-	\item Historically, the interest in multisymplectic manifolds, has been motivated by the need for understanding the geometrical foundations of first-order classical field theories.
-	The key point is that, just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single
-point-like particle constrained to some manifold), it is possible to associate a multisymplectic
-manifold to any classical field system (e.g. a continuous medium like a filament or a fluid). See frame Extra-\ref{Frame:Ms-Field-Mechanics} 
-	\item Forger and Romero say: \emph{"The multisymplectic formalism is manifestly consistent with the basic principles of field theory, preserving full covariance, and it is mathematically rigorous because it uses well established methods from calculus on finite-dimensional manifolds.
-On the other hand, it does not seem to permit any obvious definition of the Poisson bracket between observables.
-Even the question of what mathematical objects should represent physical observables is not totally clear and has in fact been the subject of much debate in the literature.
-Moreover, the introduction of n conjugate momenta for each coordinate obscures the usual duality between canonically con- jugate variables (such as momenta and positions), which plays a fundamental role in all known methods of quantization.A definite solution to these problems has yet to be found."}
-
-}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
 %------------------------------------------------------------------------------------------------

### 2024-02-21 Pictures/Frame_prequantum.tex
Updating slides for Caprarola.

\documentclass[beamer,handout,tikz]{standalone}

\usepackage{tikz}
\usepackage{amssymb}
\usetikzlibrary{shapes.geometric,calc,decorations.markings}

	%Credit: https://tex.stackexchange.com/questions/99119/beamer-problematic-use-of-visible-and-only-in-combination-with-tikz-to-draw-a
  \tikzset{
    invisible/.style={opacity=0},
    visible on/.style={alt=#1{}{invisible}},
    alt/.code args={<#1>#2#3}{%
      \alt<#1>{\pgfkeysalso{#2}}{\pgfkeysalso{#3}} % \pgfkeysalso doesn't change the path
    },
  }

\begin{document}
	\begin{tikzpicture}[
    tangent/.style={
        decoration={
            markings,% switch on markings
            mark=
                at position #1
                with
                {
                    \coordinate (tangent point-\pgfkeysvalueof{/pgf/decoration/mark info/sequence number}) at (0pt,0pt);
                    \coordinate (tangent unit vector-\pgfkeysvalueof{/pgf/decoration/mark info/sequence number}) at (1,0pt);
                    \coordinate (tangent orthogonal unit vector-\pgfkeysvalueof{/pgf/decoration/mark info/sequence number}) at (0pt,1);
                }
        },
        postaction=decorate
    },
    use tangent/.style={
        shift=(tangent point-#1),
        x=(tangent unit vector-#1),
        y=(tangent orthogonal unit vector-#1)
    },
    use tangent/.default=1
]
		\draw[yshift=-.8cm,black!40] (0,0) -- (4,0) node[black,right=2pt] {\small $M$};
		\draw[visible on=<4->,yshift=.5cm,xshift=.22cm,green!70!black] (0,0) -- (4,0) node[green!70!black,right=2pt] {\small $\textrm{ker}(\theta)$};
		\begin{scope}[xshift=-1.35cm]
		\draw[orange] (0,.5) ellipse (.25 and .5);
		\end{scope}

		\node[orange] at (-1.8,0) {\small $S^1$};

		\node[orange] at (-.7,.5) {$\curvearrowright$};

		\draw[black!70] (0,.5) ellipse (.25 and .5);
		\draw[black!70] (4,0) arc (-90:90:.25 and .5);
		\draw[dotted,black!70] (4,1) arc (90:270:.25 and .5);
		\draw[black!70] (0,0) -- (4,0) node[black,right=5pt] {\small $P$};
		\draw[black!70] (0,1) -- (4,1);

		\foreach \x in {-1,.5,...,2}
		{
			\begin{scope}[xshift=\x cm]
				\draw[orange,xshift=1.4cm,tangent=0.1,tangent=0.5,tangent=0.9] (0,0) arc (-90:90:.25 and .5);
				\draw[orange,dotted,xshift=1.4cm] (0,1) arc (90:270:.25 and .5);

				\draw [visible on=<3->,blue,->, thick, use tangent] (0,0) -- (.4,0);
				\draw [visible on=<3->,blue,->, thick, use tangent=2] (0,0) -- (.4,0);
				\draw [visible on=<3->,blue,->, thick, use tangent=3] (0,0) -- (.4,0);
			\end{scope}

		}

		\node[visible on=<3->,blue] at (2.2,1.2) {$E$};
	\end{tikzpicture}
\end{document}

### 2024-02-21 msgauge-Caprarola.tex
Updating slides for Caprarola.

@@
 %| Contents:	- 60 minutes, 
+%| Note: Riprovo a dare il talk dopo che a Wurzburg è andata male.
+%|		 Lì ho sbagliato tutti i tempi ma non so stabilire se è stato un problema di scarsa preparazione
+%|       , di farmaci, o di stress da brutte notizie sulla crioc.
+%|
+%|
 %|
@@
 %- D0cum3nt ----------------------------------------------------------------------------------------------
-\documentclass[10pt]{beamer}
+\documentclass[10pt,handout]{beamer}
 
@@
 	\begin{minipage}[t][8.5em][t]{\textwidth}
+		\only<1-3>{One can naturally associate:}
 		\begin{itemize}
 			\only<1-3>{
-			\item<1-> \alert<1>{... there is a naturally associated Poisson algebra ...}
-			\item<2-> \alert<2>{... and also a (standard twisted) Lie Algebroid}.
-			\item<3-> A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra given (in this case) by
+			\item<1-> a \alert<1>{Poisson algebra} w/ $$\{f,g\}_\omega = -\iota_{\vHam_f}\iota_{\vHam_g} \omega$$
+			\item<2-> a \alert<2>{(standard twisted) Lie Algebroid};
+			\item<3->[-] A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra w/
 			\begin{displaymath}
@@
 						\begin{tikzcd}
-							\Psi~:&[-1em] C^{\infty}(M)_\omega \ar[r,"\Psi"]& \Gamma(TM\oplus \mathbb{R})_\omega
+							\Psi~:&[-1em] (C^{\infty}(M), \{\cdot,\cdot\}_\omega) \ar[r,"\Psi"]& 
+							(\Gamma(TM\oplus \mathbb{R}), [\cdot,\cdot]_\omega)
 							\\[-2em]
@@
 	Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
+	~~ \alert{($\widetilde{\omega} = \omega - \d B$)}
 	%
@@
 			\only<6-8>{
-				\item<6-> \vspace{-2em}Consider an infinitesimal \alert<6>{Hamiltonian group action} $\mathfrak{g}\circlearrowleft M$ w.r.t. both $\omega$ and $\tilde{\omega}$.
+				\item<6-> \vspace{-2em}Consider an infinitesimal \alert<6>{Hamiltonian group action} $\mathfrak{g}\curvearrowright M$ w.r.t. both $\omega$ and $\tilde{\omega}$.
 				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
@@
 			}
+			\hfill \hyperlink{frame:whyNoVertArrow}{\color{gray}$[>>]$}%\beamerskipbutton{}}
 		\end{tcolorbox}
 	\vfill
+
 	}
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	Why we can't directly relate the two Poissons?
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
-	%
-Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
+\begin{frame}[fragile]{Why not a direct vertical arrow?}\label{frame:whyNoVertArrow}
+	\begin{center}
+			\includestandalone[width=.7\textwidth]{Pictures/Frame_BigDiagram_verticalArrow}
+	\end{center}
+	\vfill
+	\begin{itemize}
+		\item<2-> Assume exists \alert<2>{$\chi:C^\infty(M)_\omega \to C^\infty(M)_{\widetilde{\omega}}$} ~s.t. the square commutes.
+				\begin{displaymath}
+					\begin{cases}
+						\chi(f) =& f - \iota_{\vHam_f} B
+						\\
+						\widetilde{\vHam}_{\chi(f)} =& \vHam_f
+					\end{cases}
+				\end{displaymath}
+		\item<3-> Then
+			\begin{align*}
+				d \chi(f) &= - \iota_{\vHam_f}\omega - d \iota_{\vHam_f} B \\
+				\parallel & \\
+				-\iota_{\widetilde{\vHam}_{\chi(f)}} \widetilde{\omega} &= -\iota_{\vHam_f} \omega + \iota_{\vHam_f} d B
+			\end{align*}
+		\item<4-> I.e. $$\mathcal{L}_{\vHam_f} B = 0 ~ \forall f \in C^\infty(M) \qquad \qquad \text{\alert{contradiction!}}$$
+	\end{itemize}
+	\hfill \hyperlink{frame:pentagonMotivation}{\color{gray}$[<<]$}%\beamerskipbutton{}}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}\label{frame:pentagonMotivation}
+	%
+	%Consider two \alert{gauge-related} symplectic mfd. $(M,\omega)$ and $ (M,\widetilde{\omega})$.
+	We end up with a pentagonal diagram ...
 	%
@@
 			\begin{itemize}
-				\item<2->[•] It's a framework for comparing gauge-related observables.
+				\item<2->[•] It's a framework for comparing gauge-related observables (same cohomology class).
 				\item<3->[•] It has a geometric interpration when $\omega$ \alert{prequantizable}.
+				\hfill \hyperlink{frame:pentagonPrequantum}{\color{gray}$[>>]$}%\beamerskipbutton{}}
 			\end{itemize}
@@
 	\end{minipage}
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	Details on the prequantum side.
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[t]{Scope of the talk}
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Pentagonal diagram in the \emph{prequantizable} case}\label{frame:pentagonPrequantum}
+	Assume $\omega$ is \alert{prequantizable}:
+	\pause
+	%
+		\begin{columns}
+			\begin{column}{.6\linewidth}
+				\begin{itemize}
+					\item<2-> $\pi:P\to M$ \small associated $S^1$ bundle;
+					\item<3-> $E\in \mathfrak{X}(P)$ \small fundamental v.f. of $S^1\curvearrowright P$;
+					\item<4-> $\theta\in \Omega^1(P)^{S^1}$ \small connection $1$-form  s.t. $d \theta = \pi^\ast \omega$.
+				\end{itemize}
+			\end{column}
+			\begin{column}{.4\linewidth}
+				\begin{center}
+					\includestandalone[width=1\textwidth]{Pictures/Frame_prequantum}
+				\end{center}	
+			\end{column}
+		\end{columns}
+	\pause \pause \vfill
+	The Lie algebra map
+	\begin{displaymath}
+		\big(C^\infty(M),\{\cdot,\cdot\}_\omega\big) \xrightarrow{\Psi_\omega} 
+		\big(\Gamma(TM\oplus\mathbb{R}),[\cdot,\cdot]_\omega\big)
+	\end{displaymath}
+	%
+	\vfill
+	factors through the Lie algebra of \emph{\alert{infinitesimal quanto-morphisms}}
+	%
+	\pause
+	\begin{displaymath}
+		Q(P,\theta)= \left \lbrace 
+			Y \in \mathfrak{X}(P) 
+			~ \Big\vert ~
+			\mathcal{L}_Y \theta = 0
+			\right \rbrace~.
+	\end{displaymath}
+
+	\hfill \hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}%\beamerskipbutton{}}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Pentagonal diagram in the \emph{prequantizable} case \hfill (cont.)}
+	\begin{center}
+			\includestandalone[width=.8\textwidth]{Pictures/Frame_prequantumDiagram}
+	\end{center}	
+	\vfill
+	\begin{enumerate}
+		\item<2-> Start from the prequantization map (isomorphism)
+					$$\textrm{Preq}_\theta: f \mapsto \vHam_f^{Hor \theta} + (\pi^\ast f ) E $$
+					\hfill {\tiny ( where $Hor \theta$ is the horizontal lift);}
+		\item<3-> Observe that $Q(P,\theta) \subset \mathfrak{X}^{S^1}$;
+		\item<4-> By definition, $\mathfrak{X}^{S^1}= \Gamma(\textrm{at}(P))$ where $\textrm{at}(P)$ is the Atiyah Lie algebroid associated to the principal bundle $P\to M$.
+		\item<5-> $\textrm{at}(P)$ is defined by the s.e.s. $0\to \mathbb{R} \to \textrm{at}(P) \to TM \to 0$,
+		\\ $\theta$ provides a splitting, i.e. an isomorphism
+		\begin{displaymath}
+			\morphism{\sigma_\theta}{TM\oplus \mathbb{R}}{\textrm{at}(P)}
+			{\binom{v}{c}}{v^{Hor \theta} + c \cdot E}~.
+		\end{displaymath}
+	\end{enumerate}
+
+	\hfill \hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}%\beamerskipbutton{}}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[t]{Scope of the talk}\label{frame:scopeTalk}
 		\begin{center}
@@
 
-\begin{frame}[fragile]{Multisymplectic manifolds - motivations} %Fragile -->workaround tikzcd
+\begin{frame}[fragile]{Multisymplectic manifolds - mechanics perspective} %Fragile -->workaround tikzcd
+	\label{frame:hystMS}
 	\begin{block}{Historical motivation}
@@
 	\end{table}		 
+ 	\hfill \hyperlink{frame:GIMMSY_construction}{\color{gray}$[>>]$}%\beamerskipbutton{}}
 
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	Details on the GIMMSY Construction
-
-	Mention Blohmann for the higher case
+\begin{frame}[fragile]{A multisymplectic manifold in Lagrangian Field Theory}\label{frame:GIMMSY_construction}
+	\begin{center}
+		\includestandalone[width=.5\textwidth]{Pictures/Frame_GIMMSY}
+	\end{center}	
+	\vfill
+
+	Consider a \emph{\bf{first-order Lagrangian Field Theory}}:
+	\begin{itemize}
+		\item<1-> {\color{blue} Kinematics} is encoded by a {\color{blue} \emph{configuration bundle}};
+		\item<2-> {\color{red} Dynamics} is encoded by a {\color{red} \emph{Lagrangian density}};
+		\item<3-> The {\color{orange} multicontangent bundle} is naturally $n$-plectic with $\omega := d \theta$ and \\
+		$\theta \in \Omega^n(\Lambda)$ the tautological $n$-form
+		{\small
+		\begin{displaymath}
+			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
+			= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
+			\qquad \qquad \forall \eta \in \wedge^n T^* E \, , \: \forall u_i \in T_\eta (\wedge^n T^* E) 		
+		\end{displaymath}
+		}
+		\item<4-> The multisymplectic $(n+1)$-form is pulled back to $J^1 E$ through the \emph{Legendre transformation} $\mathbb{F}\Lag: J^1 E \to (J^1 E)^\ostar$
+    given intrinsically by
+    {\small
+		\begin{displaymath}
+        		\Big\langle \mathbb{F}\mathcal{L}(\gamma),\gamma'\Big\rangle=
+        		\mathcal{L}\Big(\gamma\Big) + \frac{ d}{ d \epsilon}\mathcal{L}\Big(\gamma +\epsilon(\gamma'-\gamma)\Big)\Bigg\vert_{\epsilon=0} \qquad \forall \gamma,\gamma' \in J^1 E
+    		\end{displaymath}
+    }
+
+    %
+	\end{itemize}
+	%
+	\vfill
+	\hfill \hyperlink{frame:hystMS}{\color{gray}$[<<]$}%\beamerskipbutton{}}
 \end{frame}
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	Details on the controversial notion
-
-	pdv meccanico: sono misurabili?
-
-	pdv matematico: perchè questa è preferibile a struttura di Leibniz (check che sia la stessa usata da gimsy e spagnoli)
+\begin{frame}[fragile,shrink]{Multisymplectic Observables - a controversial notion}
+	\begin{block}{ Much debate about the "correct" mathematical of \emph{multisymplectic observables}}
+		\begin{itemize}
+			\item A crucial step for quantization schemes.
+			\item Obstructed adoption of this formalism in mechanics.
+		\end{itemize}	
+	\end{block}		
+	%
+	\vspace{1.5em} \pause
+	\begin{block}{ At least a second competing notion of \emph{multisymplectic observables algebra}}
+		\begin{displaymath}
+			Leib(M,\omega) = \Big( \Omega_{ham}^{n-1}(M,\omega), \llbracket\cdot,\cdot\rrbracket \Big)
+		\end{displaymath}
+		with the binary bracket 
+		\begin{center}
+			\includestandalone{Pictures/Equation_Leibbracket}	
+		\end{center}
+	\end{block}	
+	\vspace{1em} \pause
+	\begin{block}{Open Questions:}
+		\begin{itemize}
+			\item How are the two concepts related?
+			\item Do they give what is physically expected to be called an \emph{measurable quantity}?
+				\\
+				(Folklore conjecture: No, they only give \emph{local observables})				
+		\end{itemize}
+	\end{block}
 \end{frame}
@@
 				\centering \it
-				\onslide<2->{
 				$\quad\omega,~ \tilde{\omega}~ \in \Omega^{n+1}(M)$ multisymplectic,
-				}
 			\end{column}	
@@
 				\centering \it
-				\onslide<3->{			
 				such that $\omega = \tilde{\omega} - d B$
-				}
 			\end{column}	
@@
 	\vfill
-	\pause
 	%
@@
 			\begin{column}{.325\linewidth}
-					\onslide<5->{
+					\onslide<4->{
 						\begin{displaymath}
@@
 			\begin{column}{.625\linewidth}	
-					\onslide<5->{
+					\onslide<4->{
 						\begin{displaymath}
@@
 		\bigskip
-		\only<5->{
+		\only<4->{
 			\begin{tikzpicture}[overlay,remember picture]

### 2024-02-26 msgauge-Caprarola.tex
Slides Caprarola - slides done - narrative todo.

@@
 %- D0cum3nt ----------------------------------------------------------------------------------------------
-\documentclass[10pt,handout]{beamer}
+\documentclass[10pt]{beamer}
 
@@
 \usepackage{fontawesome}
+\usepackage{amsfonts}
 
@@
 	\end{itemize}
-	\hfill \hyperlink{frame:pentagonMotivation}{\color{gray}$[<<]$}%\beamerskipbutton{}}
+	\hfill \onslide<4->{\hyperlink{frame:pentagonMotivation}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
 \end{frame}
@@
 	\pause \pause \vfill
+	\pause
 	The Lie algebra map
@@
 
-	\hfill \hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}%\beamerskipbutton{}}
+	\hfill \onslide<5->{\hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
 \end{frame}
@@
 		}
-		\item<4-> The multisymplectic $(n+1)$-form is pulled back to $J^1 E$ through the \emph{Legendre transformation} $\mathbb{F}\Lag: J^1 E \to (J^1 E)^\ostar$
+		\item<4-> The multisymplectic $(n+1)$-form is pulled back to $J^1 E$ through the \emph{Legendre transformation} $\mathbb{F}\mathcal{L} J^1 E \to (J^1 E)^\circledast$
     given intrinsically by
@@
 	\vfill
-	\hfill \hyperlink{frame:hystMS}{\color{gray}$[<<]$}%\beamerskipbutton{}}
+	\hfill \onslide<4->{\hyperlink{frame:hystMS}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
 \end{frame}
@@
 	\begin{itemize}
-		\item<6-> $(n=1) ~ \Rightarrow$ standard twisted \emph{Lie algebroid};
-		\item<7-> $(n=2) ~ \Rightarrow$ standard twisted \emph{Courant algebroid};
-	\end{itemize}
-
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Vinogradov $L_\infty$-algebra}
+		\item<6-> $(n=1) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $2$-form)}  \emph{Lie algebroid};
+		\item<7-> $(n=2) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $3$-form)} \emph{Courant algebroid};
+	\end{itemize}
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Vinogradov $L_\infty$-algebra}\label{frame:VinoLinfty}
 	Vin. alg.oids 
@@
 	}
-
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
-	Details sulla ricetta di Zambon per costruire questa Lie infinito algebra.
+	\hfill \onslide<6->{\hyperlink{frame:VinoDetails}{\color{gray}$[>>]$}}%\beamerskipbutton{}}
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[t,fragile,shrink=20]{Details on the Vinogradov $L_\infty$-algebra Construction}\label{frame:VinoDetails}
+	%
+	\begin{enumerate}[<+-| alert@+>]
+		\setlength\itemsep{2em}
+		\item Consider the \emph{Graded manifold}
+		 $$ Q = T^\ast[n] T[1] M $$
+		 call $\mathcal{C}$ the corresponding algebra of functions.
+		\item $Q$ is a (shifted) contangent, hence it's naturally Poisson
+		 $$ (\mathcal{C},\cdot,\{\cdot,\cdot\}) \qquad \text{is a Poisson $n$-algebra}~;.$$
+		\item consider coordinates on $Q\sim (x^i,v_i, P_i, p_i)$ with
+			$$ |x^i|=0,~ |v^i|=1,~ |P_i|=n, ~ |p_i|=n-1 ~;$$
+		\item The degree $n+1$ function $\mathcal{S}= \sum_i v_i P_i$ encoding the de Rham differential satisfies
+			$\{\mathcal{S},\mathcal{S}\}=0$. Hence
+			 $$ (\mathcal{C}[n],\delta=\{\mathcal{S},\cdot\},\{\cdot,\cdot\}) \qquad \text{is a DGLA}~;$$
+		\item Apply Getzler \cite{Getzler1991} and Fiorenza-Manetti \cite{Fiorenza2006}  \emph{Cone costruction} to the DGLA, one gets a $L_\infty$ algebra on the non-negative truncation of $\mathcal{C}[n]$ given by
+		\begin{displaymath}
+			\begin{tikzcd}[column sep= small,row sep=small]
+				0 \ar[r,] & C^\infty(M) \ar["d",r] &
+				\Omega^1(M) \ar["d",r] & \cdots \ar[r]
+				& \Omega^{n-2}(M) \ar[r]& \Omega^{n-1}(M)\oplus \mathfrak{X}(M) \ar[r] & 0
+			\end{tikzcd}
+		\end{displaymath}			 
+			via derived brackets.	
+	\end{enumerate}
+	\hfill \onslide<5->{\hyperlink{frame:VinoLinfty}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
 \end{frame}
@@
 	}
-
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{TODO}
+	\hfill \onslide<4->{\hyperlink{frame:thankyouslide}{\color{gray}$[\beamerskipbutton{}]$} }
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%##################################################################################
+\begin{frame}
+	\begin{center}
+	\Huge\emph{Outlook}
+	\end{center}
+\end{frame}
+\addtocounter{framenumber}{-1}
+%##################################################################################
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{A bigger picture about Multisymplectic observables}
 	OUTLOOK. La big picture. 
@@
 
+%-------------------------------------------------------------------------------------------------------------------------------------------------
 	\begin{frame}{}
@@
 	\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 \appendix
+\renewcommand{\insertframenumber}{\Alph{framenumber}}
 
@@
 %------------------------------------------------------------------------------------------------
+%##################################################################################
+\begin{frame}
+	\begin{center}
+	\Huge\emph{Supplementary Material}
+	\end{center}
+\end{frame}
+\addtocounter{framenumber}{-1}
+%##################################################################################
 

### 2024-02-27 msgauge-Caprarola.tex
Caprarola - Finished slides

@@
 
-%%-------------------------------------------------------------------------------------------------------------------------------------------------
-%\begin{frame}[fragile]{A \emph{pentagonal} diagram in symplectic geometry}
-%	Given a \alert{symplectic mfd.} $(M,\omega)$ ...
-%	\vfill
-%	\begin{center}
-%		\includestandalone[width=.95\textwidth]{Pictures/Frame_Embedding_Diagram_symplectic}
-%	\end{center}
-%	\vspace{3em}
-%	\vfill
-%	\begin{minipage}[t][8.5em][t]{\textwidth}
-%		\begin{itemize}
-%			\item<1-> \alert<1>{... there is a naturally associated Poisson algebra ...}
-%			\item<2-> \alert<2>{... and also a (standard twisted) Lie Algebroid}.
-%			\item<3-> A Lie algebroid is a "controlled" \alert<3>{$\infty$-dimensional Lie algebra.}
-%			\item[]<4->
-%				\quad\\
-%		\vspace{-.75em}
-%		\tcbset{colback=white,
-%		colbacktitle=white,
-%		colframe=red!70!black,
-%		boxrule=1pt,
-%		colupper=red!70!black,
-%		arc=15pt,
-%		}
-%		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-%			\color{blue}{
-%			\textbf{Lemma}: There exists an embedding of Lie Algebras.
-%			}
-%		\end{tcolorbox}
-%		\end{itemize}
-%	\end{minipage}
-%\end{frame}
-%%-------------------------------------------------------------------------------------------------------------------------------------------------
-
 %-------------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-%%-------------------------------------------------------------------------------------------------------------------------------------------------
-%\begin{frame}[fragile]{Compatibility between gauge transformations and comoment maps}
-%	%
-%	Consider $(M,\omega)$ \alert{symplectic mfd.}
-%	%
-%	\begin{center}
-%			\includestandalone[width=.8\textwidth]{Pictures/Frame_BigDiagram_symplectic}
-%	\end{center}
-%	%
-%	\vspace{-1em}
-%	\vfill
-%	\begin{minipage}[t][8em][t]{\textwidth}
-%		\begin{itemize}
-%			\only<2>{
-%				\item<2-> Consider a second gauge-related symplectic structure on $M$
-%					\begin{displaymath}
-%						\tilde{\omega} = \omega + d B \qquad \text{with} \quad B\in \Omega^1(M).
-%					\end{displaymath}
-%			}
-%			\only<3-4>{
-%				\item<3-> There is a natural isomorphism in the Lie Alg.oids category \emph{($B$-transformation)}
-%					\begin{displaymath}
-%						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
-%					\end{displaymath}
-%			}
-%			\only<6-7>{
-%				\item<6-> Consider an infinitesimal group action $\mathfrak{g}\circlearrowleft M$ which is Hamiltonian w.r.t. both $\omega$ and $\tilde{\omega}$.
-%				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
-%				\begin{displaymath}
-%					\tilde{f}(\xi) = f(\xi) - \iota_{\underline{\xi}}B
-%				\end{displaymath}
-%				}
-%			\item[]						
-%		\end{itemize}
-%	\only<5>{
-%		\vspace{-.75em}
-%		\begin{center}
-%		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
-%			\alert{
-%			\faQuestionCircle \qquad
-%				{How can we close the left-hand side?}
-%			\qquad \faQuestionCircle		
-%			}
-%		}
-%		\end{center}
-%	}
-%	\only<8->{
-%		\vspace{-.75em}
-%		\tcbset{colback=white,
-%		colbacktitle=white,
-%		colframe=red!70!black,
-%		boxrule=1pt,
-%		colupper=red!70!black,
-%		arc=15pt,
-%		}
-%		\begin{tcolorbox}[enhanced,frame hidden,borderline={0.5pt}{0pt}{blue}]
-%			\color{blue}{
-%			Lemma: The central pentagon commutes!
-%			}
-%		\end{tcolorbox}
-%	\vfill
-%	}
-%	\only<9->{
-%		\vspace{-.75em}
-%		\begin{center}
-%		\tcbox[enhanced,frame hidden,borderline={0.5pt}{0pt}{red,dashed}]{	
-%			\alert{
-%			\faQuestionCircle \qquad
-%				{What happens in the higher (n-plectic) case?}
-%			\qquad \faQuestionCircle		
-%			}
-%		}
-%		\end{center}
-%	}
-%	\end{minipage}	
-%\end{frame}
-%\note[itemize]{
-%	\item The horizontal embedding is  $f \mapsto (v_f,f)$;
-%	\item Vertical maps are also known as \emph{Gauge transformations}
-%	\item upshot: 
-%	\begin{enumerate}
-%		\item 
-%	\end{enumerate}
-%}
-%%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Why not a direct vertical arrow?}\label{frame:whyNoVertArrow}
-	\begin{center}
-			\includestandalone[width=.7\textwidth]{Pictures/Frame_BigDiagram_verticalArrow}
-	\end{center}
-	\vfill
-	\begin{itemize}
-		\item<2-> Assume exists \alert<2>{$\chi:C^\infty(M)_\omega \to C^\infty(M)_{\widetilde{\omega}}$} ~s.t. the square commutes.
-				\begin{displaymath}
-					\begin{cases}
-						\chi(f) =& f - \iota_{\vHam_f} B
-						\\
-						\widetilde{\vHam}_{\chi(f)} =& \vHam_f
-					\end{cases}
-				\end{displaymath}
-		\item<3-> Then
-			\begin{align*}
-				d \chi(f) &= - \iota_{\vHam_f}\omega - d \iota_{\vHam_f} B \\
-				\parallel & \\
-				-\iota_{\widetilde{\vHam}_{\chi(f)}} \widetilde{\omega} &= -\iota_{\vHam_f} \omega + \iota_{\vHam_f} d B
-			\end{align*}
-		\item<4-> I.e. $$\mathcal{L}_{\vHam_f} B = 0 ~ \forall f \in C^\infty(M) \qquad \qquad \text{\alert{contradiction!}}$$
-	\end{itemize}
-	\hfill \onslide<4->{\hyperlink{frame:pentagonMotivation}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
 %-------------------------------------------------------------------------------------------------------------------------------------------------
@@
 
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Pentagonal diagram in the \emph{prequantizable} case}\label{frame:pentagonPrequantum}
-	Assume $\omega$ is \alert{prequantizable}:
-	\pause
-	%
-		\begin{columns}
-			\begin{column}{.6\linewidth}
-				\begin{itemize}
-					\item<2-> $\pi:P\to M$ \small associated $S^1$ bundle;
-					\item<3-> $E\in \mathfrak{X}(P)$ \small fundamental v.f. of $S^1\curvearrowright P$;
-					\item<4-> $\theta\in \Omega^1(P)^{S^1}$ \small connection $1$-form  s.t. $d \theta = \pi^\ast \omega$.
-				\end{itemize}
-			\end{column}
-			\begin{column}{.4\linewidth}
-				\begin{center}
-					\includestandalone[width=1\textwidth]{Pictures/Frame_prequantum}
-				\end{center}	
-			\end{column}
-		\end{columns}
-	\pause \pause \vfill
-	\pause
-	The Lie algebra map
-	\begin{displaymath}
-		\big(C^\infty(M),\{\cdot,\cdot\}_\omega\big) \xrightarrow{\Psi_\omega} 
-		\big(\Gamma(TM\oplus\mathbb{R}),[\cdot,\cdot]_\omega\big)
-	\end{displaymath}
-	%
-	\vfill
-	factors through the Lie algebra of \emph{\alert{infinitesimal quanto-morphisms}}
-	%
-	\pause
-	\begin{displaymath}
-		Q(P,\theta)= \left \lbrace 
-			Y \in \mathfrak{X}(P) 
-			~ \Big\vert ~
-			\mathcal{L}_Y \theta = 0
-			\right \rbrace~.
-	\end{displaymath}
-
-	\hfill \hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}%\beamerskipbutton{}}
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Pentagonal diagram in the \emph{prequantizable} case \hfill (cont.)}
-	\begin{center}
-			\includestandalone[width=.8\textwidth]{Pictures/Frame_prequantumDiagram}
-	\end{center}	
-	\vfill
-	\begin{enumerate}
-		\item<2-> Start from the prequantization map (isomorphism)
-					$$\textrm{Preq}_\theta: f \mapsto \vHam_f^{Hor \theta} + (\pi^\ast f ) E $$
-					\hfill {\tiny ( where $Hor \theta$ is the horizontal lift);}
-		\item<3-> Observe that $Q(P,\theta) \subset \mathfrak{X}^{S^1}$;
-		\item<4-> By definition, $\mathfrak{X}^{S^1}= \Gamma(\textrm{at}(P))$ where $\textrm{at}(P)$ is the Atiyah Lie algebroid associated to the principal bundle $P\to M$.
-		\item<5-> $\textrm{at}(P)$ is defined by the s.e.s. $0\to \mathbb{R} \to \textrm{at}(P) \to TM \to 0$,
-		\\ $\theta$ provides a splitting, i.e. an isomorphism
-		\begin{displaymath}
-			\morphism{\sigma_\theta}{TM\oplus \mathbb{R}}{\textrm{at}(P)}
-			{\binom{v}{c}}{v^{Hor \theta} + c \cdot E}~.
-		\end{displaymath}
-	\end{enumerate}
-
-	\hfill \onslide<5->{\hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
 \end{frame}
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{A multisymplectic manifold in Lagrangian Field Theory}\label{frame:GIMMSY_construction}
-	\begin{center}
-		\includestandalone[width=.5\textwidth]{Pictures/Frame_GIMMSY}
-	\end{center}	
-	\vfill
-
-	Consider a \emph{\bf{first-order Lagrangian Field Theory}}:
-	\begin{itemize}
-		\item<1-> {\color{blue} Kinematics} is encoded by a {\color{blue} \emph{configuration bundle}};
-		\item<2-> {\color{red} Dynamics} is encoded by a {\color{red} \emph{Lagrangian density}};
-		\item<3-> The {\color{orange} multicontangent bundle} is naturally $n$-plectic with $\omega := d \theta$ and \\
-		$\theta \in \Omega^n(\Lambda)$ the tautological $n$-form
-		{\small
-		\begin{displaymath}
-			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
-			= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
-			\qquad \qquad \forall \eta \in \wedge^n T^* E \, , \: \forall u_i \in T_\eta (\wedge^n T^* E) 		
-		\end{displaymath}
-		}
-		\item<4-> The multisymplectic $(n+1)$-form is pulled back to $J^1 E$ through the \emph{Legendre transformation} $\mathbb{F}\mathcal{L} J^1 E \to (J^1 E)^\circledast$
-    given intrinsically by
-    {\small
-		\begin{displaymath}
-        		\Big\langle \mathbb{F}\mathcal{L}(\gamma),\gamma'\Big\rangle=
-        		\mathcal{L}\Big(\gamma\Big) + \frac{ d}{ d \epsilon}\mathcal{L}\Big(\gamma +\epsilon(\gamma'-\gamma)\Big)\Bigg\vert_{\epsilon=0} \qquad \forall \gamma,\gamma' \in J^1 E
-    		\end{displaymath}
-    }
-
-    %
-	\end{itemize}
-	%
-	\vfill
-	\hfill \onslide<4->{\hyperlink{frame:hystMS}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
 \section{What is the \textbf{higher analogue} of the \textbf{Poisson algebra}?}
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile,shrink]{Multisymplectic Observables - a controversial notion}
-	\begin{block}{ Much debate about the "correct" mathematical of \emph{multisymplectic observables}}
-		\begin{itemize}
-			\item A crucial step for quantization schemes.
-			\item Obstructed adoption of this formalism in mechanics.
-		\end{itemize}	
-	\end{block}		
-	%
-	\vspace{1.5em} \pause
-	\begin{block}{ At least a second competing notion of \emph{multisymplectic observables algebra}}
-		\begin{displaymath}
-			Leib(M,\omega) = \Big( \Omega_{ham}^{n-1}(M,\omega), \llbracket\cdot,\cdot\rrbracket \Big)
-		\end{displaymath}
-		with the binary bracket 
-		\begin{center}
-			\includestandalone{Pictures/Equation_Leibbracket}	
-		\end{center}
-	\end{block}	
-	\vspace{1em} \pause
-	\begin{block}{Open Questions:}
-		\begin{itemize}
-			\item How are the two concepts related?
-			\item Do they give what is physically expected to be called an \emph{measurable quantity}?
-				\\
-				(Folklore conjecture: No, they only give \emph{local observables})				
-		\end{itemize}
-	\end{block}
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
 \section{What is the \textbf{higher analogue} of the \textbf{twisted Lie algebroid}?}
@@
 
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[t,fragile,shrink=20]{Details on the Vinogradov $L_\infty$-algebra Construction}\label{frame:VinoDetails}
-	%
-	\begin{enumerate}[<+-| alert@+>]
-		\setlength\itemsep{2em}
-		\item Consider the \emph{Graded manifold}
-		 $$ Q = T^\ast[n] T[1] M $$
-		 call $\mathcal{C}$ the corresponding algebra of functions.
-		\item $Q$ is a (shifted) contangent, hence it's naturally Poisson
-		 $$ (\mathcal{C},\cdot,\{\cdot,\cdot\}) \qquad \text{is a Poisson $n$-algebra}~;.$$
-		\item consider coordinates on $Q\sim (x^i,v_i, P_i, p_i)$ with
-			$$ |x^i|=0,~ |v^i|=1,~ |P_i|=n, ~ |p_i|=n-1 ~;$$
-		\item The degree $n+1$ function $\mathcal{S}= \sum_i v_i P_i$ encoding the de Rham differential satisfies
-			$\{\mathcal{S},\mathcal{S}\}=0$. Hence
-			 $$ (\mathcal{C}[n],\delta=\{\mathcal{S},\cdot\},\{\cdot,\cdot\}) \qquad \text{is a DGLA}~;$$
-		\item Apply Getzler \cite{Getzler1991} and Fiorenza-Manetti \cite{Fiorenza2006}  \emph{Cone costruction} to the DGLA, one gets a $L_\infty$ algebra on the non-negative truncation of $\mathcal{C}[n]$ given by
-		\begin{displaymath}
-			\begin{tikzcd}[column sep= small,row sep=small]
-				0 \ar[r,] & C^\infty(M) \ar["d",r] &
-				\Omega^1(M) \ar["d",r] & \cdots \ar[r]
-				& \Omega^{n-2}(M) \ar[r]& \Omega^{n-1}(M)\oplus \mathfrak{X}(M) \ar[r] & 0
-			\end{tikzcd}
-		\end{displaymath}			 
-			via derived brackets.	
-	\end{enumerate}
-	\hfill \onslide<5->{\hyperlink{frame:VinoLinfty}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
 \end{frame}
@@
 %##################################################################################
+\section*{Outlook}
 \begin{frame}
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile,shrink]{Multisymplectic Observables - a controversial notion}
+	\begin{block}{ Much debate about the "correct" mathematical of \emph{multisymplectic observables}}
+		\begin{itemize}
+			\item A crucial step for quantization schemes.
+			\item Obstructed adoption of this formalism in mechanics.
+		\end{itemize}	
+	\end{block}		
+	%
+	\vspace{1.5em} \pause
+	\begin{block}{ At least a second competing notion of \emph{multisymplectic observables algebra}}
+		\begin{displaymath}
+			Leib(M,\omega) = \Big( \Omega_{ham}^{n-1}(M,\omega), \llbracket\cdot,\cdot\rrbracket \Big)
+		\end{displaymath}
+		with the binary bracket 
+		\begin{center}
+			\includestandalone{Pictures/Equation_Leibbracket}	
+		\end{center}
+	\end{block}	
+	\vspace{1em} \pause
+	\begin{block}{Open Questions:}
+		\begin{itemize}
+			\item How are the two concepts related?
+			\item Do they give what is physically expected to be called an \emph{measurable quantity}?
+				\\
+				(Folklore conjecture: No, they only give \emph{local observables})				
+		\end{itemize}
+	\end{block}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
 \begin{frame}[fragile]{A bigger picture about Multisymplectic observables}
-	OUTLOOK. La big picture. 
+	%
+	\begin{center}
+		\includestandalone[width=.95\textwidth]{Pictures/Frame_OutlookDiagram}
+	\end{center}
+
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Pentagonal Diagram and higher Prequantization}
+	%
+	\begin{center}
+		\includestandalone[width=.8\textwidth]{Pictures/Frame_OutlookPrequantum}
+	\end{center}		
+	\onslide<3->{
+		\small
+		\begin{block}{Partial Results in the $2$-plectic case}
+			\begin{itemize}
+				\item G. Sevestre \& T. Wurzbacher, "On the Prequantisation Map for 2-Plectic Manifolds",  \cite{Sevestre2021};
+				\item D. Djounvouna \& D. Krepski, "Infinitesimal symmetries of bundle gerbes and Courant algebroids"\cite{Djounvouna2023}.
+			\end{itemize}
+		\end{block}
+	}
 \end{frame}
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
-\begin{frame}[fragile]{Homotopy comomentum maps}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
-	\vfill
-	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)} \cite{Callies2016}]
-			\includestandalone{Pictures/Frame_Lifting}
-	\end{defblock}
-	\onslide<4->{
-	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
-			%
-			HCMM is a sequence of (graded-skew) multilinear maps:
-			\begin{displaymath}
-				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
-				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
-			\end{displaymath}
-			\emph{fulfilling:}%\emph{such that:}
-			\begin{itemize}
-				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
-				\item<6-> $d f_k (p) = f_{k-1} (
-				\tikz[baseline,remember picture]{\node[rounded corners,
-                        fill=green!5,draw=green!30,anchor=base]            
-            			(target) {$\partial $ };
-            	}				
-				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
-				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
-			\end{itemize}
-		\onslide<7->{
-			\tikz[overlay,remember picture]
-			{
-				\node[rounded corners,
-	                 draw=green!30,anchor=base]            
-	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
-			}	
-		\begin{tikzpicture}[overlay,remember picture]
-	    	\path[->] (base.west) edge[bend right,green](target.north east);
-	    \end{tikzpicture}
-	    }
-	\end{lemblock}	
-	}
-	\vfill
-\end{frame}
-%-------------------------------------------------------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------------------------------------------------------
-\subsection{Leibniz-algebra of Observables}
-\begin{frame}[fragile,t]{Leibniz-algebra of Observables}
-
-	\begin{defblock}[Leibniz algebra of observables]
-		\hspace{.25em} $Leib(M,\omega)$ is given by:
-		\begin{itemize}
-			\item[•] the vector space $$\Omega_{ham}^{n-1}(M,\omega)$$
-			\item[•] with the binary bracket 
-			\begin{center}
-				\includestandalone{Pictures/Equation_Leibbracket}	
-			\end{center}
-		\end{itemize}	
-	\end{defblock}
-	\vfill
-	\pause
-	%
-	\begin{propblock}
-		\begin{itemize}
-			\setlength\itemsep{1em}
-			\item[i.] $\vHam_{\llbracket \alpha, \beta \rrbracket} = [\vHam_\alpha,\vHam_\beta]$
-			\item[ii.] $\llbracket \sigma, \llbracket \alpha, \beta \rrbracket \rrbracket =
-			\llbracket\llbracket \sigma, \alpha \rrbracket, \beta \rrbracket
-			+
-			\llbracket \alpha, \llbracket \sigma, \beta \rrbracket \rrbracket$
-			\item[iii.] $\llbracket \alpha, \beta \rrbracket + \llbracket \beta,\alpha \rrbracket = d \left( \iota_{\vHam_\alpha} \beta + \iota_{\vHam_\beta} \alpha\right)$
-		\end{itemize}
-	\end{propblock}
-
-\end{frame}
-\note[itemize]{
-	\item in addition to being extendable to an $L_\infty$-algebra, the space $\Omega^{n-1}_{ham}(M)$ also carries the structure of a Leibniz algebra.
-This structure is very important for multisymplectic reduction procedures.
-	\item 
-	\item Take away: Two brackets on $\Omega_H^{k-1}(M)$, ${\color{red}\llbracket\alpha,\beta\rrbracket = \mathcal{L}_{X_\alpha} \beta}$ and ${\color{green}\{\alpha,\beta\}=\iota_{X_\alpha}\d\beta}$,
-	Equal up to a coboundary: ${\color{red}\mathcal{L}_{X_\alpha}\beta} = {\color{green}\iota_{X_\alpha}\d\beta} + \d\hspace{1pt}\iota_{X_\alpha}\beta$
-}
-%---------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Why not a direct vertical arrow?}\label{frame:whyNoVertArrow}
+	\begin{center}
+			\includestandalone[width=.7\textwidth]{Pictures/Frame_BigDiagram_verticalArrow}
+	\end{center}
+	\vfill
+	\begin{itemize}
+		\item<2-> Assume exists \alert<2>{$\chi:C^\infty(M)_\omega \to C^\infty(M)_{\widetilde{\omega}}$} ~s.t. the square commutes.
+				\begin{displaymath}
+					\begin{cases}
+						\chi(f) =& f - \iota_{\vHam_f} B
+						\\
+						\widetilde{\vHam}_{\chi(f)} =& \vHam_f
+					\end{cases}
+				\end{displaymath}
+		\item<3-> Then
+			\begin{align*}
+				d \chi(f) &= - \iota_{\vHam_f}\omega - d \iota_{\vHam_f} B \\
+				\parallel & \\
+				-\iota_{\widetilde{\vHam}_{\chi(f)}} \widetilde{\omega} &= -\iota_{\vHam_f} \omega + \iota_{\vHam_f} d B
+			\end{align*}
+		\item<4-> I.e. $$\mathcal{L}_{\vHam_f} B = 0 ~ \forall f \in C^\infty(M) \qquad \qquad \text{\alert{contradiction!}}$$
+	\end{itemize}
+	\hfill \onslide<4->{\hyperlink{frame:pentagonMotivation}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Pentagonal diagram in the \emph{prequantizable} case}\label{frame:pentagonPrequantum}
+	Assume $\omega$ is \alert{prequantizable}:
+	\pause
+	%
+		\begin{columns}
+			\begin{column}{.6\linewidth}
+				\begin{itemize}
+					\item<2-> $\pi:P\to M$ \small associated $S^1$ bundle;
+					\item<3-> $E\in \mathfrak{X}(P)$ \small fundamental v.f. of $S^1\curvearrowright P$;
+					\item<4-> $\theta\in \Omega^1(P)^{S^1}$ \small connection $1$-form  s.t. $d \theta = \pi^\ast \omega$.
+				\end{itemize}
+			\end{column}
+			\begin{column}{.4\linewidth}
+				\begin{center}
+					\includestandalone[width=1\textwidth]{Pictures/Frame_prequantum}
+				\end{center}	
+			\end{column}
+		\end{columns}
+	\pause \pause \vfill
+	\pause
+	The Lie algebra map
+	\begin{displaymath}
+		\big(C^\infty(M),\{\cdot,\cdot\}_\omega\big) \xrightarrow{\Psi_\omega} 
+		\big(\Gamma(TM\oplus\mathbb{R}),[\cdot,\cdot]_\omega\big)
+	\end{displaymath}
+	%
+	\vfill
+	factors through the Lie algebra of \emph{\alert{infinitesimal quanto-morphisms}}
+	%
+	\pause
+	\begin{displaymath}
+		Q(P,\theta)= \left \lbrace 
+			Y \in \mathfrak{X}(P) 
+			~ \Big\vert ~
+			\mathcal{L}_Y \theta = 0
+			\right \rbrace~.
+	\end{displaymath}
+
+	\hfill \hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}%\beamerskipbutton{}}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Pentagonal diagram in the \emph{prequantizable} case \hfill (cont.)}
+	\begin{center}
+			\includestandalone[width=.8\textwidth]{Pictures/Frame_prequantumDiagram}
+	\end{center}	
+	\vfill
+	\begin{enumerate}
+		\item<2-> Start from the prequantization map (isomorphism)
+					$$\textrm{Preq}_\theta: f \mapsto \vHam_f^{Hor \theta} + (\pi^\ast f ) E $$
+					\hfill {\tiny ( where $Hor \theta$ is the horizontal lift);}
+		\item<3-> Observe that $Q(P,\theta) \subset \mathfrak{X}^{S^1}$;
+		\item<4-> By definition, $\mathfrak{X}^{S^1}= \Gamma(\textrm{at}(P))$ where $\textrm{at}(P)$ is the Atiyah Lie algebroid associated to the principal bundle $P\to M$.
+		\item<5-> $\textrm{at}(P)$ is defined by the s.e.s. $0\to \mathbb{R} \to \textrm{at}(P) \to TM \to 0$,
+		\\ $\theta$ provides a splitting, i.e. an isomorphism
+		\begin{displaymath}
+			\morphism{\sigma_\theta}{TM\oplus \mathbb{R}}{\textrm{at}(P)}
+			{\binom{v}{c}}{v^{Hor \theta} + c \cdot E}~.
+		\end{displaymath}
+	\end{enumerate}
+
+	\hfill \onslide<5->{\hyperlink{frame:scopeTalk}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
 
@@
 
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{A multisymplectic manifold in Lagrangian Field Theory}\label{frame:GIMMSY_construction}
+	\begin{center}
+		\includestandalone[width=.5\textwidth]{Pictures/Frame_GIMMSY}
+	\end{center}	
+	\vfill
+
+	Consider a \emph{\bf{first-order Lagrangian Field Theory}}:
+	\begin{itemize}
+		\item<1-> {\color{blue} Kinematics} is encoded by a {\color{blue} \emph{configuration bundle}};
+		\item<2-> {\color{red} Dynamics} is encoded by a {\color{red} \emph{Lagrangian density}};
+		\item<3-> The {\color{orange} multicontangent bundle} is naturally $n$-plectic with $\omega := d \theta$ and \\
+		$\theta \in \Omega^n(\Lambda)$ the tautological $n$-form
+		{\small
+		\begin{displaymath}
+			\left[ \iota_{u_1 \wedge \ldots \wedge u_n} \theta \right]_\eta 
+			= \iota_{u_1 \wedge \ldots \wedge u_n} \pi^\ast \eta 
+			\qquad \qquad \forall \eta \in \wedge^n T^* E \, , \: \forall u_i \in T_\eta (\wedge^n T^* E) 		
+		\end{displaymath}
+		}
+		\item<4-> The multisymplectic $(n+1)$-form is pulled back to $J^1 E$ through the \emph{Legendre transformation} $\mathbb{F}\mathcal{L} J^1 E \to (J^1 E)^\circledast$
+    given intrinsically by
+    {\small
+		\begin{displaymath}
+        		\Big\langle \mathbb{F}\mathcal{L}(\gamma),\gamma'\Big\rangle=
+        		\mathcal{L}\Big(\gamma\Big) + \frac{ d}{ d \epsilon}\mathcal{L}\Big(\gamma +\epsilon(\gamma'-\gamma)\Big)\Bigg\vert_{\epsilon=0} \qquad \forall \gamma,\gamma' \in J^1 E
+    		\end{displaymath}
+    }
+
+    %
+	\end{itemize}
+	%
+	\vfill
+	\hfill \onslide<4->{\hyperlink{frame:hystMS}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[t,fragile,shrink=20]{Details on the Vinogradov $L_\infty$-algebra Construction}\label{frame:VinoDetails}
+	%
+	\begin{enumerate}[<+-| alert@+>]
+		\setlength\itemsep{2em}
+		\item Consider the \emph{Graded manifold}
+		 $$ Q = T^\ast[n] T[1] M $$
+		 call $\mathcal{C}$ the corresponding algebra of functions.
+		\item $Q$ is a (shifted) contangent, hence it's naturally Poisson
+		 $$ (\mathcal{C},\cdot,\{\cdot,\cdot\}) \qquad \text{is a Poisson $n$-algebra}~;.$$
+		\item consider coordinates on $Q\sim (x^i,v_i, P_i, p_i)$ with
+			$$ |x^i|=0,~ |v^i|=1,~ |P_i|=n, ~ |p_i|=n-1 ~;$$
+		\item The degree $n+1$ function $\mathcal{S}= \sum_i v_i P_i$ encoding the de Rham differential satisfies
+			$\{\mathcal{S},\mathcal{S}\}=0$. Hence
+			 $$ (\mathcal{C}[n],\delta=\{\mathcal{S},\cdot\},\{\cdot,\cdot\}) \qquad \text{is a DGLA}~;$$
+		\item Apply Getzler \cite{Getzler1991} and Fiorenza-Manetti \cite{Fiorenza2006}  \emph{Cone costruction} to the DGLA, one gets a $L_\infty$ algebra on the non-negative truncation of $\mathcal{C}[n]$ given by
+		\begin{displaymath}
+			\begin{tikzcd}[column sep= small,row sep=small]
+				0 \ar[r,] & C^\infty(M) \ar["d",r] &
+				\Omega^1(M) \ar["d",r] & \cdots \ar[r]
+				& \Omega^{n-2}(M) \ar[r]& \Omega^{n-1}(M)\oplus \mathfrak{X}(M) \ar[r] & 0
+			\end{tikzcd}
+		\end{displaymath}			 
+			via derived brackets.	
+	\end{enumerate}
+	\hfill \onslide<5->{\hyperlink{frame:VinoLinfty}{\color{gray}$[<<]$}}%\beamerskipbutton{}}
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile]{Homotopy comomentum maps}
+	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  \underline{preserving the $n$-plectic form $\omega$}.
+	\vfill
+	\begin{defblock}[Homotopy comomentum map \emph{(Callies, Fregier, Rogers, Zambon)} \cite{Callies2016}]
+			\includestandalone{Pictures/Frame_Lifting}
+	\end{defblock}
+	\onslide<4->{
+	\begin{lemblock}[HCMM unfolded  \cite{Callies2016}]
+			%
+			HCMM is a sequence of (graded-skew) multilinear maps:
+			\begin{displaymath}
+				(f)  = \big\lbrace f_k: \; \Lambda^k{\mathfrak g} \to L^{1-k} \subseteq \Omega^{n-k}(M) 
+				~\big\vert~ 0\leq k \leq n+1  \big\rbrace
+			\end{displaymath}
+			\emph{fulfilling:}%\emph{such that:}
+			\begin{itemize}
+				\item<5-> $f_0 = 0 $, $f_{n+1} = 0$
+				\item<6-> $d f_k (p) = f_{k-1} (
+				\tikz[baseline,remember picture]{\node[rounded corners,
+                        fill=green!5,draw=green!30,anchor=base]            
+            			(target) {$\partial $ };
+            	}				
+				p)  - (-1)^{\frac{k(k+1)}{2}} \iota(v_p) \omega 
+				\qquad\scriptstyle \forall p \in \Lambda^k(\mathfrak{g}),\; \forall k=1,\dots n+1$
+			\end{itemize}
+		\onslide<7->{
+			\tikz[overlay,remember picture]
+			{
+				\node[rounded corners,
+	                 draw=green!30,anchor=base]            
+	            	 (base) at ($(current page.east)-(3,3)$) [rotate=-0,align=center] {\footnotesize{\hyperlink{frame:CE-complex}{\emph{Chevalley-Eilenberg boundary op.}}}};
+			}	
+		\begin{tikzpicture}[overlay,remember picture]
+	    	\path[->] (base.west) edge[bend right,green](target.north east);
+	    \end{tikzpicture}
+	    }
+	\end{lemblock}	
+	}
+	\vfill
+\end{frame}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{frame}[fragile,t]{Leibniz-algebra of Observables}
+
+	\begin{defblock}[Leibniz algebra of observables]
+		\hspace{.25em} $Leib(M,\omega)$ is given by:
+		\begin{itemize}
+			\item[•] the vector space $$\Omega_{ham}^{n-1}(M,\omega)$$
+			\item[•] with the binary bracket 
+			\begin{center}
+				\includestandalone{Pictures/Equation_Leibbracket}	
+			\end{center}
+		\end{itemize}	
+	\end{defblock}
+	\vfill
+	\pause
+	%
+	\begin{propblock}
+		\begin{itemize}
+			\setlength\itemsep{1em}
+			\item[i.] $\vHam_{\llbracket \alpha, \beta \rrbracket} = [\vHam_\alpha,\vHam_\beta]$
+			\item[ii.] $\llbracket \sigma, \llbracket \alpha, \beta \rrbracket \rrbracket =
+			\llbracket\llbracket \sigma, \alpha \rrbracket, \beta \rrbracket
+			+
+			\llbracket \alpha, \llbracket \sigma, \beta \rrbracket \rrbracket$
+			\item[iii.] $\llbracket \alpha, \beta \rrbracket + \llbracket \beta,\alpha \rrbracket = d \left( \iota_{\vHam_\alpha} \beta + \iota_{\vHam_\beta} \alpha\right)$
+		\end{itemize}
+	\end{propblock}
+
+\end{frame}
+\note[itemize]{
+	\item in addition to being extendable to an $L_\infty$-algebra, the space $\Omega^{n-1}_{ham}(M)$ also carries the structure of a Leibniz algebra.
+This structure is very important for multisymplectic reduction procedures.
+	\item 
+	\item Take away: Two brackets on $\Omega_H^{k-1}(M)$, ${\color{red}\llbracket\alpha,\beta\rrbracket = \mathcal{L}_{X_\alpha} \beta}$ and ${\color{green}\{\alpha,\beta\}=\iota_{X_\alpha}\d\beta}$,
+	Equal up to a coboundary: ${\color{red}\mathcal{L}_{X_\alpha}\beta} = {\color{green}\iota_{X_\alpha}\d\beta} + \d\hspace{1pt}\iota_{X_\alpha}\beta$
+}
+%---------------------------------------------------------------------------------------------------------------------------------------------------
+
 %------------------------------------------------------------------------------------------------

### 2024-02-27 msgauge-Caprarola.tex
Corrected overlays

@@
 	\begin{table}
-		\ifHandout
-		%
-		\else
-		\only<2>{
 		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
@@
             \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra &  \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map &  
-            \\
-            \hline
-  \multicolumn{1}{c}{}
-            &  \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{point-like particles systems}}$} 
-            &  \multicolumn{1}{@{}c@{}}{}              \\
-		\end{tabular}
-		}
-		\fi
-		\onslide<3->{
-		\begin{tabular}{|p{0.2\textwidth}|p{0.3\textwidth}|p{0.35\textwidth}|} 
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{mechanics} & \multicolumn{2}{c|}{geometry} \\
-            \hline
-            \parbox[][20pt][c]{0.2\textwidth}{phase space} & symplectic manifold & multisymplectic manifold \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{classical \\ observables} & Poisson algebra & $L_\infty$-algebra \\[.25em]
-            \parbox[][20pt][c]{0.2\textwidth}{symmetries} &  group actions admitting comoment map & group actions admitting (homotopy) comomentum map
+            \parbox[][20pt][b]{0.2\textwidth}{phase space} 
+            &\onslide<2->{symplectic manifold}
+            &\onslide<3->{multisymplectic manifold}
+            \\[.25em]
+            \parbox[][20pt][b]{0.2\textwidth}{classical \\ observables} 
+            &\onslide<2->{Poisson algebra}
+            &\onslide<3->{$L_\infty$-algebra}
+            \\[.25em]
+            \parbox[][20pt][b]{0.2\textwidth}{symmetries} 
+            &\onslide<2->{group actions admitting comoment map}
+            &\onslide<3->{group actions admitting (homotopy) comomentum map}
             \\
@@
             \multicolumn{1}{@{}c@{}}{$\underbrace{\hspace*{.3\textwidth}}_{\text{field-theoretic systems}}$}
-               \\
 		\end{tabular}
-		}
 	\end{table}		 
+	\pause
  	\hfill \hyperlink{frame:GIMMSY_construction}{\color{gray}$[>>]$}%\beamerskipbutton{}}

### 2024-02-28 msgauge-Caprarola.tex
Addendum by MZ.

@@
 
+\usepackage{pdfpages} %copy from other sources
+
 %--Beamer Style----------------------------------------------------------------------------------------
@@
 
+\setbeamercovered{transparent}
 %-------------------------------------------------------------------------------------------------------------------------------------------------
@@
 %-------------------------------------------------------------------------------------------------------------------------------------------------
+\setbeamercovered{invisible}
 
@@
 			\item<2-> a \alert<2>{(standard twisted) Lie Algebroid};
-			\item<3->[-] A Lie algebroid is a "controlled" $\infty$-dimensional Lie algebra w/
+			\item<3->[-] A Lie algebroid is a "controlled" $\infty$-dimensional \alert<3>{Lie algebra} w/
 			\begin{displaymath}
@@
 						\binom{x}{f} \mapsto \binom{x}{f-\iota_x B} ~.
-					\end{displaymath}~.
+					\end{displaymath}
 				\item<4-> It descends to an \alert<4>{isomorphism of Lie algebras}.
@@
 				\item<6-> \vspace{-2em}Consider an infinitesimal \alert<6>{Hamiltonian group action} $\mathfrak{g}\curvearrowright M$ w.r.t. both $\omega$ and $\tilde{\omega}$.
-				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two comoment map s.t.
+				\item<7-> let be $f:\mathfrak{g} \to C^\infty(M)_\omega$ and $\tilde{f}:\mathfrak{g} \to C^\infty(M)_{\tilde{\omega}}$ two \alert<7>{comoment maps} s.t.
 				\begin{displaymath}
@@
 	\begin{center}
-			\includestandalone[width=.8\textwidth]{Pictures/hyb-image_BigDiagram_symplectic}
+			\includestandalone[width=.95\textwidth]{Pictures/hyb-image_BigDiagram_symplectic}
 	\end{center}
@@
 			\begin{itemize}
-				\item[\cmark] Skew-symmetric;
+				\item[\cmark] Skew-symmetric brakets;
 				\item[\cmark] multiplication of observables;
@@
 			\begin{itemize}
-				\item[\cmark] Skew-symmetric;
+				\item[\cmark] Skew-symmetric brackets;
 				\item[\xmark] multiplication of observables;
@@
 		\begin{center}
-			\includestandalone{Pictures/Frame_Observables}
+			\includestandalone[width=0.95\textwidth]{Pictures/Frame_Observables}
 		\end{center}
@@
 	\begin{itemize}
-		\item<6-> $(n=1) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $2$-form)}  \emph{Lie algebroid};
-		\item<7-> $(n=2) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $3$-form)} \emph{Courant algebroid};
+		\item<5-> $(n=1) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $2$-form)}  \emph{Lie algebroid};
+		\item<5-> $(n=2) ~ \Rightarrow$ standard twisted {\small \color{UniGreen} (by a closed $3$-form)} \emph{Courant algebroid};
 	\end{itemize}
@@
 	\vfill
-	\only<6->{
+	\only<3->{
 		\tikz[overlay,remember picture]
@@
                  fill=gray!1,draw=gray!30,anchor=base]            
-            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] { \footnotesize{\color{gray}{
+            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] {
+            	 \footnotesize{\color{gray}{
+            	 \onslide<4->{
             	 	$e_i = \binom{X_i}{\alpha_i} \in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)$ 
             	 	\quad~,\qquad
+            	 }
             	 $f_i \in \bigoplus_{k=0}^{n-2}\Omega^k(M)$.
@@
 \begin{frame}[t]{Comoment maps}
-	Consider a Lie algebra action $v:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
+	Consider a Lie algebra action $\underline{\,\cdot\,}:\mathfrak{g} \to \mathfrak{X}(M)$  preserving the $n$-plectic form $\omega$,
 	\vfill
@@
 					such that
-					$$ d~f (x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
+					$$ d~f (\xi) = -\iota_{\underline{\xi}} \omega \qquad \forall \xi \in \mathfrak{g}~.$$
 				\end{defblock}
@@
 					such that
-					$$ d~f_1(x) = -\iota_{v_x} \omega \qquad \forall x \in \mathfrak{g}~.$$
+					$$ d~f_1(\xi) = -\iota_{\underline{\xi}} \omega \qquad \forall \xi \in \mathfrak{g}~.$$
 				\end{defblock}	
@@
 				\small Fixed $H\in C^\infty_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant) ,
-				$$\mathcal{L}_{v_H} f(x) = 0 \qquad \forall x \in \mathfrak{g}$$
+				$$\mathcal{L}_{\vHam_H} f(\xi) = 0 \qquad \forall \xi \in \mathfrak{g}$$
 			\end{propblock}
@@
 				\small Fixed $H\in \Omega^{n-1}_{\text{Ham}}(M)$ ($\mathfrak{g}$-invariant),
-				$$\mathcal{L}_{v_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
+				$$\mathcal{L}_{\vHam_H} f_k(p) \in B^k(M) \qquad \forall p \in Z_k(\mathfrak{g})$$			
 			\end{propblock}
@@
 	%
-	Consider \quad $v:\mathfrak{g} \to \mathfrak{X}(M)$ preserving $\omega$ and $\tilde{\omega}$,
+	Consider \quad $\underline{\,\cdot\,} : \mathfrak{g} \to \mathfrak{X}(M)$ preserving $\omega$ and $\tilde{\omega}$,
 	%\phantom{consider}\quad $\mathcal{L}_{v_\xi}\omega=\mathcal{L}_{v_\xi}\tilde{\omega} = 0 \quad \forall \xi \in \mathfrak{g}$
 	\\
-	let \qquad$f: \mathfrak{g}\to L_\infty(M,\omega)$ an \emph{homotopy comoment map} ~ w.r.t. $\mathfrak{g}\circlearrowleft (M,\omega)$
+	let \qquad$f: \mathfrak{g}\to L_\infty(M,\omega)$ an \emph{homotopy comoment map} ~ w.r.t. $\mathfrak{g}\curvearrowright (M,\omega)$
 	\pause
@@
 							\& \xi_1\wedge\dots \xi_k \ar[r,mapsto] \&
-							(-)^k \iota(v_{\xi_1})\dots \iota(v_{\xi_{x_k}}) B
+							(-)^k \iota(\underline{\xi_1})\dots \iota(\underline{\xi_{x_k}}) B
 						\end{tikzcd}		
@@
 \begin{frame}[t]{Higher $B$-transformation}
-	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega + d B$}:
+	Consider now $\omega$ \alert{n-plectic} \quad and \quad \alert{$\tilde{\omega}=\omega - d B$}:
 		\medskip
@@
 					\& \binom{x}{\alpha} \ar[r,mapsto] \&
-					\binom{x}{\alpha +\iota_x B}
+					\binom{x}{\alpha -\iota_x B}
 				\end{tikzcd}	
@@
 % https://en.wikibooks.org/wiki/LaTeX/Bibliographies_with_biblatex_and_biber
+\subsection{Bibliography}
 \begin{frame}[t,allowframebreaks]{Extended Bibliography}
@@
 
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+\section{Addendum}
+%------------------------------------------------------------------------------------------------
+%##################################################################################
+\begin{frame}
+	\begin{center}
+	\Huge\emph{Addendum}
+
+	\vspace{1em}
+	\small(Credits to \href{https://www.icmat.es/congresos/2022/poisson-ggi/program.php}{M. Zambon})
+	\end{center}
+\end{frame}
+\addtocounter{framenumber}{-1}
+%##################################################################################
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+% Include From M Zambon Talk.
+\includepdf[pages={7-15}]{Sources/Zambon-slides.pdf}
+%-------------------------------------------------------------------------------------------------------------------------------------------------
+
 %------------------------------------------------------------------------------------------------
